### 2020-10-13 00_Input/01_CIRP_Template/PROCIR_CMS_2021_Tex_Template/PROCIR_CMS_2021.tex
First commit

% Template for Elsevier CRC journal article
% version 1.2 dated 09 May 2011

% This file (c) 2009-2011 Elsevier Ltd.  Modifications may be freely made,
% provided the edited file is saved under a different name

% This file contains modifications for Transportation Research Procedia

% Changes since version 1.1
% - added "procedia" option compliant with ecrc.sty version 1.2a
%   (makes the layout approximately the same as the Word CRC template)
% - added example for generating copyright line in abstract

%-----------------------------------------------------------------------------------

%% This template uses the elsarticle.cls document class and the extension package ecrc.sty
%% For full documentation on usage of elsarticle.cls, consult the documentation "elsdoc.pdf"
%% Further resources available at http://www.elsevier.com/latex

%-----------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                          %%
%% Important note on usage                                  %%
%% -----------------------                                  %%
%% This file should normally be compiled with PDFLaTeX      %%
%% Using standard LaTeX should work but may produce clashes %%
%%                                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The '3p' and 'times' class options of elsarticle are used for Elsevier CRC
%% The 'procedia' option causes ecrc to approximate to the Word template
\documentclass[5p,times,procedia]{elsarticle}
\flushbottom

%% The `ecrc' package must be called to make the CRC functionality available
\usepackage{ecrc}
%\usepackage{amsmath}

%% The ecrc package defines commands needed for running heads and logos.
%% For running heads, you can set the journal name, the volume, the starting page and the authors

%% set the volume if you know. Otherwise `00'
\volume{00}

%% set the starting page if not 1
\firstpage{1}

%% Give the name of the journal
\journalname{Procedia CIRP}

%% Give the author list to appear in the running head
%% Example \runauth{C.V. Radhakrishnan et al.}
\runauth{Author name}

%% The choice of journal logo is determined by the \jid and \jnltitlelogo commands.
%% A user-supplied logo with the name <\jid>logo.pdf will be inserted if present.
%% e.g. if \jid{yspmi} the system will look for a file yspmilogo.pdf
%% Otherwise the content of \jnltitlelogo will be set between horizontal lines as a default logo

%% Give the abbreviation of the Journal.
\jid{trpro}

%% Give a short journal name for the dummy logo (if needed)
%\jnltitlelogo{Transportation Research}

%% Hereafter the template follows `elsarticle'.
%% For more details see the existing template files elsarticle-template-harv.tex and elsarticle-template-num.tex.

%% Elsevier CRC generally uses a numbered reference style
%% For this, the conventions of elsarticle-template-num.tex should be followed (included below)
%% If using BibTeX, use the style file elsarticle-num.bst

%% End of ecrc-specific commands
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The amssymb package provides various useful mathematical symbols

\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%\biboptions{authoryear}

% \biboptions{}

% if you have landscape tables
\usepackage[figuresright]{rotating}
%\usepackage{harvard}
% put your own definitions here:x
%   \newcommand{\cZ}{\cal{Z}}
%   \newtheorem{def}{Definition}[section]
%   ...

% add words to TeX's hyphenation exception list
%\hyphenation{author another created financial paper re-commend-ed Post-Script}

% declarations for front matter

\usepackage[bookmarks=false]{hyperref}
    \hypersetup{colorlinks,
      linkcolor=blue,
      citecolor=blue,
      urlcolor=blue}

\begin{document}
\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\dochead{54th CIRP Conference on Manufacturing Systems}%

\title{Insert here, the title of your paper, Capitalize first letter}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[a]{First Author} 
\author[b]{Second Author}
\author[a,b]{Third Author\corref{*}}
%\ead{author@institute.xxx}

\address[a]{First affiliation, Address, City and Postcode, Country}
\address[b]{Second affiliation, Address, City and Postcode, Country}

\aucores{* Corresponding author. Tel.: +0-000-000-0000 ; fax: +0-000-000-0000. {\it E-mail address:} author@institute.xxx}

\begin{abstract}
%% Text of abstract
Insert here your abstract text. Abstract is a maximum of 100 words.
\end{abstract}

\begin{keyword}
Type your keywords here, separated by semicolons ;

%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}
%\cortext[cor1]{Corresponding author. Tel.: +0-000-000-0000 ; fax: +0-000-000-0000.}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

%% main text

%\enlargethispage{-7mm}
\section{Main Text}
\label{main}

Here introduce the paper, and put a nomenclature if necessary, in a box with the same font size as the rest of the paper. The paragraphs continue from here and are only separated by headings, subheadings, images and formulae. The section headings are arranged by numbers, bold and 10 pt. Here follows further instructions for authors.

\vspace*{8pt}
\begin{nomenclature}
\begin{deflist}[A]
\defitem{A}\defterm{radius of}
\defitem{B}\defterm{position of}
\defitem{C}\defterm{further nomenclature continues down the page inside the text box}
\end{deflist}
\end{nomenclature}\vskip24pt

\subsection{ Structure}
Files must be in LaTeX format only and should be formatted for direct printing, using the CRC LaTeX template provided. Figures and tables should be embedded and not supplied separately.

Please make sure that you use as much as possible normal fonts in your documents. Special fonts, such as fonts used in\vadjust{\vfill\pagebreak} the Far East (Japanese, Chinese, Korean, etc.) may cause problems during processing. To avoid unnecessary errors you are strongly advised to use the `spellchecker' function of TeX Editor. Follow this order when typing manuscripts: Title, Authors, Affiliations, Abstract, Keywords, Main text (including figures and tables), Acknowledgements, References, Appendix. Collate acknowledgements in a separate section at the end of the article and do not include them on the title page, as a footnote to the title or otherwise.

Bulleted lists may be included and should look like this:
\begin{itemize}[]
\item First point
\item Second point
\item And so on
\end{itemize}

Ensure that you return to the `Els-body-text' style, the style that you will mainly be using for large blocks of text, when you have completed your bulleted list.

Please do not alter the formatting and style layouts which have been set up in this template document. As indicated in the template, papers should be prepared in single column format suitable for direct printing onto paper with trim size $192 \times 262$ mm. Do not number pages on the front, as page numbers will be added separately for the preprints and the Proceedings. Leave a line clear between paragraphs. All the required style templates are provided in the file ``LaTeX Template'' with the appropriate name supplied, e.g. choose 1. Els1st-order-head for your first order heading text, els-abstract-text for the abstract text etc.

\subsection{ Tables}

All tables should be numbered with Arabic numerals. Every table should have a caption. Headings should be placed above tables, left justified. Only horizontal lines should be used within a table, to distinguish the column headings from the body of the table, and immediately above and below the table. Tables must be embedded into the text and not supplied separately. Below is an example which the authors may find useful.

\begin{table}[h]
\caption{An example of a table.}
\begin{tabular*}{\hsize}{@{\extracolsep{\fill}}lll@{}}
\toprule
An example of a column heading & Column A ({\it{t}}) & Column B ({\it{t}})\\
\colrule
And an entry &   1 &  2\\
And another entry  & 3 &  4\\
And another entry &  5 &  6\\
\botrule
\end{tabular*}
\end{table}

%\enlargethispage{12pt}

\subsection{ Construction of references}

References must be listed at the end of the paper. Do not begin them on a new page unless this is absolutely necessary. Authors should ensure that every reference in the text appears in the list of references and vice versa. Indicate references by \cite{clark} or \cite{Deal} or \cite{Fachinger2006} in the text.

Some examples of how your references should be listed are given at the end of this template in the `References' section, which will allow you to assemble your reference list according to the correct format and font size.

Reference generation by using bibliography style commands for LaTeX template only.

The author may use ``elsarticle-harv.bst'' as per the style required in document. The sample bib file could be referred. 
If the author may using bibstyle for providing references author must comment the bibliography section in TeX file, Bibtex will generate the reference automatically.

If the author may not able to view the references in output same could be done by copying the bibliography section from ``filename.bbl'' file and paste in TeX file.

\subsection{Section headings}
Section headings should be left justified, bold, with the first letter capitalized and numbered consecutively, starting with the Introduction. Sub-section headings should be in capital and lower-case italic letters, numbered 1.1, 1.2, etc,~and left justified, with second~and subsequent lines indented. All headings should have a minimum of two text lines after them before a page or column break.
Ensure the text area is not blank except for the last page.

\subsection{General guidelines for the preparation of your text}
Avoid hyphenation at the end of a line. Symbols denoting vectors and matrices should be indicated in bold type. Scalar variable names should normally be expressed using italics. Weights and measures should be expressed in SI units. All non-standard abbreviations or symbols must be defined when first mentioned, or a glossary provided.

\subsection{File naming and delivery}
Please title your files in this order `procedia acronym\_conference acronym\_authorslastname'.  Submit both the source file and the PDF to the Guest Editor.

Artwork filenames should comply with the syntax ``aabbbbbb.ccc'', where:
\begin{itemize}
\item a = artwork component type
\item b = manuscript reference code
\item c = standard file extension

Component types:
\item gr = figure
\item pl = plate
\item sc = scheme
\item fx = fixed graphic
\end{itemize}

\begin{figure*}[t]\vspace*{4pt}
%\centerline{\includegraphics{fx1}\hspace*{5mm}\includegraphics{fx1}}
\centerline{\includegraphics{gr1}}
\caption{(a) first picture; (b) second picture.}
\end{figure*}

\subsection{Footnotes}
Footnotes should be avoided if possible. Necessary footnotes should be denoted in the text by consecutive superscript letters\footnote{Footnote text.}. The footnotes should be typed single spaced, and in smaller type size (8 pt), at the foot of the page in which they are mentioned, and separated from the main text by a one line space extending at the foot of the column. The `Els-footnote' style is available in the ``TeX Template'' for the text of the footnote.

Please do not change the margins of the template as this can result in the footnote falling outside printing range.

\section{Illustrations}
All figures should be numbered with Arabic numerals (1,2,3,$\,\ldots.$). Every figure should have a caption. All\break photographs, schemas, graphs and diagrams are to be referred to as figures. Line drawings should be good\break quality scans or true electronic output. Low-quality scans are not acceptable. Figures must be embedded into the text and not supplied separately. In MS word input the figures must be properly coded. Preferred format of figures are PNG, JPEG, GIF etc. Lettering and symbols should be clearly defined either in the caption or in a legend provided as part of the figure. Figures should be placed at the top or bottom of a page wherever possible, as close as possible to the first reference to them in the paper. Please ensure that all the figures are of 300 DPI resolutions as this will facilitate good output.

The figure number and caption should be typed below the illustration in 8 pt and left justified [{\bfseries\itshape Note:} one-line captions of length less than column width (or full typesetting width or oblong) centered]. For more guidelines and\break information to help you submit high quality artwork please visit: http://www.elsevier.com/artworkinstructions\break Artwork has no text along the side of it in the main body of the text. However, if two images fit next to each other, these may be placed next to each other to save space. For example, see Fig.~1.

\section{Equations}
Equations and formulae should be typed in MathType, and numbered consecutively with Arabic numerals in parentheses on the right hand side of the page (if referred to explicitly in the text). They should also be separated from the surrounding text by one space
\begin{equation}
\begin{array}{lcl}
\displaystyle X_r &=& \displaystyle\dot{Q}^{''}_{rad}\left/\left(\dot{Q}^{''}_{rad} + \dot{Q}^{''}_{conv}\right)\right.\\[6pt]
\displaystyle \rho &=& \displaystyle\frac{\vec{E}}{J_c(T={\rm const.})\cdot\left(P\cdot\left(\displaystyle\frac{\vec{E}}{E_c}\right)^m+(1-P)\right)}
\end{array}
\end{equation}

\section{Online license transfer}
All authors are required to complete the Procedia exclusive license transfer agreement before the article can be published, which they can do online. This transfer agreement enables Elsevier to protect the copyrighted material for the authors, but does not relinquish the authors' proprietary rights. The copyright transfer covers the exclusive rights to reproduce and distribute the article, including reprints, photographic reproductions, microfilm or any other reproductions of similar nature and translations. Authors are responsible for obtaining from the copyright holder, the permission to reproduce any figures for which copyright exists.

\vfill\pagebreak

\section*{Acknowledgements}

Acknowledgements and Reference heading should be left justified, bold, with the first letter capitalized but have no numbers. Text below continues as normal.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

\appendix
\section{An example appendix}
Authors including an appendix section should do so before References section. Multiple appendices should all have headings in the style used above. They will automatically be ordered A, B, C etc.

\subsection{Example of a sub-heading within an appendix}
There is also the option to include a subheading within the Appendix if you wish.
%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}         ==>>  [#]
%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
%%

%The citation must be used in following style: \cite{article-minimal} \cite{article-full} \cite{article-crossref} \cite{whole-journal}.
%% References with BibTeX database:

%\bibliography{xampl}
%\bibliographystyle{elsarticle-harv}

%% Authors are advised to use a BibTeX database file for their reference list.
%% The provided style file elsarticle-num.bst formats references in the required Procedia style

%% For references without a BibTeX database:

 \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

\bibitem[Clark et al.(1962)]{clark}Clark, T., Woodley, R., De Halas, D., 1962. Gas-Graphite Systems, in ``{\it Nuclear Graphite}''. 
In: Nightingale, R. (Ed.). Academic Press, New York, pp. 387.

\bibitem[Deal and Grove(2009) ]{Deal}Deal, B., Grove, A., 1965. General Relationship for the Thermal Oxidation of Silicon. Journal of Applied Physics 36.2, 37--70.

\bibitem[Deep(2009)]{Deep}Deep-Burn Project: Annual Report for 2009, Idaho National Laboratory, Sept. 2009.

\bibitem[Fachinger(2004)]{Fachinger2004}Fachinger, J., den Exter, M., Grambow, B., Holgerson, S., Landesmann, C., Titov, M., Podruhzina, T., 2004. ``Behavior of spent HTR fuel elements in aquatic phases of repository host rock formations,'' 2nd International Topical Meeting on High Temperature Reactor Technology. Beijing, China, paper \#B08.

\bibitem[Fachinger(2006)]{Fachinger2006}Fachinger, J., 2006. Behavior
of HTR Fuel Elements in Aquatic Phases of Repository Host Rock Formations. Nuclear Engineering \& Design 236.3,      54.

 \end{thebibliography}

\clearpage\onecolumn

%%%% This page is for instructions only, once the article is finalize please omit the below text before creating the final PDF
\normalMode

\section*{Instructions to Authors for LaTeX template:}

\section{ZIP mode for LaTeX template:}

The zip package is created as per the guide lines present on the URL http://www.elsevier.com/author-schemas/ preparing-crc-journal-articles-with-latex for creating the LaTeX zip file of Procedia LaTeX template.  The zip generally contains the following files:
\begin{Itemize}[]\leftskip-12.7pt\labelsep3.3pt
\item ecrc.sty
\item  elsarticle.cls
\item elsdoc.pdf
\item .bst file
\item Manuscript templates for use with these bibliographic styles
\item  Generic and journal specific logos, etc.
\end{Itemize}

The LaTeX package is the main LaTeX template. All LaTeX support files are required for LaTeX pdf generation from the LaTeX template package.

{\bf Reference style .bst file used for collaboration support:} In the LaTeX template packages of all Procedia titles a new ``.bst'' file is used which supports collaborations downloaded from the path http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class

\end{document}

%%
%% End of file.

### 2020-10-16 02_Paper/paper.tex
paper.

--- 2020-10-13 00_Input/01_CIRP_Template/PROCIR_CMS_2021_Tex_Template/PROCIR_CMS_2021.tex
@@
 
-\title{Insert here, the title of your paper, Capitalize first letter}
+\title{Predictive analytics in quality assurance for assembly processes:
+       lessons learned from a case study at an industry 4.0 demonstration cell}
 
@@
 
-\author[a]{First Author} 
-\author[b]{Second Author}
-\author[a,b]{Third Author\corref{*}}
+\author[a]{Peter Burggräf}
+\author[a]{Johannes Wagner}
+\author[a]{Benjamin Koke}
+\author[a]{Fabian Steinberg} 
+\author[a]{Alejandro R. Pérez M.}
+\author[b,c]{Jochen Garcke}
+\author[b]{Daniela Steffes-Lai}
+\author[b,d]{Moritz Wolter}
+
 %\ead{author@institute.xxx}
 
-\address[a]{First affiliation, Address, City and Postcode, Country}
-\address[b]{Second affiliation, Address, City and Postcode, Country}
+\address[a]{Chair of International Production Engineering and Management (IPEM), Universität Siegen, Paul-Bonatz-Straße 9-11, Siegen - 57076, Germany}
+\address[b]{Fraunhofer Institute for Algorithms and Scientific Computing (SCAI), Schloss Birlinghoven 1, Sankt Augustin- 53757, Germany}
+\address[c]{Institut for Numerical Simulation, Universität Siegen, Endenicher Allee 19b, 53115 Bonn}
+\address[d]{Institut for Computer Science, Universität Bonn, Endenicher Allee 19A}
 
@@
 %% Text of abstract
-Insert here your abstract text. Abstract is a maximum of 100 words.
+Quality assurance (QA) is an important task in manufacturing to assess whether products 
+meet their specifications. However, QA might be expensive, time-consuming, incomplete, or delayed.
+This paper presents a solution for predictive analytics in QA based on machine sensor values during production while employing machine-learning models based on logistic regression in a controlled environment.
+Furthermore, we present lessons learned while implementing this model, which helps to reduce complexity in further industrial applications.
+The paper’s outcome proves that the developed model was able to predict the product quality, as well as to identify the correlation between machine-status and faulty product occurrence.
 \end{abstract}

### 2020-10-16 02_Paper/setup_autoformat.sh
paper backbone.

@@ -1,0 +1,110 @@
+#!/bin/bash
+
+pushd "$(dirname $0)" >/dev/null
+
+bold=""
+red=""
+green=""
+normal=""
+
+if test -t 1; then
+  ncolors=$(tput colors)
+  if test -n "$ncolors" && test $ncolors -ge 8; then
+    bold="$(tput bold)"
+    red="$(tput setaf 1)"
+    green="$(tput setaf 2)"
+    normal="$(tput sgr0)"
+  fi
+fi
+
+git diff --quiet --exit-code
+changed=$?
+git diff --quiet --cached --exit-code
+staged=$?
+
+if [ $changed != 0 -o $staged != 0 ]; then
+    echo "${bold}${red}You have uncommitted changes. Please commit them first before running this script.${normal}" >&2
+    popd >/dev/null
+    exit -2
+fi
+
+cat <<END
+This script installs a filter that re-formats your TEX files according to
+your preferences automatically every time you check in or check out a file.
+END
+
+perl -e 'use Text::Reflow;' 2>/dev/null
+reflow=$?
+OPTION_SENTENCE="Format one sentence per line"
+OPTION_PARAGRAPH="Format one paragraph per line"
+OPTION_SERVER="Use same format as the GIT server does"
+OPTION_WRAP="Wrap lines after fixed number of columns"
+OPTION_UNINSTALL="Uninstall the filter, do not do anything"
+if [ $reflow != 0 ]; then
+    echo "Optional feature not available:"
+    echo "    Line wrapping after a fixed number of clumns is not available on your machine."
+    echo "    To enable it, install the Perl module Text::Reflow and run this script again."
+    case "$OSTYPE" in
+    linux-gnu) echo "    sudo apt-get install libtext-reflow-perl";;
+    darwin*)   echo "    cpan -i Text::Reflow";;
+    esac
+    echo
+    options=("$OPTION_SENTENCE" "$OPTION_PARAGRAPH" "$OPTION_SERVER" "$OPTION_UNINSTALL")
+else
+    options=("$OPTION_SENTENCE" "$OPTION_PARAGRAPH" "$OPTION_WRAP" "$OPTION_SERVER" "$OPTION_UNINSTALL")
+fi
+
+echo "Please select your favorite format:"
+
+SMUDGE=""
+PS3=$'\n'"${bold}Please enter your choice: ${normal}"
+select opt in "${options[@]}"
+do
+    case "$opt" in
+        "${OPTION_SENTENCE}")
+            SMUDGE="sentence"
+            break
[…]

### 2020-10-16 02_Paper/setup_autoformat.sh
first commit.

@@ -103,7 +103,7 @@ fi
 echo
 
 # don't need stashing as we make sure that there are no uncommitted changes
-git checkout master
+git checkout main
 
 echo "${bold}${green}Successfully installed filter.${normal}"
 popd >/dev/null

### 2020-10-16 02_Paper/paper.tex
paper backbone.
abstract.
latex setup done.

@@
 meet their specifications. However, QA might be expensive, time-consuming, incomplete, or delayed.
-This paper presents a solution for predictive analytics in QA based on machine sensor values during production while employing machine-learning models based on logistic regression in a controlled environment.
-Furthermore, we present lessons learned while implementing this model, which helps to reduce complexity in further industrial applications.
-The paper’s outcome proves that the developed model was able to predict the product quality, as well as to identify the correlation between machine-status and faulty product occurrence.
+This paper presents a solution for predictive analytics in QA based on machine sensor values during
+production while employing machine-learning models based on logistic regression in a controlled environment. 
+Furthermore, we present lessons learned while implementing this model, which helps to reduce complexity in
+further industrial applications. The paper’s outcome proves that the developed model was able to predict
+product quality, as well as to identify the correlation between machine-status and faulty product occurrence.
 \end{abstract}
@@
 
-%%
-%% Start line numbering here if you want
-%%
-% \linenumbers
+\section{Introduction}
 
-%% main text
+\section{Related Works}
 
-%\enlargethispage{-7mm}
-\section{Main Text}
-\label{main}
+\section{The Demo-Cell}
 
-Here introduce the paper, and put a nomenclature if necessary, in a box with the same font size as the rest of the paper.
-The paragraphs continue from here and are only separated by headings, subheadings, images and formulae.
-The section headings are arranged by numbers, bold and 10 pt.
-Here follows further instructions for authors.
+\section{Methods}
 
-\vspace*{8pt}
-\begin{nomenclature}
-\begin{deflist}[A]
-\defitem{A}\defterm{radius of}
-\defitem{B}\defterm{position of}
-\defitem{C}\defterm{further nomenclature continues down the page inside the text box}
-\end{deflist}
-\end{nomenclature}\vskip24pt
+\section{Experiments}
 
-\subsection{ Structure}
-Files must be in LaTeX format only and should be formatted for direct printing, using the CRC LaTeX template provided. Figures and tables should be embedded and not supplied separately.
-
-Please make sure that you use as much as possible normal fonts in your documents.
-Special fonts, such as fonts used in\vadjust{\vfill\pagebreak} the Far East (Japanese, Chinese, Korean, etc.) may cause problems during processing.
-To avoid unnecessary errors you are strongly advised to use the `spellchecker' function of TeX Editor.
-Follow this order when typing manuscripts: Title, Authors, Affiliations, Abstract, Keywords, Main text (including figures and tables), Acknowledgements, References, Appendix.
-Collate acknowledgements in a separate section at the end of the article and do not include them on the title page, as a footnote to the title or otherwise.
-
-Bulleted lists may be included and should look like this:
-\begin{itemize}[]
-\item First point
-\item Second point
-\item And so on
-\end{itemize}
-
-Ensure that you return to the `Els-body-text' style, the style that you will mainly be using for large blocks of text, when you have completed your bulleted list.
-
-Please do not alter the formatting and style layouts which have been set up in this template document.
-As indicated in the template, papers should be prepared in single column format suitable for direct printing onto paper with trim size $192 \times 262$ mm.
-Do not number pages on the front, as page numbers will be added separately for the preprints and the Proceedings.
-Leave a line clear between paragraphs.
-All the required style templates are provided in the file ``LaTeX Template'' with the appropriate name supplied, e.g.
-choose 1.
-Els1st-order-head for your first order heading text, els-abstract-text for the abstract text etc.
-
-\subsection{ Tables}
-
-All tables should be numbered with Arabic numerals.
-Every table should have a caption.
-Headings should be placed above tables, left justified.
-Only horizontal lines should be used within a table, to distinguish the column headings from the body of the table, and immediately above and below the table.
-Tables must be embedded into the text and not supplied separately.
-Below is an example which the authors may find useful.
-
-\begin{table}[h]
-\caption{An example of a table.}
-\begin{tabular*}{\hsize}{@{\extracolsep{\fill}}lll@{}}
-\toprule
-An example of a column heading & Column A ({\it{t}}) & Column B ({\it{t}})\\
-\colrule
-And an entry &   1 &  2\\
-And another entry  & 3 &  4\\
-And another entry &  5 &  6\\
-\botrule
-\end{tabular*}
-\end{table}
-
-%\enlargethispage{12pt}
-
-\subsection{ Construction of references}
-
-References must be listed at the end of the paper.
-Do not begin them on a new page unless this is absolutely necessary.
-Authors should ensure that every reference in the text appears in the list of references and vice versa.
-Indicate references by \cite{clark} or \cite{Deal} or \cite{Fachinger2006} in the text.
-
-Some examples of how your references should be listed are given at the end of this template in the `References' section, which will allow you to assemble your reference list according to the correct format and font size.
-
-Reference generation by using bibliography style commands for LaTeX template only.
-
-The author may use ``elsarticle-harv.bst'' as per the style required in document. The sample bib file could be referred. 
-If the author may using bibstyle for providing references author must comment the bibliography section in TeX file, Bibtex will generate the reference automatically.
-
-If the author may not able to view the references in output same could be done by copying the bibliography section from ``filename.bbl'' file and paste in TeX file.
-
-\subsection{Section headings}
-Section headings should be left justified, bold, with the first letter capitalized and numbered consecutively, starting with the Introduction.
-Sub-section headings should be in capital and lower-case italic letters, numbered 1.1, 1.2, etc,~and left justified, with second~and subsequent lines indented.
-All headings should have a minimum of two text lines after them before a page or column break.
-Ensure the text area is not blank except for the last page.
-
-\subsection{General guidelines for the preparation of your text}
-Avoid hyphenation at the end of a line.
-Symbols denoting vectors and matrices should be indicated in bold type.
-Scalar variable names should normally be expressed using italics.
-Weights and measures should be expressed in SI units.
-All non-standard abbreviations or symbols must be defined when first mentioned, or a glossary provided.
-
-\subsection{File naming and delivery}
-Please title your files in this order `procedia acronym\_conference acronym\_authorslastname'.  Submit both the source file and the PDF to the Guest Editor.
-
-Artwork filenames should comply with the syntax ``aabbbbbb.ccc'', where:
-\begin{itemize}
-\item a = artwork component type
-\item b = manuscript reference code
-\item c = standard file extension
-
-Component types:
-\item gr = figure
-\item pl = plate
-\item sc = scheme
-\item fx = fixed graphic
-\end{itemize}
-
-\begin{figure*}[t]\vspace*{4pt}
-%\centerline{\includegraphics{fx1}\hspace*{5mm}\includegraphics{fx1}}
-\centerline{\includegraphics{gr1}}
-\caption{(a) first picture; (b) second picture.}
-\end{figure*}
-
-\subsection{Footnotes}
-Footnotes should be avoided if possible.
-Necessary footnotes should be denoted in the text by consecutive superscript letters\footnote{Footnote text.}.
-The footnotes should be typed single spaced, and in smaller type size (8 pt), at the foot of the page in which they are mentioned, and separated from the main text by a one line space extending at the foot of the column.
-The `Els-footnote' style is available in the ``TeX Template'' for the text of the footnote.
-
-Please do not change the margins of the template as this can result in the footnote falling outside printing range.
-
-\section{Illustrations}
-All figures should be numbered with Arabic numerals (1,2,3,$\,\ldots.$).
-Every figure should have a caption.
-All\break photographs, schemas, graphs and diagrams are to be referred to as figures.
-Line drawings should be good\break quality scans or true electronic output.
-Low-quality scans are not acceptable.
-Figures must be embedded into the text and not supplied separately.
-In MS word input the figures must be properly coded.
-Preferred format of figures are PNG, JPEG, GIF etc.
-Lettering and symbols should be clearly defined either in the caption or in a legend provided as part of the figure.
-Figures should be placed at the top or bottom of a page wherever possible, as close as possible to the first reference to them in the paper.
-Please ensure that all the figures are of 300 DPI resolutions as this will facilitate good output.
-
-The figure number and caption should be typed below the illustration in 8 pt and left justified [{\bfseries\itshape Note:} one-line captions of length less than column width (or full typesetting width or oblong) centered].
-For more guidelines and\break information to help you submit high quality artwork please visit: http://www.elsevier.com/artworkinstructions\break Artwork has no text along the side of it in the main body of the text.
-However, if two images fit next to each other, these may be placed next to each other to save space.
-For example, see Fig.~1.
-
-\section{Equations}
-Equations and formulae should be typed in MathType, and numbered consecutively with Arabic numerals in parentheses on the right hand side of the page (if referred to explicitly in the text).
-They should also be separated from the surrounding text by one space
-\begin{equation}
-\begin{array}{lcl}
-\displaystyle X_r &=& \displaystyle\dot{Q}^{''}_{rad}\left/\left(\dot{Q}^{''}_{rad} + \dot{Q}^{''}_{conv}\right)\right.\\[6pt]
-\displaystyle \rho &=& \displaystyle\frac{\vec{E}}{J_c(T={\rm const.})\cdot\left(P\cdot\left(\displaystyle\frac{\vec{E}}{E_c}\right)^m+(1-P)\right)}
-\end{array}
-\end{equation}
-
-\section{Online license transfer}
-All authors are required to complete the Procedia exclusive license transfer agreement before the article can be published, which they can do online.
-This transfer agreement enables Elsevier to protect the copyrighted material for the authors, but does not relinquish the authors' proprietary rights.
-The copyright transfer covers the exclusive rights to reproduce and distribute the article, including reprints, photographic reproductions, microfilm or any other reproductions of similar nature and translations.
-Authors are responsible for obtaining from the copyright holder, the permission to reproduce any figures for which copyright exists.
-
-\vfill\pagebreak
-
-\section*{Acknowledgements}
-
-Acknowledgements and Reference heading should be left justified, bold, with the first letter capitalized but have no numbers. Text below continues as normal.
-
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-\appendix
-\section{An example appendix}
-Authors including an appendix section should do so before References section. Multiple appendices should all have headings in the style used above. They will automatically be ordered A, B, C etc.
-
-\subsection{Example of a sub-heading within an appendix}
-There is also the option to include a subheading within the Appendix if you wish.
-%% References
-%%
-%% Following citation commands can be used in the body text:
-%% Usage of \cite is as follows:
-%%   \cite{key}         ==>>  [#]
-%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
-%%
-
-%The citation must be used in following style: \cite{article-minimal} \cite{article-full} \cite{article-crossref} \cite{whole-journal}.
-%% References with BibTeX database:
-
-%\bibliography{xampl}
-%\bibliographystyle{elsarticle-harv}
-
-%% Authors are advised to use a BibTeX database file for their reference list.
-%% The provided style file elsarticle-num.bst formats references in the required Procedia style
-
-%% For references without a BibTeX database:
-
- \begin{thebibliography}{00}
-
-%% \bibitem must have the following form:
-%%   \bibitem{key}...
-%%
-
-\bibitem[Clark et al.(1962)]{clark}Clark, T., Woodley, R., De Halas, D., 1962. Gas-Graphite Systems, in ``{\it Nuclear Graphite}''. 
-In: Nightingale, R. (Ed.). Academic Press, New York, pp. 387.
-
-\bibitem[Deal and Grove(2009) ]{Deal}Deal, B., Grove, A., 1965. General Relationship for the Thermal Oxidation of Silicon. Journal of Applied Physics 36.2, 37--70.
-
-\bibitem[Deep(2009)]{Deep}Deep-Burn Project: Annual Report for 2009, Idaho National Laboratory, Sept. 2009.
-
-\bibitem[Fachinger(2004)]{Fachinger2004}Fachinger, J., den Exter, M., Grambow, B., Holgerson, S., Landesmann, C., Titov, M., Podruhzina, T., 2004.
-``Behavior of spent HTR fuel elements in aquatic phases of repository host rock formations,'' 2nd International Topical Meeting on High Temperature Reactor Technology.
-Beijing, China, paper \#B08.
-
-\bibitem[Fachinger(2006)]{Fachinger2006}Fachinger, J., 2006. Behavior
-of HTR Fuel Elements in Aquatic Phases of Repository Host Rock Formations. Nuclear Engineering \& Design 236.3,      54.
-
- \end{thebibliography}
-
-\clearpage\onecolumn
-
-%%%% This page is for instructions only, once the article is finalize please omit the below text before creating the final PDF
-\normalMode
-
-\section*{Instructions to Authors for LaTeX template:}
-
-\section{ZIP mode for LaTeX template:}
-
-The zip package is created as per the guide lines present on the URL http://www.elsevier.com/author-schemas/ preparing-crc-journal-articles-with-latex for creating the LaTeX zip file of Procedia LaTeX template.
-The zip generally contains the following files:
-\begin{Itemize}[]\leftskip-12.7pt\labelsep3.3pt
-\item ecrc.sty
-\item  elsarticle.cls
-\item elsdoc.pdf
-\item .bst file
-\item Manuscript templates for use with these bibliographic styles
-\item  Generic and journal specific logos, etc.
-\end{Itemize}
-
-The LaTeX package is the main LaTeX template. All LaTeX support files are required for LaTeX pdf generation from the LaTeX template package.
-
-{\bf Reference style .bst file used for collaboration support:} In the LaTeX template packages of all Procedia titles a new ``.bst'' file is used which supports collaborations downloaded from the path http://www.elsevier.com/author-schemas/the-elsarticle-latex-document-class
+\section{Conclusion}
 
 \end{document}
-
-%%
-%% End of file.

### 2020-10-16 02_Paper/paper.tex
fix encoding
fix INS.

@@
 \usepackage{ecrc}
-%\usepackage{amsmath}
+\usepackage{amsmath}
+\usepackage[utf8]{inputenc}
 
@@
 \address[b]{Fraunhofer Institute for Algorithms and Scientific Computing (SCAI), Schloss Birlinghoven 1, Sankt Augustin- 53757, Germany}
-\address[c]{Institut for Numerical Simulation, Universität Siegen, Endenicher Allee 19b, 53115 Bonn}
-\address[d]{Institut for Computer Science, Universität Bonn, Endenicher Allee 19A}
+\address[c]{Institut for Numerical Simulation, Universität Bonn, Endenicher Allee 19b, 53115 Bonn}
+\address[d]{Institut for Computer Science, Universität Bonn, Endenicher Allee 19a, 53115 Bonn}
 

### 2020-10-30 02_Paper/paper.tex
Update corresponding author and keywords
Paper structure
Update structure

@@
 
-\aucores{* Corresponding author. Tel.: +0-000-000-0000 ; fax: +0-000-000-0000. {\it E-mail address:} author@institute.xxx}
+\aucores{* Corresponding author. Tel.: +49-271-740-4509; fax: +49-271-740-2630. {\it E-mail address:} alejandro.perez@uni-siegen.de}
 
@@
 \begin{keyword}
-Type your keywords here, separated by semicolons ;
+Machine-Learning \sep Predictive Quality \sep Production \sep Quality Assurance \sep Logistic Regression
 
@@
 
-\section{Introduction}
+\section{Introduction} % 1 Page (incl authors, abstract)
 
-\section{Related Works}
+% a)	Products’ quality must always be guaranteed.
+% b)	In certain cases (especially in series assembly production) there is a delay between quality inspection and end of the production process  high potential for producing scrap 
+% c)	By doing quality inspection based on samples, there is still a risk of sending NOK parts to customers
+% d)	Cost of quality check might be expensive
+% e)	Quality assurance is normally done at the end of production (for assembly processes)   
+% f)	Early prediction of the production’s quality  would help to decrease the amount of scrap  and the risk of sending NOK parts to customers
+% g)	Variable predictions by using machine learning models is currently widely used in diverse fields due to its accurate predictions  with the data collected from the machines, prediction models can be implemented for specific predicted values
 
-\section{The Demo-Cell}
+\section{Related Works} % 1 Page
 
-\section{Methods}
+\subsection{Quality check in production} % Basic books (find summarize) basic concepts
 
-\section{Experiments}
+% a)	How quality check is done in production
+%        i)	Concepts and sampling plan
+%        ii)	Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]
 
-\section{Conclusion}
+\subsection{Predictive analytics in production}
+
+% b)	Predictive analytics in production focusing in QA
+%        i)	Existing approaches and methods
+
+\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page
+
+% What is the demozelle and why it is relevant as study case
+% a)	Description of the assemble process in the Demozelle 
+% Incl pictures
+
+\section{Methods} %3/4 Page
+
+% b)	Data  is collected from the demonstration cell and analyzed 
+% c)	ML model [regression] is trained [type of model tbd]
+
+\section{Experiments} % 1.5 Pages
+
+\subsection{Lesson Learned} % 1/2 Page
+
+% h)	Explain experiences by doing the research
+
+\section{Conclusion} % 1/2 Page
 

### 2020-11-02 02_Paper/paper.tex
update structure
extra sections.

@@
 
-\section{Introduction} % 1 Page (incl authors, abstract)
+\section{Introduction}
 
@@
 
-\section{Related Works} % 1 Page
+\section{Related Works}
 
-\subsection{Quality check in production} % Basic books (find summarize) basic concepts
+\subsection{Quality check in production}
 
-% a)	How quality check is done in production
+% b)	How quality check is done in production
 %        i)	Concepts and sampling plan
@@
 
-% b)	Predictive analytics in production focusing in QA
+% a)	Predictive analytics in production focusing in QA
 %        i)	Existing approaches and methods
 
-\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page
+\section{The Demo-Cell}
 
 % What is the demozelle and why it is relevant as study case
+
+\section{Methods}
+
 % a)	Description of the assemble process in the Demozelle 
-% Incl pictures
-
-\section{Methods} %3/4 Page
-
 % b)	Data  is collected from the demonstration cell and analyzed 
 % c)	ML model [regression] is trained [type of model tbd]
+\subsection{Measurement}
 
-\section{Experiments} % 1.5 Pages
+\subsection{Machine Learning}
 
-\subsection{Lesson Learned} % 1/2 Page
+\section{Experiments}
+
+\subsection{Recording the data}
+
+\subsection{Classifier optimization and testing}
+
+\begin{table}
+       \begin{tabular}{ c c }
+              Support Vector Machine & 95.\% \\
+              Multilinear Perceptron & 95.\% \\
+              Random Forest          & 100\%
+       \end{tabular}
+       \caption{Method comparison for fault detection using the industry demo data test set.}
+\end{table}
+
+\section{Conclusion}
+
+\subsection{Lesson Learned}
 
@@
 
-\section{Conclusion} % 1/2 Page
-
 \end{document}

### 2020-11-02 02_Paper/paper.tex

--- 2020-10-30 02_Paper/paper.tex
@@
 \author[a]{Alejandro R. Pérez M.}
+\author[a]{Lennart Schmallenbach}
 \author[b,c]{Jochen Garcke}
@@
 
-\section{Related Works} % 1 Page
+\section{Related Works} % 1 Page \Lennart
 
@@
 
+% Predictive analytics as concepts
+% Implementation in production
+%   - Predictive Maintenance
+%   - Scheduling
+%   - Other
+
+% If happens to be something with P.A. Quality Check
 % b)	Predictive analytics in production focusing in QA
@@
 
-\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page
+% Note: Ideal is to find a gap in literature, that proves why do we do it and why it is important
+
+\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases
 
@@
 % c)	ML model [regression] is trained [type of model tbd]
+\subsection{Measurement}
 
-\section{Experiments} % 1.5 Pages
+\subsection{Machine Learning}
+
+\section{Experiments}
+
+\subsection{Recording the data}
+
+\subsection{Classifier optimization and testing}
+
+\begin{table}
+       \begin{tabular}{ c c }
+              Support Vector Machine & 95.\% \\
+              Multilinear Perceptron & 95.\% \\
+              Random Forest          & 100\%
+       \end{tabular}
+       \caption{Method comparison for fault detection using the industry demo data test set.}
+\end{table}
+
+\section{Conclusion}
 

### 2020-11-02 02_Paper/paper.tex
tex discussion commands.
paper update.

@@
       urlcolor=blue}
+\usepackage{xcolor}
+\newcommand{\AP}[1]{{\color{blue} {\bf (AP: #1)}}}
+\newcommand{\LS}[1]{{\color{purple} {\bf (LS: #1)}}}
+\newcommand{\MW}[1]{{\color{teal} {\bf (MW: #1)}}}
+\newcommand{\JG}[1]{{\color{green} {\bf (JG: #1)}}}
+\newcommand{\DSL}[1]{{\color{blue} {\bf (DSL: #1)}}}
 
@@
 
-% a)	Products’ quality must always be guaranteed.
-% b)	In certain cases (especially in series assembly production) there is a delay between quality inspection and end of the production process  high potential for producing scrap 
-% c)	By doing quality inspection based on samples, there is still a risk of sending NOK parts to customers
-% d)	Cost of quality check might be expensive
-% e)	Quality assurance is normally done at the end of production (for assembly processes)   
-% f)	Early prediction of the production’s quality  would help to decrease the amount of scrap  and the risk of sending NOK parts to customers
-% g)	Variable predictions by using machine learning models is currently widely used in diverse fields due to its accurate predictions  with the data collected from the machines, prediction models can be implemented for specific predicted values
+\AP{\begin{itemize}
+       \item	Products’ quality must always be guaranteed.
+       \item	In certain cases (especially in series assembly production) there is a delay between quality inspection
+              and end of the production process high potential for producing scrap 
+       \item	By doing quality inspection based on samples, there is still a risk of sending NOK parts to customers
+       \item	The cost of quality checks might be expensive
+       \item	Quality assurance is normally done at the end of production (for assembly processes)   
+       \item	Early prediction of the production’s quality  would help to decrease the amount of scrap  and the risk of sending NOK parts to customers
+       \item	Variable predictions by using machine learning models is currently widely used in diverse fields due to its accurate predictions with the data collected from the machines, 
+              prediction models can be implemented for specific predicted values
+\end{itemize}}
 
@@
 
-% a)	How quality check is done in production
-%        i)	Concepts and sampling plan
-%        ii)	Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]
+\AP{
+\begin{itemize}
+\item How quality check is done in production
+\item Concepts and sampling plan
+\item Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]
+\end{itemize}}
 
@@
 
-% Predictive analytics as concepts
-% Implementation in production
-%   - Predictive Maintenance
-%   - Scheduling
-%   - Other
-
-% If happens to be something with P.A. Quality Check
-% b)	Predictive analytics in production focusing in QA
-%        i)	Existing approaches and methods
-
-% Note: Ideal is to find a gap in literature, that proves why do we do it and why it is important
+\AP{
+Predictive analytics as concepts. Implementation in production
+\begin{itemize}
+       \item Predictive Maintenance
+       \item Scheduling
+       \item Other
+\end{itemize}       
+If happens to be something with P.A. Quality Check
+\begin{itemize}
+       \item	Predictive analytics in production focusing in QA
+       \item	Existing approaches and methods
+\end{itemize}      
+Note: Ideal is to find a gap in literature, that proves why do we do it and why it is important
+}
 
@@
 
-% What is the demozelle and why it is relevant as study case
-% a)	Description of the assemble process in the Demozelle 
-% Incl pictures
-
+\AP{
+What is the demozelle and why it is relevant as study case
+Description of the assemble process in the Demozelle 
+Incl pictures
+}
 \section{Methods} %3/4 Page
 
-% b)	Data  is collected from the demonstration cell and analyzed 
-% c)	ML model [regression] is trained [type of model tbd]
+Data  is collected from the demonstration cell and analyzed
+
 \subsection{Measurement}
@@
 \subsection{Classifier optimization and testing}
-
+We work with a total of 462 measurements. 
 \begin{table}
@@
 
-% h)	Explain experiences by doing the research
+\AP{explain experiences by doing the research}
 

### 2020-11-02 02_Paper/paper.tex
classifier update.

@@
 \subsection{Classifier optimization and testing}
-We work with a total of 462 measurements. 
+We work with a total of 132 measurements. Each containing arm and belt data
+logs of individual cell runs. 20 samples are set aside at random for testing 
+purposes, leaving 112 training samples. The random seed is set to 1
+
+We compare a total of three different classifier architectures on the data.
+A Support Vector Machine (SVM), a multilinear perceptron and a Random Forest
+structure. 
 \begin{table}
@@
        \caption{Method comparison for fault detection using the industry demo data test set.}
+       \label{tab:class_comp}
 \end{table}
+Results are shown in table~\ref{tab:class_comp}. For 55 of the total 132 samples
+quality measurements indicate a problem. This sets the 
+baseline over the entire data set, that would be obtained by simply labeling all samples
+as good. Over the entire data set, we require to classify more than 58.3\% of the data correctly.
+The test set contains eight incorrect samples. We would therefore expect the naive classifier
+to produce a 60\% accuracy, which we have to beat. In Table~\ref{tab:class_comp},
+we observe that this is indeed the case for all three approaches evaluated here.
 

### 2020-11-02 02_Paper/paper.tex
robot arm plot.

@@
 \usepackage[utf8]{inputenc}
+\usepackage[mode=buildnew]{standalone}% requires -shell-escape
+\usepackage{tikz}
+\usepackage{pgfplots}
+\usepgfplotslibrary{groupplots}
+\usepgfplotslibrary{dateplot}
+\pgfplotsset{compat=newest}
 
@@
 \end{itemize}      
-Note: Ideal is to find a gap in literature, that proves why do we do it and why it is important
+Note: Ideal is to find a gap in the literature, that proves why do we do it and why it is important
 }
@@
 \section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases
+\begin{figure}
+       \includestandalone[width=.45\textwidth]{img/cell_data_plot}
+       \caption{Robot arm movement patterns.}
+\end{figure}
 
@@
 logs of individual cell runs. 20 samples are set aside at random for testing 
-purposes, leaving 112 training samples. The random seed is set to 1
+purposes, leaving 112 training samples. The random number generator seed is
+set to one in order to ensure the train and test set splits are identical 
+for all experiments.
 
@@
 A Support Vector Machine (SVM), a multilinear perceptron and a Random Forest
-structure. 
+structure. All three methods are trained using standard hyperparameters.
+\footnote{In order to allow exact reproduction of these results source
+code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
 \begin{table}
+       \centering
        \begin{tabular}{ c c }
@@
               Multilinear Perceptron & 95.\% \\
-              Random Forest          & 100\%
+              Random Forest          & 100.\%
        \end{tabular}
-       \caption{Method comparison for fault detection using the industry demo data test set.}
+       \caption{Method comparison for our annomaly detection task 
+                using the industry demo data test set.}
        \label{tab:class_comp}
@@
 as good. Over the entire data set, we require to classify more than 58.3\% of the data correctly.
-The test set contains eight incorrect samples. We would therefore expect the naive classifier
+The test set contains eight incorrect samples. We would therefore expect any naive classifier
 to produce a 60\% accuracy, which we have to beat. In Table~\ref{tab:class_comp},
 we observe that this is indeed the case for all three approaches evaluated here.
+The random forest performed best in this case.
 

### 2020-11-03 02_Paper/paper.tex
robot arm figure.

@@
 \begin{figure}
-       \includestandalone[width=.45\textwidth]{img/cell_data_plot}
-       \caption{Robot arm movement patterns.}
+\caption{The industry simulation cell. \MW{TODO: Find image.}}
+\label{fig:ind_cell}
+\end{figure}
+
+\begin{figure}
+       \includestandalone[width=.45\textwidth]{img/arm_data_plot}
+       \caption{Robot arm movement patterns. We show the movement of the 
+                cell's robot arm, its grippers and an encoding of the overall
+                position in the system. The changes in the grip flag are triggered,
+                when the gripper opens or closes. Zero indicates an open, while
+                one indicates a closed gripper. The position flags marks the state
+                of the cell's arm.  0 means the black disk is in store,
+                one that the black disk is in the gate, two that the white disk
+                is in store and three that the white disk is located in gate.
+             }
+\label{fig:robot_pos_cell}
 \end{figure}
@@
 \subsection{Machine Learning}
+We compare Support Vector Machines (SVM), Multilinear Perceptrons
+\cite{bishop2006pattern} as well as Random forests in the task of
+quality prediction.
 
@@
 
-\subsection{Classifier optimization and testing}
+\subsection{Classifier optimization and testing}\label{sec:ml_exp}
+The robot's position at disc drop is marked in 
+Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
+framed as a classification task. The input vectors which we feed into our
+classifiers consists of the arm positions at the disc drops for both
+discs in three dimensions, as well as the largest recorded belt speed
+of all three belts. The interpretation of the quality measurement is 
+used as the training target. It can be good or bad which we encode as 
+zero and one.
+
 We work with a total of 132 measurements. Each containing arm and belt data
@@
 
+\bibliographystyle{abbrv}
+\bibliography{bib}
+
 \end{document}

### 2020-11-07 02_Paper/paper.tex
experiment text.
worked on section 3: democell

@@
 \section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases
+
+The demonstration cell is a demonstrator representing a general assembly process
+and is essentially composed of assembly lines, a universal robot and a wide
+range of sensor technology. The following use case is implemented:
+shown is a stylized assembly process where two disks are to be stacked on top of each other.
+The quality of the pseudo products is predicted on the basis of the concentricity of both
+parts to be joined and the optimum operating point. The demonstration cell is configured to 
+imitate certain situations that occur in real applications. For example, it is possible to 
+simulate failures in the motors, problems with the conveyor belts or incorrect
+positioning of an object by the robot arm, which causes anomalies in the vibration sensors,
+temperature rise, fluctuations in the air pressure system and other deviations. 
+Due to its manageable size and high scalability,
+findings gained with the demonstration cell can be transferred to various real
+assembly processes and use cases.
+
 \begin{figure}
@@
 }
+
 \section{Methods} %3/4 Page

### 2020-11-08 02_Paper/paper.tex
worked on section 2

@@
 
+The quality control of production processes and products is one part of the general quality management
+and contains the measures and activities needed to fulfill the quality requirements \cite{illés2017new}.
+Currently there are three main concepts: off-line quality control, statistical process control
+and acceptance sampling. Off-line quality control is the first step in the quality control, 
+because it starts in the developing and designing phase of a new product or process. The main goal is
+to select and adjust the process parameters in a way to minimize the deviation between the production outputs
+and the desired results. Thus the process parameters don't have to be determined while production
+begins and the possibility of defect products decrease.
+The statistical process control (SPC) is used for a target-performance comparison. In case of a discrepancy 
+between target and performance, the SPC is taking remedial actions. This concept of quality control
+also provides information on whether a new product can also be produced using the existing production process.
+If a real-time application is needed, e.g. to execute corrective actions due to product quality discrepancies,
+online statistical process control can be used \cite{mitra2016fundamentals}.
+The third concept is represented by the acceptance sampling. 
+...
+The quality characteristics of a product can be classified as variables or attributes.
+Variables are measurable characteristics, which are shown as numbers. On the contrary,
+attributes are not measureable and can only take the value go or no-go. Often, even if the
+quality characteristics of a product are measureable, a go/no-go differentiation is faster and cheaper.
+
 \AP{
@@
 temperature rise, fluctuations in the air pressure system and other deviations. 
-Due to its manageable size and high scalability,
+Due to its manageable size and high degree of scalability,
 findings gained with the demonstration cell can be transferred to various real

### 2020-11-13 02_Paper/paper.tex
Update paper.tex

@@
 
-The demonstration cell is a demonstrator representing a general assembly process
-and is essentially composed of assembly lines, a universal robot and a wide
-range of sensor technology. The following use case is implemented:
-shown is a stylized assembly process where two disks are to be stacked on top of each other.
-The quality of the pseudo products is predicted on the basis of the concentricity of both
-parts to be joined and the optimum operating point. The demonstration cell is configured to 
-imitate certain situations that occur in real applications. For example, it is possible to 
-simulate failures in the motors, problems with the conveyor belts or incorrect
-positioning of an object by the robot arm, which causes anomalies in the vibration sensors,
-temperature rise, fluctuations in the air pressure system and other deviations. 
+In our work we applied a case-based research approach to answer the research question.
+One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance.
+%This sentence can be deleted if needed.
+In addition case-based research approahes have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....).
+%@Lennart: hier müssen entsürechend Beispiele eingetragen werden
+Our case is a production demonstration cell composed of conveyer belts, a universal robot and a wide range of sensor technology.
+The demonstration cell is executing an stylized assembly process where two disks are to be stacked on top of each other.
+The quality of the pseudo products is evaluated via the concentricity of both
+parts to be assembled. The demonstration cell is configured to imitate certain situations that occur in real applications. For example, it is possible to 
+simulate failures in the motors, problems with the conveyor belts or incorrect positioning of an object by the robot arm, which causes anomalies in the vibration sensors, temperature rise, fluctuations in the air pressure system and other deviations.
+Based on the sensor values and process parameters want to predict the concentricity of the assembled parts prior to actual the quality check.
 Due to its manageable size and high degree of scalability,

### 2020-11-13 02_Paper/paper.tex
Update paper.tex

@@
 
-In our work we applied a case-based research approach to answer the research question.
-One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance.
-%This sentence can be deleted if needed.
+In our work we applied a case-based research approach \cite{yin2016case} to answer the research question.
+One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case} %This sentence can be deleted if needed.
 In addition case-based research approahes have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....).
-%@Lennart: hier müssen entsürechend Beispiele eingetragen werden
+%@Lennart: hier müssen entsprechend Beispiele eingetragen werden
 Our case is a production demonstration cell composed of conveyer belts, a universal robot and a wide range of sensor technology.

### 2020-11-13 02_Paper/paper.tex
fix references.

@@
 The quality control of production processes and products is one part of the general quality management
-and contains the measures and activities needed to fulfill the quality requirements \cite{illés2017new}.
+and contains the measures and activities needed to fulfill the quality requirements \cite{illes2017new}.
 Currently there are three main concepts: off-line quality control, statistical process control
@@
 
-In our work we applied a case-based research approach \cite{yin2016case} to answer the research question.
+In our work we applied a case-based research approach \cite{yin2017case} to answer the research question.
 One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case} %This sentence can be deleted if needed.

### 2020-11-14 02_Paper/paper.tex
Worked on section 2.1

@@
 and contains the measures and activities needed to fulfill the quality requirements \cite{illes2017new}.
-Currently there are three main concepts: off-line quality control, statistical process control
-and acceptance sampling. Off-line quality control is the first step in the quality control, 
-because it starts in the developing and designing phase of a new product or process. The main goal is
-to select and adjust the process parameters in a way to minimize the deviation between the production outputs
-and the desired results. Thus the process parameters don't have to be determined while production
-begins and the possibility of defect products decrease.
-The statistical process control (SPC) is used for a target-performance comparison. In case of a discrepancy 
-between target and performance, the SPC is taking remedial actions. This concept of quality control
-also provides information on whether a new product can also be produced using the existing production process.
-If a real-time application is needed, e.g. to execute corrective actions due to product quality discrepancies,
-online statistical process control can be used \cite{mitra2016fundamentals}.
-The third concept is represented by the acceptance sampling. 
-...
+According to Illés, currently there are three etablished tools and methods of quality control \cite{illes2017new}:
+The Statsitical Process Control (SPC), Auditing and Total Quality Control (TQC).   
+The SPC is used for checking the quality of the products with statistical techniques and contains methods like acceptance sampling or
+quality control charts \cite{selvamuthu2018introduction}. it can take place before and after a manufacturing process
+as off-line SPC or implemented in the manufacturing process as in-line SPC.
+With SPC, large batches can be checked, but it is only possible, if the variance of the product quality is small enough,
+to ensure process capability \cite{kahle2013zuverlässigkeitsanalyse}.
+Auditing, in this case especially product and process auditing, is the most fundamental quality control technique. 
+Product and process auditing is the independent examination of product and process quality to provide information. This is executed by
+an independent auditor, based on sampling, or checking records. But the auditor is just reporting incorrect processes or products.
+The required adapting is done by others \cite{fox1993quality}. This is associated with higher costs compared to a quality control
+based on a machine learning model.The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
+by involving all departments of the organization \cite{illes2017new}.
 The quality characteristics of a product can be classified as variables or attributes.
 Variables are measurable characteristics, which are shown as numbers. On the contrary,
-attributes are not measureable and can only take the value go or no-go. Often, even if the
-quality characteristics of a product are measureable, a go/no-go differentiation is faster and cheaper.
+attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
+The advantage of variable measurements are that in the event of a defective intermediate or end product, 
+precise measured values are available, which enable precise adjustment of the process parameters. 
+This allows the desired quality to be restored. With that in mind, a predictive quality control is a promising solution.
 
@@
 In our work we applied a case-based research approach \cite{yin2017case} to answer the research question.
-One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case} %This sentence can be deleted if needed.
-In addition case-based research approahes have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....).
+One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
+%This sentence can be deleted if needed.
+In addition case-based research approaches have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....).
 %@Lennart: hier müssen entsprechend Beispiele eingetragen werden

### 2020-11-16 02_Paper/paper.tex
minor corrections, some questions

@@
 \newcommand{\JG}[1]{{\color{green} {\bf (JG: #1)}}}
-\newcommand{\DSL}[1]{{\color{blue} {\bf (DSL: #1)}}}
+\newcommand{\DSt}[1]{{\color{orange} {\bf (DSt: #1)}}}
 
@@
 \author[b,c]{Jochen Garcke}
-\author[b]{Daniela Steffes-Lai}
+\author[b]{Daniela Steffes-lai}
 \author[b,d]{Moritz Wolter}
@@
 and contains the measures and activities needed to fulfill the quality requirements \cite{illes2017new}.
-According to Illés, currently there are three etablished tools and methods of quality control \cite{illes2017new}:
-The Statsitical Process Control (SPC), Auditing and Total Quality Control (TQC).   
+According to Illés, currently there are three established tools and methods of quality control \cite{illes2017new}:
+The Statistical Process Control (SPC), Auditing, and Total Quality Control (TQC).   
 The SPC is used for checking the quality of the products with statistical techniques and contains methods like acceptance sampling or
-quality control charts \cite{selvamuthu2018introduction}. it can take place before and after a manufacturing process
+quality control charts \cite{selvamuthu2018introduction}. It can take place before and after a manufacturing process
 as off-line SPC or implemented in the manufacturing process as in-line SPC.
 With SPC, large batches can be checked, but it is only possible, if the variance of the product quality is small enough,
-to ensure process capability \cite{kahle2013zuverlässigkeitsanalyse}.
+to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
 Auditing, in this case especially product and process auditing, is the most fundamental quality control technique. 
@@
 attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
-The advantage of variable measurements are that in the event of a defective intermediate or end product, 
+The advantage of variable measurements is that in the event of a defective intermediate or end product, 
 precise measured values are available, which enable precise adjustment of the process parameters. 
@@
 In addition case-based research approaches have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....).
-%@Lennart: hier müssen entsprechend Beispiele eingetragen werden
+% @Lennart: hier müssen entsprechend Beispiele eingetragen werden
 Our case is a production demonstration cell composed of conveyer belts, a universal robot and a wide range of sensor technology.
@@
 simulate failures in the motors, problems with the conveyor belts or incorrect positioning of an object by the robot arm, which causes anomalies in the vibration sensors, temperature rise, fluctuations in the air pressure system and other deviations.
-Based on the sensor values and process parameters want to predict the concentricity of the assembled parts prior to actual the quality check.
+Based on the sensor values and process parameters, we want to predict the concentricity of the assembled parts prior to actual quality check.
 Due to its manageable size and high degree of scalability,
@@
 
-Data  is collected from the demonstration cell and analyzed
+Data  is collected from the demonstration cell and analyzed.
 
 \subsection{Measurement}
+\DSt{
+- what is this section about?
+}
 
@@
 \subsection{Recording the data}
+\DSt{
+- could we include collection via OPCUA server? or manually? 
+}
 
@@
 
+\section*{Acknowledgments}
+This project was partly supported by the german and european IKT.NRW
+project "`ManuBrain"' 
+\DSt{
+do we need to include ManuBrain reference here?
+}
+
 \bibliographystyle{abbrv}

### 2020-11-16 02_Paper/paper.tex
worked on section 2.2 and bib

@@
 
+Predictive analytics discover according to Delen and Damirkan explanatory and predictive patterns which represents 
+the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
+This offers a wide range of applications. In the context of industrial or production enviroments, this includes for example 
+predictive maintenance of machines, the increase of organization performance, production efficiency or improving product design %Quellen einfügen.
+Predictive analytics combined with quality control can be a powerful tool, because it is an improvement compared with the mentioned earlier currently
+etablished quality control methods, in terms of speed, accuracy and time delay.
+%...
+
 \AP{

### 2020-11-17 02_Paper/paper.tex
worked on section 2 and bib.bib

@@
 the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
-This offers a wide range of applications. In the context of industrial or production enviroments, this includes for example 
-predictive maintenance of machines, the increase of organization performance, production efficiency or improving product design %Quellen einfügen.
+This offers a wide range of applications. In the context of industrial or production enviroments, this includes in the areas of Processes, Products and Machines & Assets for example 
+predictive maintenance, product design or optimization of routing and scheduling \cite{krauss2019machine}. 
 Predictive analytics combined with quality control can be a powerful tool, because it is an improvement compared with the mentioned earlier currently
 etablished quality control methods, in terms of speed, accuracy and time delay.
-%...
+So far, only in exceptional cases in the literature is a combination of predictive analytics and quality control found \cite{aumi2012model, ritter1992neue}.
+With regard to general approaches to the use of predictive analytics,
+for example in the form of machine learning in quality prediction, there is a lack in the literature. 
+Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.
+The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
+the collection and processing of the data from the process parameters in continous and a few different ML algorithms are used for prediction, 
+in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
+In addition, it is described in detail how the collected data was collected, prepared and processed.
 
@@
 The demonstration cell is executing an stylized assembly process where two disks are to be stacked on top of each other. 
-The quality of the pseudo products is evaluated via the concentricity of both
-parts to be assembled. The demonstration cell is configured to imitate certain situations that occur in real applications. For example, it is possible to 
-simulate failures in the motors, problems with the conveyor belts or incorrect positioning of an object by the robot arm, which causes anomalies in the vibration sensors, temperature rise, fluctuations in the air pressure system and other deviations.
+The quality of the pseudo products is evaluated via the concentricity of both parts to be assembled. The demonstration cell is configured to imitate certain situations that occur in real applications.
+For example, it is possible to simulate failures in the motors, problems with the conveyor belts or incorrect positioning of an object by the robot arm, which causes anomalies in the vibration sensors,
+temperature rise, fluctuations in the air pressure system and other deviations.
 Based on the sensor values and process parameters, we want to predict the concentricity of the assembled parts prior to actual quality check.

### 2020-11-17 02_Paper/paper.tex
correcting error

@@
 the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
-This offers a wide range of applications. In the context of industrial or production enviroments, this includes in the areas of Processes, Products and Machines & Assets for example 
+This offers a wide range of applications. In the context of industrial or production enviroments, this includes in the areas of Processes, Products and Machines and Assets for example 
 predictive maintenance, product design or optimization of routing and scheduling \cite{krauss2019machine}. 

### 2020-11-24 02_Paper/paper.tex
Demozelle section update

@@
 
-\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases
+\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page
 
@@
 % @Lennart: hier müssen entsprechend Beispiele eingetragen werden
-Our case is a production demonstration cell composed of conveyer belts, a universal robot and a wide range of sensor technology.
-The demonstration cell is executing an stylized assembly process where two disks are to be stacked on top of each other. 
-The quality of the pseudo products is evaluated via the concentricity of both parts to be assembled. The demonstration cell is configured to imitate certain situations that occur in real applications.
-For example, it is possible to simulate failures in the motors, problems with the conveyor belts or incorrect positioning of an object by the robot arm, which causes anomalies in the vibration sensors,
-temperature rise, fluctuations in the air pressure system and other deviations.
-Based on the sensor values and process parameters, we want to predict the concentricity of the assembled parts prior to actual quality check.
-Due to its manageable size and high degree of scalability,
-findings gained with the demonstration cell can be transferred to various real
-assembly processes and use cases.
+\AP{ 
+       - How does the previous sentences apply to the democell?
+       - This suits better in the methods section}
+
+Our case of study is an abstraction of an assembly process at the industry.
+The industry 4.0 demonstration cell is composed by three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200.
+The assembly process done at this demostration cell consist on stacking two disk of different size on the top of each other.
+The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disk.
+If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
+By considering that malfunctions can occurs during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:
+
+\begin{itemize}
+       \item Assemble errors due to robotic arm
+       \item Bearing damage on the conveyor belt
+       \item Resistance on the conveyor belt
+       \item Leakage in the compressed air system
+       \item Productivity limit reached
+       \item Missing material
+\end{itemize}
+
+Those simulated failures have a real impact in the data collected by the sensors.
+Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticiable shifting on pieces' position as well as the stop of the process.
+
+The continous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learching implementations.
+With this in mind, our goal is to predict the quality of the product (concentricity of the assambled parts), prior to the actual quality check done by the laser scanner.
+The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and high degree of scalability.
+This would be an step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assambled pieces.
 
 \begin{figure}
-\caption{The industry simulation cell. \MW{TODO: Find image.}}
+       \includegraphics[width=.45\textwidth]{img/demozelle}
+       \caption{The industry 4.0 demonstration cell at the University of Siegen}
 \label{fig:ind_cell}
@@
 
-\AP{
-What is the demozelle and why it is relevant as study case
-Description of the assemble process in the Demozelle 
-Incl pictures
-}
+\AP{ @Moritz: Why is the figure 2 whithin the area of the Demozelle section?}
 
@@
 
-\AP{explain experiences by doing the research}
+\AP{explain experiences by doing the research
+
+- Connection problem between devices
+- Missing tags  
+- Interpretation of data: preprocessing   
+   - What data is relevant?
+- Data sample size
+- ML implementation @Moritz
+
+}
 

### 2020-11-24 02_Paper/paper.tex
Fixed some grammar issues

@@
 the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
-This offers a wide range of applications. In the context of industrial or production enviroments, this includes in the areas of Processes, Products and Machines and Assets for example 
+This offers a wide range of applications. In the context of industrial or production environments, this includes in the areas of Processes, Products and Machines and Assets for example 
 predictive maintenance, product design or optimization of routing and scheduling \cite{krauss2019machine}. 
-Predictive analytics combined with quality control can be a powerful tool, because it is an improvement compared with the mentioned earlier currently
-etablished quality control methods, in terms of speed, accuracy and time delay.
+Predictive analytics combined with quality control can be a powerful tool because it is an improvement compared with the mentioned earlier currently
+established quality control methods, in terms of speed, accuracy and time delay.
 So far, only in exceptional cases in the literature is a combination of predictive analytics and quality control found \cite{aumi2012model, ritter1992neue}.
@@
 The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
-the collection and processing of the data from the process parameters in continous and a few different ML algorithms are used for prediction, 
+the collection and processing of the data from the process parameters in continuous and a few different ML algorithms are used for prediction, 
 in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
@@
 
+\AP{ - Research Question and research hypotesis}
+
 \section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page
@@
 \AP{ 
-       - How does the previous sentences apply to the democell?
-       - This suits better in the methods section}
+       - To answer the question, we apply a case base research. Then explain 
+}
 
@@
 The industry 4.0 demonstration cell is composed by three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200.
-The assembly process done at this demostration cell consist on stacking two disk of different size on the top of each other.
-The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disk.
+The assembly process done at this demonstration cell consist on stacking two disks of different size on the top of each other.
+The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disks.
 If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
@@
 \begin{itemize}
-       \item Assemble errors due to robotic arm
+       \item Assemble errors due to the robotic arm
        \item Bearing damage on the conveyor belt
@@
 Those simulated failures have a real impact in the data collected by the sensors.
-Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticiable shifting on pieces' position as well as the stop of the process.
+Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticeable shifting on pieces' position as well as the stop of the process.
 
-The continous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learching implementations.
-With this in mind, our goal is to predict the quality of the product (concentricity of the assambled parts), prior to the actual quality check done by the laser scanner.
-The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and high degree of scalability.
-This would be an step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assambled pieces.
+The continuous data collection and the clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations.
+With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner.
+The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and the high degree of scalability.
+This would be a step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.
 
@@
        \caption{Robot arm movement patterns. We show the movement of the 
-                cell's robot arm, its grippers and an encoding of the overall
+                cell's robot arm, its grippers, and the encoding of the overall
                 position in the system. The changes in the grip flag are triggered,
@@
                 of the cell's arm. 0 means the black disk is in store,
-                one that the black disk is in the gate, two that the white disk
-                is in store and three that the white disk is located in gate.
+                one that the black disk is at the gate, two that the white disk
+                is in store and three that the white disk is located at the gate.
              }
@@
 
-\AP{ @Moritz: Why is the figure 2 whithin the area of the Demozelle section?}
+\AP{ @Moritz: Why is figure 2 within the area of the Demozelle section?}
 
@@
 
-\subsection{Recording the data}
+\subsection{Recording the data} %collecting the data
 \DSt{
 - could we include collection via OPCUA server? or manually? 
+}
+
+\AP{
+       - AUExpert manually/ automated
 }
@@
        \end{tabular}
-       \caption{Method comparison for our annomaly detection task 
+       \caption{Method comparison for our anomaly detection task 
                 using the industry demo data test set.}
@@
 - Connection problem between devices
-- Missing tags  
+   - Network connection
+   - Device restriction: SIM4000, SIEMENS. 
+   - Server Timestamp syncr.
+- Missing data tags: modifying PLC and robot code to have tags
 - Interpretation of data: preprocessing
@@
 This project was partly supported by the german and european IKT.NRW
-project "`ManuBrain"' 
+project "ManuBrain"
 \DSt{
 do we need to include ManuBrain reference here?
+}
+\AP{
+Expand EFRE @stn
 }

### 2020-11-25 02_Paper/paper.tex
Update sections: meeting 201125 Moritz and prz

@@
 \newcommand{\LS}[1]{{\color{purple} {\bf (LS: #1)}}}
+\newcommand{\FS}[1]{{\color{cyan} {\bf (FS: #1)}}}
 \newcommand{\MW}[1]{{\color{teal} {\bf (MW: #1)}}}
@@
 
-\begin{figure}
-       \includestandalone[width=.45\textwidth]{img/arm_data_plot}
-       \caption{Robot arm movement patterns. We show the movement of the 
-                cell's robot arm, its grippers, and the encoding of the overall
-                position in the system. The changes in the grip flag are triggered,
-                when the gripper opens or closes. Zero indicates an open, while
-                one indicates a closed gripper. The position flags marks the state
-                of the cell's arm. 0 means the black disk is in store,
-                one that the black disk is at the gate, two that the white disk
-                is in store and three that the white disk is located at the gate.
-             }
-\label{fig:robot_pos_cell}
-\end{figure}
+\section{Machine Learning Methods} %3/4 Page
 
-\AP{ @Moritz: Why is figure 2 within the area of the Demozelle section?}
-
-\section{Methods} %3/4 Page
-
-Data  is collected from the demonstration cell and analyzed.
-
-\subsection{Measurement}
-\DSt{
-- what is this section about?
-}
-
-\subsection{Machine Learning}
 We compare Support Vector Machines (SVM), Multilinear Perceptrons
@@
 \subsection{Classifier optimization and testing}\label{sec:ml_exp}
+
+\begin{figure}
+       \includestandalone[width=.45\textwidth]{img/arm_data_plot}
+       \caption{Robot arm movement patterns. We show the movement of the 
+                cell's robot arm, its grippers, and the encoding of the overall
+                position in the system. The changes in the grip flag are triggered,
+                when the gripper opens or closes. Zero indicates an open, while
+                one indicates a closed gripper. The position flags marks the state
+                of the cell's arm. 0 means the black disk is in store,
+                one that the black disk is at the gate, two that the white disk
+                is in store and three that the white disk is located at the gate.
+             }
+\label{fig:robot_pos_cell}
+\end{figure}
+
 The robot's position at disc drop is marked in 
@@
    - Server Timestamp syncr.
-- Missing data tags: modifying PLC and robot code to have tags
 - Interpretation of data: preprocessing
    - What data is relevant?
-- Data sample size
+   - Missing data tags: modifying PLC and robot code to have tags -> key point
+        - Without label we cannot use supervised ML methods
+- Dataset size
 - ML implementation @Moritz

### 2020-11-25 02_Paper/paper.tex
worked on section 2.1

--- 2020-11-24 02_Paper/paper.tex
@@
 The Statistical Process Control (SPC), Auditing, and Total Quality Control (TQC).   
-The SPC is used for checking the quality of the products with statistical techniques and contains methods like acceptance sampling or
-quality control charts \cite{selvamuthu2018introduction}. It can take place before and after a manufacturing process
+The SPC is used to monitor the production process using recorded data values for the quality characteristics and to indicate any significant changes
+in the quality characteristics in the production process \cite{selvamuthu2018introduction}. It can take place before and after a manufacturing process
 as off-line SPC or implemented in the manufacturing process as in-line SPC.
-With SPC, large batches can be checked, but it is only possible, if the variance of the product quality is small enough,
+With SPC, large batches can be checked, but it is only possible, if the variance of the process parameters and product quality is small enough,
 to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
@@
 Product and process auditing is the independent examination of product and process quality to provide information. This is executed by
-an independent auditor, based on sampling, or checking records. But the auditor is just reporting incorrect processes or products.
-The required adapting is done by others \cite{fox1993quality}. This is associated with higher costs compared to a quality control
-based on a machine learning model.The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
+an independent auditor, based on sampling, or checking records. But the auditor is just reporting incorrect processes or products. The required adapting is done by others \cite{fox1993quality}.
+Both statistical methods and hundred percent controls can be applied as an audit tool.
+Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundert percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
+In the case of a hundred percent control, this is associated with higher costs and higher requirement of time compared to a quality control based on a machine learning model.
+Statistical methods are faster but have the same problem like the SPC: This methods are prone to errors, if the variance of the product quality is to high.
+The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
 by involving all departments of the organization \cite{illes2017new}.

### 2020-11-25 02_Paper/paper.tex
correcting typos

@@
 According to Illés, currently there are three established tools and methods of quality control \cite{illes2017new}:
-The Statistical Process Control (SPC), Auditing, and Total Quality Control (TQC).   
+The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
 The SPC is used to monitor the production process using recorded data values for the quality characteristics and to indicate any significant changes
@@
 as off-line SPC or implemented in the manufacturing process as in-line SPC.
-With SPC, large batches can be checked, but it is only possible, if the variance of the process parameters and product quality is small enough,
+With SPC, large batches can be checked, but it is only possible, if the variance of the process and product parameters is small enough,
 to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
@@
 Both statistical methods and hundred percent controls can be applied as an audit tool.
-Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundert percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
-In the case of a hundred percent control, this is associated with higher costs and higher requirement of time compared to a quality control based on a machine learning model.
-Statistical methods are faster but have the same problem like the SPC: This methods are prone to errors, if the variance of the product quality is to high.
+Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
+In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
+Statistical methods are faster as hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
+if the variance of the product quality is to high.
 The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,

### 2020-11-26 02_Paper/paper.tex
worked on section 2.1
Solve merge issue section LS

@@
 
-\subsection{Quality check in production} % Basic books (find summarize) basic concepts
+\subsection{Quality check in production} \label{sec:qcp} % Basic books (find summarize) basic concepts
 
-The quality control of production processes and products is one part of the general quality management
-and contains the measures and activities needed to fulfill the quality requirements \cite{illes2017new}.
-According to Illés, currently there are three established tools and methods of quality control \cite{illes2017new}:
+The quality control of production processes and products is one fundamental part of the general quality management.
+It contains the measures and activities needed to fulfill specific quality requirements \cite{illes2017new}.
+According to Illés, there are three established tools and methods of quality control \cite{illes2017new}:
 The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
-The SPC is used to monitor the production process using recorded data values for the quality characteristics and to indicate any significant changes
-in the quality characteristics in the production process \cite{selvamuthu2018introduction}. It can take place before and after a manufacturing process
-as off-line SPC or implemented in the manufacturing process as in-line SPC.
-With SPC, large batches can be checked, but it is only possible, if the variance of the process and product parameters is small enough,
-to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
-Auditing, in this case especially product and process auditing, is the most fundamental quality control technique. 
-Product and process auditing is the independent examination of product and process quality to provide information. This is executed by
-an independent auditor, based on sampling, or checking records. But the auditor is just reporting incorrect processes or products. The required adapting is done by others \cite{fox1993quality}.
+The SPC is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes
+in the quality characteristics in the production process \cite{selvamuthu2018introduction}.
+This method can take place right before and/or after a manufacturing process and be implemented as an "off-line" or "in-line" SPC.
+\AP{@Lennart, last sentence is still quite confising to me}
+
+The biggest advantage of working with SPC is that large batches can be checked without major time impact on the QC process, however, this would be only possible if the variance of the process product parameters is small enough, to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
+
+\AP{100\% method is not introduced}
+
+Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
+This method is executed by
+an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
+In a further step, the findings would be later corrected by other than the auditor \cite{fox1993quality}.
+
 Both statistical methods and hundred percent controls can be applied as an audit tool.
+
 Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
+
+While the SPC mostly optimizes the capability of the process, for example the acceptance plan prevents the nonconforming product to be pass and then delivered to the next process or the customer \cite{kurniati2015quality}.
 In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
-Statistical methods are faster as hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
+Statistical methods are faster as \AP{as "or" "than"} hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
 if the variance of the product quality is to high.
@@
 
-Predictive analytics discover according to Delen and Damirkan explanatory and predictive patterns which represents 
-the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
-This offers a wide range of applications. In the context of industrial or production enviroments, this includes in the areas of Processes, Products and Machines and Assets for example 
-predictive maintenance, product design or optimization of routing and scheduling \cite{krauss2019machine}. 
-Predictive analytics combined with quality control can be a powerful tool, because it is an improvement compared with the mentioned earlier currently
-etablished quality control methods, in terms of speed, accuracy and time delay.
-So far, only in exceptional cases in the literature is a combination of predictive analytics and quality control found \cite{aumi2012model, ritter1992neue}.
-With regard to general approaches to the use of predictive analytics,
-for example in the form of machine learning in quality prediction, there is a lack in the literature. 
+According to Delen and Damirkan, predictive analytics (PA) consist on unravel the inherent relationships, if any, between data input and output by using data and mathematical techniques \cite{delen2013data}.
+
+PA offers a wide range of applications, and it can be implemented as long as there is enough data available.
+By conosidering industrial and production environment, PA would be a great asset due to the high flexibility and high amound of data available comming from processes, single machines or cells, producs, and others.
+Some commmon industrial applications of PA at the industry are focused products (design and optimization), machine (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.
+
+Applications that combines PA with QC might be a great improvement in the quality control process because it is an improvement compared with the earlier mentioned methods \ref{sec:qcp}, in terms of speed, accuracy and time delay.
+
+The outcome of an explorative literature review on this matter, shows that the findings that combines PA and QC are very scarce in literature.
+This could be in great part, due to the novelty of the area \cite{aumi2012model, ritter1992neue}.
 Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.
+
+Based on an explorative literature review on this matter, the short outcome is that the findings that combines PA and QC are very scarce in literature.
+This could be in great part, due to computer power limitations in early researchs and the recent increase of ML applications on this area  \cite{aumi2012model, ritter1992neue}.
+Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.
+
+\AP{
+       - Introduce research question
+       - why do we do it?
+       - what do we expect to find or prove
+       - the motivation is clear
+
+       }
+
 The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
@@
 
-\AP{
-Predictive analytics as concepts. Implementation in production
-\begin{itemize}
-       \item Predictive Maintenance
-       \item Scheduling
-       \item Other
-\end{itemize}       
-If happens to be something with P.A. Quality Check
-\begin{itemize}
-       \item	Predictive analytics in production focusing in QA
-       \item	Existing approaches and methods
-\end{itemize}      
-Note: Ideal is to find a gap in the literature, that proves why do we do it and why it is important
-}
+\AP{Last paragraph goes in intro}
 
@@
 
-\begin{figure}
-       \includestandalone[width=.45\textwidth]{img/arm_data_plot}
-       \caption{Robot arm movement patterns. We show the movement of the 
-                cell's robot arm, its grippers and an encoding of the overall
-                position in the system. The changes in the grip flag are triggered,
-                when the gripper opens or closes. Zero indicates an open, while
-                one indicates a closed gripper. The position flags marks the state
-                of the cell's arm. 0 means the black disk is in store,
-                one that the black disk is in the gate, two that the white disk
-                is in store and three that the white disk is located in gate.
-             }
-\label{fig:robot_pos_cell}
-\end{figure}
+\section{Machine Learning Methods} %3/4 Page
 
-\AP{ @Moritz: Why is the figure 2 whithin the area of the Demozelle section?}
-
-\section{Methods} %3/4 Page
-
-Data  is collected from the demonstration cell and analyzed.
-
-\subsection{Measurement}
-\DSt{
-- what is this section about?
-}
-
-\subsection{Machine Learning}
 We compare Support Vector Machines (SVM), Multilinear Perceptrons
@@
 - Connection problem between devices
-- Missing tags  
+   - Network connection
+   - Device restriction: SIM4000, SIEMENS. 
+   - Server Timestamp syncr.
 - Interpretation of data: preprocessing
    - What data is relevant?
-- Data sample size
+   - Missing data tags: modifying PLC and robot code to have tags -> key point
+        - Without label we cannot use supervised ML methods
+- Dataset size
 - ML implementation @Moritz

### 2020-11-26 02_Paper/paper.tex
worked on comments

@@
 in the quality characteristics in the production process \cite{selvamuthu2018introduction}.
-This method can take place right before and/or after a manufacturing process and be implemented as an "off-line" or "in-line" SPC.
+This method can also take place before the actual manufacturing process in form of an "off-line SPC".
+During the designing phase of a process or product,
+off-line SPC procedueres are aiming to select and choose controllable product and process parameters to increase the quality of the outcoming product \cite{mitra2016fundamentals}.
 \AP{@Lennart, last sentence is still quite confising to me}
@@
 \AP{100\% method is not introduced}
-
+The contrary method to any statistical method, is the hundred percent control, where every product is controlled and sorted by being an ok or non-ok part.
 Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
@@
 In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
-Statistical methods are faster as \AP{as "or" "than"} hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
+Statistical methods are faster than hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
 if the variance of the product quality is to high.

### 2020-11-26 02_Paper/paper.tex
fix typos.

@@
 During the designing phase of a process or product,
-off-line SPC procedueres are aiming to select and choose controllable product and process parameters to increase the quality of the outcoming product \cite{mitra2016fundamentals}.
-\AP{@Lennart, last sentence is still quite confising to me}
+off-line SPC procedures are aiming to select and choose controllable product and process parameters to increase the quality of the outcoming product \cite{mitra2016fundamentals}.
+\AP{@Lennart, last sentence is still quite confusing to me}
 
@@
 Variables are measurable characteristics, which are shown as numbers. On the contrary,
-attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
+attributes are not measurable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
 The advantage of variable measurements is that in the event of a defective intermediate or end product, 
 precise measured values are available, which enable precise adjustment of the process parameters. 
-This allows the desired quality to be restored. With that in mind, a predictive quality control is a promising solution.
+This allows the desired quality to be restored. With that in mind, predictive quality control is a promising solution.
 
@@
 PA offers a wide range of applications, and it can be implemented as long as there is enough data available.
-By conosidering industrial and production environment, PA would be a great asset due to the high flexibility and high amound of data available comming from processes, single machines or cells, producs, and others.
-Some commmon industrial applications of PA at the industry are focused products (design and optimization), machine (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.
+By considering industrial and production environment, PA would be a great asset due to the high flexibility and high amound of data available coming from processes, single machines or cells, products, and others.
+Some common industrial applications of PA at the industry are focused products (design and optimization), machine (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.
 
@@
 
-The outcome of an explorative literature review on this matter, shows that the findings that combines PA and QC are very scarce in literature.
+The outcome of an explorative literature review on this matter, shows that the findings that combines PA and QC are very scarce in the literature.
 This could be in great part, due to the novelty of the area \cite{aumi2012model, ritter1992neue}.
@@
 
-Based on an explorative literature review on this matter, the short outcome is that the findings that combines PA and QC are very scarce in literature.
-This could be in great part, due to computer power limitations in early researchs and the recent increase of ML applications on this area  \cite{aumi2012model, ritter1992neue}.
+Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature.
+This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area  \cite{aumi2012model, ritter1992neue}.
 Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.
@@
 Those simulated failures have a real impact in the data collected by the sensors.
-Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticiable shifting on pieces' position as well as the stop of the process.
+Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticeable shifting on pieces' position as well as the stop of the process.
 
-The continous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learching implementations.
-With this in mind, our goal is to predict the quality of the product (concentricity of the assambled parts), prior to the actual quality check done by the laser scanner.
-The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and high degree of scalability.
-This would be an step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assambled pieces.
+The continous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations.
+With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner.
+The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability.
+This would be an step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.
 
@@
 \section*{Acknowledgments}
-This project was partly supported by the german and european IKT.NRW
+This project was partly supported by the German and European IKT.NRW
 project "`ManuBrain"' 

### 2020-11-26 02_Paper/paper.tex
worked on mm methods section.

@@
 If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
-By considering that malfunctions can occurs during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:
+By considering that malfunctions can occur during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:
 
@@
 
-The continous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations.
+The continuous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations.
 With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner.
 The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability.
-This would be an step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.
+This would be a step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.
 
@@
 quality prediction. 
+\subsection{Multilinear perceptrons}
+These feedforward neural networks typically combine multiple layers
+and activation functions. A layer contains a large weight matrix and
+a bias vector. To evaluate the layer the input vector must be
+multiplied with the weight matrix before the bias vector is added.
+Each layer is typically followed by an activation function 
+which adds non-linearity to the network graph. Rectified linear units
+(ReLUs) are zero for negative inputs leave positive inputs unchanged.
+Due to their enormous popularity, we utilize ReLUs here as well.
+Since the linear parts of the ReLU and the linear matrix multiplication
+are differentiable we can employ gradient descent to train our 
+classifier.
+
+\subsection{Support Vector Machines}
+Support Vector Machines offer a convex alternative to MLPs \cite{Suykens2002least}.
+A convex classifier is guaranteed to converge to a global solution regardless 
+of its initialization.
+
+\subsection{Random Forests}
 
@@
 
-We work with a total of 132 measurements. Each containing arm and belt data
-logs of individual cell runs. 20 samples are set aside at random for testing 
-purposes, leaving 112 training samples. The random number generator seed is
-set to one in order to ensure the train and test set splits are identical 
+We work with a total of 528 measurements. Each containing arm and belt data
+logs of individual cell runs. 50 samples are set aside at random for testing 
+purposes, leaving 478 training samples. The random number generator seed is
+set to one to ensure the train and test set splits are identical 
 for all experiments.
@@
 We compare a total of three different classifier architectures on the data.
-A Support Vector Machine (SVM), a multilinear perceptron and a Random Forest
+A Support Vector Machine (SVM), a multilinear perceptron (MLP) and a Random Forest
 structure. All three methods are trained using standard hyperparameters.
@@
        \begin{tabular}{ c c }
-              Support Vector Machine & 95.\% \\
-              Multilinear Perceptron & 95.\% \\
-              Random Forest          & 100.\%
+              Baseline & 64 \% \\
+              Support Vector Machine & 82 \% \\
+              Multilinear Perceptron & 88 \% \\
+              Random Forest          & 98 \%
        \end{tabular}
-       \caption{Method comparison for our annomaly detection task 
-                using the industry demo data test set.}
+       \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
+                Random Forest classification on our annomaly detection task. 
+                The first row shows the performance of naively predicting a broken piece
+                every time.}
        \label{tab:class_comp}
 \end{table}
-Results are shown in table~\ref{tab:class_comp}. For 55 of the total 132 samples
+Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples
 quality measurements indicate a problem. This sets the 
-baseline over the entire data set, that would be obtained by simply labeling all samples
-as good. Over the entire data set, we require to classify more than 58.3\% of the data correctly.
-The test set contains eight incorrect samples. We would therefore expect any naive classifier
-to produce a 60\% accuracy, which we have to beat. In Table~\ref{tab:class_comp},
-we observe that this is indeed the case for all three approaches evaluated here.
-The random forest performed best in this case.
+baseline over the entire data set, which would be obtained by simply labeling all samples
+as faulty. Over the test set, we require to classify more than 64\% of the data correctly.
+We would therefore expect any naive classifier to produce at least 64\% accuracy, which we have to beat.
+In Table~\ref{tab:class_comp}, we observe that this is indeed the case for all three approaches evaluated here.
+We found the random forest performed best followed by the multilinear
+perceptron and the support vector machine.
 
@@
 - Dataset size
-- ML implementation @Moritz
-
-}
+} \\
+\textbf{Machine Learning}; careful measurement and  meaningful preprocessing
+of our cell-date was key to the successful application of all three algorithms.
+Without the labels the problem could not have been framed as a supervised 
+classification problem.
 
@@
 project "`ManuBrain"'
-\DSt{
-do we need to include ManuBrain reference here?
-}
 

### 2020-11-26 02_Paper/paper.tex
talk about svm.

@@
 \usepackage{pgfplots}
+\usepackage{booktabs}
 \usepgfplotslibrary{groupplots}
@@
 We compare Support Vector Machines (SVM), Multilinear Perceptrons
-\cite{bishop2006pattern} as well as Random forests in the task of
-quality prediction. 
-\subsection{Multilinear perceptrons}
+\cite{bishop2006pattern} as well as random forests in the task of
+quality prediction. All three will be introduced next.
+
+\subsection{Multilayer perceptrons}
 These feedforward neural networks typically combine multiple layers
-and activation functions. A layer contains a large weight matrix and
+and activation functions \cite{bishop2006pattern}.
+A layer contains a large weight matrix and
 a bias vector. To evaluate the layer the input vector must be
@@
 (ReLUs) are zero for negative inputs leave positive inputs unchanged.
-Due to their enormous popularity, we utilize ReLUs here as well.
+ReLUs are the recommended activation function for modern neural
+networks \cite{goodfellow2016deep} we use these here as well.
 Since the linear parts of the ReLU and the linear matrix multiplication
@@
 \subsection{Support Vector Machines}
-Support Vector Machines offer a convex alternative to MLPs \cite{Suykens2002least}.
+Support Vector Machines (SVM) offer a convex alternative to MLPs \cite{Suykens2002least}.
 A convex classifier is guaranteed to converge to a global solution regardless 
 of its initialization. 
+The Kernel trick allows SVM to solve non-linear classification problems \cite{Suykens2002least} by mapping implicitly mapping the inputs into a higher feature space.
+Radial basis functions (RBF) are commonly chosen as kernels
+\cite{Suykens2002least} we choose to follow this practice as well.
 
@@
        \centering
-       \begin{tabular}{ c c }
-              Baseline & 64 \% \\
+       \begin{tabular}{ c c } \toprule
+              Approach         & accuracy \\ \midrule
+              Na\"ive-Baseline & 64 \% \\
               Support Vector Machine & 82 \% \\
-              Multilinear Perceptron & 88 \% \\
-              Random Forest          & 98 \%
+              Multilayer Perceptron & 88 \% \\
+              Random Forest          & 98 \% \\ \bottomrule
        \end{tabular}

### 2020-11-27 02_Paper/paper.tex
done for today.
lessons learnt

@@
 During the designing phase of a process or product,
-off-line SPC procedures are aiming to select and choose controllable product and process parameters to increase the quality of the outcoming product \cite{mitra2016fundamentals}.
+off-line SPC procedures are aiming to select and choose a controllable product and process parameters to increase the quality of the outcoming product \cite{mitra2016fundamentals}.
 \AP{@Lennart, last sentence is still quite confusing to me}
@@
 
-\AP{100\% method is not introduced}
-The contrary method to any statistical method, is the hundred percent control, where every product is controlled and sorted by being an ok or non-ok part.
+The contrary method to any statistical method, is the hundred percent control, where every product is controlled and binary sorted as an OK or Non-OK part.
 Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
@@
 \subsection{Random Forests}
+Random Forests \cite{breiman2001random} \MW{Will finish tomorrow.}
 
@@
 
-\AP{explain experiences by doing the research
+\textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data within each other due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture.
+To overcome the situation stated above, it was necessary to reprogram big sections of the machine control system.
 
-- Connection problem between devices
-   - Network connection
-   - Device restriction: SIM4000, SIEMENS. 
-   - Server Timestamp syncr.
-- Interpretation of data: preprocessing
-   - What data is relevant?
-   - Missing data tags: modifying PLC and robot code to have tags -> key point
-        - Without label we cannot use supervised ML methods
-- Dataset size
-} \\
+\textbf{Data synchronization}; two OPC-UA servers were used on this implementation. This lead to a series of data synchronization problems due to differences on the internal clock of both servers.
+In order to solve the issue, it was needed to write a time-stamp synchronization script that was deployed during the data preprocessing phase.
+Without harmonious time-stamps, the input data for the ML model would have been useless and the model inaccurate.
+
+\textbf{Data interpretation}; complex, time-consuming, and fundamental step on any ML applications.
+It is fundamental to understand the assembly process, the timing from the machine movements, the boundaries of the machine's sensors, as well of a basic correlation within the presented data.
+
+\textbf{Missing values}; in order to minimize the risk of false results delivered by the ML model, it would be compulsory to carefully review the ML input data.
+Missing values can have a great impact in the ML prediction, that is the reason why we deliberately review all the input data and validate it with the expected output from the diverse sensors.
+Whenever there was missing data, and as long as we did not fabricate data, we employed statistical methods to fill the data gap.
+
+\textbf{Adapting the industry 4.0 demonstration cell}; the initial state of the demonstrator was very limited.
+Even though the process was well known, the lack of labels or flags whenever certain actions occurs, made complicated to have accurate data sampling from each assembly cycle.
+In order to overcome this uncertainty, we modify the machine program to raise specify flags whenever certain actions would be executed.
+
 \textbf{Machine Learning}; careful measurement and  meaningful preprocessing
@@
 classification problem.
+
+\textbf{Dataset size}; as the starting point we collected as many data points as the ones found in the iris Dataset \cite{fisher_1936}.
+The next step was to double the samples, until we progressively increased the dataset size by indexing the new samples to the older data.
 

### 2020-11-27 02_Paper/paper.tex
chapter 5
Chapter 1, 2, 6
chapter 2

@@
 
+The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
+the collection and processing of the data from the process parameters in continuous and a few different ML algorithms are used for prediction, 
+in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
+In addition, it is described in detail how the collected data was collected, prepared and processed.
+
 \section{Related Works} % 1 Page \Lennart
@@
 
-The quality control of production processes and products is one fundamental part of the general quality management.
+The quality control of production processes and products is one fundamental part of general quality management.
 It contains the measures and activities needed to fulfill specific quality requirements \cite{illes2017new}.
@@
 The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
-The SPC is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes
-in the quality characteristics in the production process \cite{selvamuthu2018introduction}.
-This method can also take place before the actual manufacturing process in form of an "off-line SPC".
-During the designing phase of a process or product,
-off-line SPC procedures are aiming to select and choose a controllable product and process parameters to increase the quality of the outcoming product \cite{mitra2016fundamentals}.
-\AP{@Lennart, last sentence is still quite confusing to me}
+The SPC is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes in the quality characteristics in the production process \cite{selvamuthu2018introduction}.
+SPC methods can also take place before the actual manufacturing process, this is commonly known as "off-line SPC".
+
+During the design phase of a process or product, off-line SPC procedures are deployed.
+Those procedures aim to increase the quality of the outcoming product by choosing controllable products and  process parameter \cite{mitra2016fundamentals}.
 
@@
 
-The contrary method to any statistical method, is the hundred percent control, where every product is controlled and binary sorted as an OK or Non-OK part.
+Another conservative technique to perform the quality check would be to check 100\% of the produced parts.
+On this method, every product is controlled and binary sorted as an OK or Non-OK part.
+However, this has the disadvantage of high cost related to personal or specialized material and in certain cases, could lead to a delay in production.
+
 Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
@@
 an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
-In a further step, the findings would be later corrected by other than the auditor \cite{fox1993quality}.
+In a further step, the findings would be later corrected by other person than the auditor \cite{fox1993quality}.
 
-Both statistical methods and hundred percent controls can be applied as an audit tool.
+%Both statistical methods and hundred percent controls can be applied as an audit tool.
 
@@
 In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
-Statistical methods are faster than hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
-if the variance of the product quality is to high.
-The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
-by involving all departments of the organization \cite{illes2017new}.
+Generally, statistical methods are faster than hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
+those assumptions might lead to errors if the variance of the product quality higher than expected.
+
+The concept of TQC is to extend the scope of quality control to the whole company and product life cycle, by involving all departments of the organization \cite{illes2017new}.
 The quality characteristics of a product can be classified as variables or attributes.
-Variables are measurable characteristics, which are shown as numbers. On the contrary,
-attributes are not measurable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
-The advantage of variable measurements is that in the event of a defective intermediate or end product, 
-precise measured values are available, which enable precise adjustment of the process parameters. 
+Variables are measurable characteristics, which are shown as numbers.
+On the contrary, attributes are not measurable and can only take the binary values like "go" or "no-go" \cite{mitra2016fundamentals}.
+The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters.
 This allows the desired quality to be restored. With that in mind, predictive quality control is a promising solution.
-
-\AP{
-\begin{itemize}
-\item How quality check is done in production
-\item Concepts and sampling plan
-\item Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]
-\end{itemize}}
 
@@
 
-According to Delen and Damirkan, predictive analytics (PA) consist on unravel the inherent relationships, if any, between data input and output by using data and mathematical techniques \cite{delen2013data}.
+According to Delen and Damirkan, predictive analytics (PA) consist on unravel the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
 
 PA offers a wide range of applications, and it can be implemented as long as there is enough data available.
-By considering industrial and production environment, PA would be a great asset due to the high flexibility and high amound of data available coming from processes, single machines or cells, products, and others.
-Some common industrial applications of PA at the industry are focused products (design and optimization), machine (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.
+By considering the industrial and production environment, PA would be a great asset due to the high flexibility and high amount of data available coming from processes, single machines or cells, products, and others.
+Some common industrial applications of PA at the industry are focused products (design and optimization), machines (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.
 
@@
 Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature.
-This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area  \cite{aumi2012model, ritter1992neue}.
-Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.
+This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area.
+Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated}; product quality prediction in a process chain \cite{krauss2019machine}; model development for predictive quality control of batch processes \cite{aumi2012model}; and ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}
 
@@
        }
-
-The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
-the collection and processing of the data from the process parameters in continuous and a few different ML algorithms are used for prediction, 
-in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
-In addition, it is described in detail how the collected data was collected, prepared and processed.
-
-\AP{Last paragraph goes in intro}
 
@@
 
-\subsection{Recording the data}
+\subsection{Data acquisition}
 \DSt{
@@
 
-\section{Conclusion} % 1/2 Page
-
 \section*{Acknowledgments}

### 2020-11-27 02_Paper/paper.tex
confusion matrix idea.

--- 2020-11-27 02_Paper/paper.tex
@@
 
-\AP{
-\begin{itemize}
-\item How quality check is done in production
-\item Concepts and sampling plan
-\item Attributive vs Variable measurements [VM has higher measurement accuracy, reason why it’s better to use regression model]
-\end{itemize}}
-
 \subsection{Predictive analytics in production}
@@
        }
-
-The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
-the collection and processing of the data from the process parameters in continuous and a few different ML algorithms are used for prediction, 
-in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
-In addition, it is described in detail how the collected data was collected, prepared and processed.
-
-\AP{Last paragraph goes in intro}
-
 \section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page
@@
 \end{table}
+
+\begin{figure}
+\caption{\MW{TODO: Add confusion matrix.}}
+\end{figure}
+
 Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples
@@
 In Table~\ref{tab:class_comp}, we observe that this is indeed the case for all three approaches evaluated here.
+\MW{discuss confusion matrix.}
 We found the random forest performed best followed by the multilinear

### 2020-11-30 02_Paper/paper.tex
Chapter 2

@@
 This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area.
-Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated}; product quality prediction in a process chain \cite{krauss2019machine}; model development for predictive quality control of batch processes \cite{aumi2012model}; and ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}
-
-\AP{
-       - Introduce research question
-       - why do we do it?
-       - what do we expect to find or prove
-       - the motivation is clear
-
-       }
+Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated}; product quality prediction in a process chain \cite{krauss2019machine}; model development for predictive quality control of batch processes \cite{aumi2012model}; and ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}.
+Considering the lack of literature, our goal is to decrease this gap on the research area by implementing a functional predictive model in quality assurance for an assembly process and describing the lesson learned during this implementation.
 

### 2020-11-30 02_Paper/paper.tex
Chapter 3
ideas for introduction

@@
 
+Product features such as reliability and durability or complete functionality determine to a large extent the success and profit of a company on the market.
+In addition, product quality is a company's showcase. Therefore, the established standard must be ensured by careful quality assurance.
+Traditional methods of quality control, such as 100\% control, may conflict with other production goals, such as production speed and low reject rates.
+When choosing the right quality control tools, a compromise must be made in most cases. For example, a higher production speed requires statistical quality control. Statistical methods, however,
+do not provide one hundred percent certainty that the required product quality will be achieved.
+A new approach based on quality prediction using ML algorithms provides a remedy here.
+
 The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
@@
        - This suits better in the methods section}
+       - Review
 

### 2020-11-30 02_Paper/paper.tex
more on the trees.

@@
 
-\subsection{Random Forests}
-Random Forests \cite{breiman2001random} \MW{Will finish tomorrow.}
+\subsection{Decision Tree}
+Decision trees are binary trees, these binary trees work with the input
+features at the roots, resulting decisions are found by moving
+trough the tree to top leaves. At every branch in the tree a decision
+is made, until one arrives at the final conclusion \cite{Marsland2015Machine}.
+Decision trees are trained using  
+\MW{Will write more tomorrow.}
 
@@
               Multilayer Perceptron & 88 \% \\
-              Random Forest          & 98 \% \\ \bottomrule
+              Decision Tree         & 98 \% \\ \bottomrule
        \end{tabular}

### 2020-12-01 02_Paper/paper.tex
Chapter 5

--- 2020-11-30 02_Paper/paper.tex
@@
 The assembly process done at this demonstration cell consist on stacking two disks of different size on the top of each other.
-The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disks.
+The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disks Figure~\ref{fig:ind_cell}.
 If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
@@
 }
+
+Industrial projects requires to work with a variety of sensors and controllers.
+Thus, it might occurs incompatibility between technologies.
+In order to avoid that problem, universal protocols are often found at industrial projects.
+The industrial 4.0 demonstration cell data is shared via protocol OPC-UA.
+The Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram between sensors and controllers.
+
+\begin{figure}
+       \includegraphics[width=.45\textwidth]{img/demozelle_conex_diagram.png}
+       \caption{Industry 4.0 demostration cell: Connection diagram (simplified)
+             }
+\label{fig:demo_conn_diag}
+\end{figure}
 

### 2020-12-01 02_Paper/paper.tex
Chapter 5

@@
 \usepackage{booktabs}
+\usepackage{adjustbox}
 \usepgfplotslibrary{groupplots}
@@
 \subsection{Data acquisition}
-\DSt{
-- could we include collection via OPCUA server? or manually? 
-}
 
@@
 Thus, it might occurs incompatibility between technologies.
-In order to avoid that problem, universal protocols are often found at industrial projects.
-The industrial 4.0 demonstration cell data is shared via protocol OPC-UA.
-The Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram between sensors and controllers.
+In order to avoid that problem, universal protocols are often implemented at industrial projects.
+This is the case for our industrial 4.0 demonstration cell, which shares data via protocol OPC-UA.
+
+Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell.
+For our case, the data is shared independently from two OPC-UA servers.
+This in order to represent the interaction between multiple servers in real production environments.
+
+The first step to collect the data is to list all the variables of interest and to map their source, see Table.~\ref{tab:data_source} . For this research, we focussed on the following data:
+
+\begin{table}
+       \centering
+       \begin{adjustbox}{width=.45\textwidth}
+       \begin{tabular}{ c c c } \toprule
+              \textbf{Data of interest} & \textbf{Server Source} & \textbf{Variable}\\ \midrule
+              Conveyor speed       & Siemens PLC       & \begin{minipage}[c]{0.4\textwidth}
+              \begin{description}
+                     \item Conveyor-Gate 1
+                     \item Conveyor-QC 2
+                     \item Conveyor-Store/Magazine
+                     \end{description}
+                     \end{minipage} \\
+              UR3 Position         & Siemens PLC       & \begin{minipage}[c]{0.4\textwidth}
+              \begin{description}
+                     \item $xyz$ Gripper position
+                     \end{description}
+                     \end{minipage} \\ 
+              Action Flags         & Siemens PLC       & \begin{minipage}[c]{0.4\textwidth}
+              \begin{description}
+                     \item UR3 gripper open/close
+                     \item Grab/drop disk based on disk type
+                     \end{description}
+                     \end{minipage} \\
+              Quality control      & SICK SIM4000      & \begin{minipage}[c]{0.4\textwidth}
+              \begin{description}
+                     \item OK-NOK label
+                     \item $xy$ disk deviation from center point
+                     \item absolute disk deviation
+                     \end{description}
+                     \end{minipage} \\
+              Gate position        & SICK SIM4000      & \begin{minipage}[c]{0.4\textwidth}
+              \begin{description}
+                     \item Position
+                     \item Speed
+                     \item Safe to go
+                     \end{description}
+                     \end{minipage} \\
+              Store/Magazine       & SICK SIM4000      & \begin{minipage}[c]{0.4\textwidth}
+                     \begin{description}
+                     \item Disk Size
+                     \end{description}
+                   \end{minipage} \\ \bottomrule
+       \end{tabular}
+       \end{adjustbox}
+       \caption{Industriy 4.0 demonstration cell: Relevant data with its reference source server}
+       \label{tab:data_source}
+\end{table}
+
+The data was collected manually by using the software "UAExperts"
 

### 2020-12-01 02_Paper/paper.tex
Chapter 5

@@
 
-The first step to collect the data is to list all the variables of interest and to map their source, see Table.~\ref{tab:data_source} . For this research, we focussed on the following data:
+The first step to collect the data is to list all the variables of interest and to map their source.
+The second step is to determine the use cases of interest.
+On this research, we focussed on the data described on Table.~\ref{tab:data_source} and the six use cases described on Table.~\ref{tab:use_cases}.
+The data was manually collected by using the software "UAExperts".
+Aproximately 15 hours of data was collected, by equally sampling each use case during the data acquisition time.
 
@@
               \textbf{Data of interest} & \textbf{Server Source} & \textbf{Variable}\\ \midrule
-              Conveyor speed       & Siemens PLC       & \begin{minipage}[c]{0.4\textwidth}
+              Conveyor speed       & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
               \begin{description}
-                     \item Conveyor-Gate 1
-                     \item Conveyor-QC 2
-                     \item Conveyor-Store/Magazine
+                     \item Conveyor: Gate
+                     \item Conveyor: QC
+                     \item Conveyor: Store
                      \end{description}
-                     \end{minipage} \\
-              UR3 Position         & Siemens PLC       & \begin{minipage}[c]{0.4\textwidth}
+                     \end{minipage} \\ \hline
+              UR3 Position         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
               \begin{description}
@@
                      \end{description}
-                     \end{minipage} \\ 
-              Action Flags         & Siemens PLC       & \begin{minipage}[c]{0.4\textwidth}
+                     \end{minipage} \\ \hline
+              Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
               \begin{description}
@@
                      \end{description}
-                     \end{minipage} \\
-              Quality control      & SICK SIM4000      & \begin{minipage}[c]{0.4\textwidth}
+                     \end{minipage} \\ \hline
+              Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
               \begin{description}
@@
                      \item $xy$ disk deviation from center point
-                     \item absolute disk deviation
+                     \item Absolute disk deviation
                      \end{description}
-                     \end{minipage} \\
-              Gate position        & SICK SIM4000      & \begin{minipage}[c]{0.4\textwidth}
+                     \end{minipage} \\ \hline
+              Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
               \begin{description}
@@
                      \end{description}
-                     \end{minipage} \\
-              Store/Magazine       & SICK SIM4000      & \begin{minipage}[c]{0.4\textwidth}
+                     \end{minipage} \\ \hline
+              Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
                      \begin{description}
@@
 
-The data was collected manually by using the software "UAExperts"
+\begin{table}
+       \centering
+       \begin{tabular}{ c c } \toprule
+              Use Case        & Description \\ \midrule
+              Use Case 1  & \begin{minipage}[t]{0.25\textwidth}
+                            \begin{description}
+                                   \item Conveyor speed: Slow
+                                   \item Robot position: OK
+                            \end{description}
+                            \end{minipage}  \\ \hline
+              Use Case 2  & \begin{minipage}[t]{0.25\textwidth}
+                            \begin{description}
+                                   \item Conveyor speed: Slow
+                                   \item Robot position: NOK
+                            \end{description}
+                            \end{minipage}  \\ \hline
+              Use Case 3  & \begin{minipage}[t]{0.25\textwidth}
+                            \begin{description}
+                                   \item Conveyor speed: Fast
+                                   \item Robot position: OK
+                            \end{description}
+                            \end{minipage}  \\ \hline
+              Use Case 4  & \begin{minipage}[t]{0.25\textwidth}
+                            \begin{description}
+                                   \item Conveyor speed: Fast
+                                   \item Robot position: NOK
+                            \end{description}
+                            \end{minipage}  \\ \hline
+              Use Case 5  & \begin{minipage}[t]{0.25\textwidth}
+                            \begin{description}
+                                   \item Conveyor speed: Too Fast
+                                   \item Robot position: OK
+                            \end{description}
+                            \end{minipage}  \\ \hline
+              Use Case 6  & \begin{minipage}[t]{0.25\textwidth}
+                            \begin{description}
+                                   \item Conveyor speed: Too Fast
+                                   \item Robot position: NOK
+                            \end{description}
+                            \end{minipage}  \\ \bottomrule
+       \end{tabular}
+       \caption{Industrial 4.0 demostration cell: Controlled use-cases.
+       Use cases with Robot position: NOK and Conveyor speed: Too Fast will result in NOK pieces.}
+       \label{tab:use_cases}
+\end{table}
 
@@
 \end{figure}
+
+\subsection{Data preprocessing}
+
+Once enough data is collected, the next step is to clean the raw data and organize it accordingly.
+For our case, that means to merge the data collected from the two OPC-UA servers, synchronize the time stamps.
+Since our systems are not completely synchronized, it was needed to calculate the delta-time based between servers based on the base clock from each server.
+Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.
+
+Data tags interpretation is an important step in the preprocessing process.
+The raw data collected from the sensors is sometimes tagged by an alphanumeric code.
+In order to work with the data, it was needed to implement diverse functions wich have the task to clean the raw data in a more human-readable form.
+This means to remove samples out of clear boundaries and missing values, as well as to translate the sensors code based in a predefined dictionary settle by the authors.
+This last step, could be optional in other implementations, however, it proves to be a great addition for testing purposes.
+
+Once the data is clean and compiled in one directory, the next step would be to split the data based on the assembly cycle.
+For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset \ref{tab:data_source}.
+Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so.
+At this point we have a series de data-samples, which each of them is based in time series.
+However, we are not interested in a time series analysis, therefore it would be needed to compress each time-series based data-sample in an atemporal data-sample.
+
+To eliminate time as a variable in our dataset, we defined a series of rules:
+
+\begin{itemize}
+       \item Robot position ($xyz$) while dropping the disk in the storage area
+       \item Mean conveyor speed per conveyor band
+       \item Absolute deviation ($xy$) at the quality control check
+       \item Absolute quality check result: OK - NOK
+\end{itemize}
+
+Each time-series sample was evaluated based on the rules stated above, and the result of each evaluation was considered as our atemporal data-sample, which would be used by our classifier.
 

### 2020-12-01 02_Paper/paper.tex
Conclusion

@@
 
+Quality assurance is an important topic in production.
+Quality assurance methods in production might diverge one from each other, however, all of them seek to prove the product quality in one way or another.
+
+Based on the literature review, we observed that the hundred percent quality check method proves to be the most efficient method to guarantee the final product quality, however, the high implementation cost is its biggest draw back.
+On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each individual product until the next bach review might imply a considerable loss whenever NOK products are found.
+This based in the uncertainty of when did the error occurs and how many products are affected.
+
+By implementing ML models capable to predict the quality of the product, just by the initial conditions of the process would be a great asset for the industrial processes.
+Within the limits of our work, we are able to predict with 98\% certainty the product quality by implementing a supported-vector-machine with a 6-variables vector as input.
+For further work, we expect to increase the certainty of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.
+
+It is important to state that this prediction model is not yet ready to fully replace the statistical methods, not the hundred percent quality check method.
+However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this will somehow compensate one of the disadvantages from statistical methods.
+
+It is worth to mention the most important points learned during the project implementation. This might help as building blocks for further research in the area.
+
 \subsection{Lesson Learned} % 1/2 Page

### 2020-12-01 02_Paper/paper.tex
Chapter 3

@@
 
+This paper is divided in 6 sections:
+
+\begin{itemize}
+       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
+       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
+       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project.
+It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
+       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
+       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
+       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
+\end{itemize}
+
 \section{Related Works} % 1 Page \Lennart
@@
 an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
-In a further step, the findings would be later corrected by other person than the auditor \cite{fox1993quality}.
+In a further step, the findings would be later corrected by another person rather than the auditor \cite{fox1993quality}.
 
@@
 
-Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
+Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and the hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
 
@@
 In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
-Generally, statistical methods are faster than hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
+Generally, statistical methods are faster than the hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
 those assumptions might lead to errors if the variance of the product quality higher than expected.
@@
 Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated}; product quality prediction in a process chain \cite{krauss2019machine}; model development for predictive quality control of batch processes \cite{aumi2012model}; and ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}.
-Considering the lack of literature, our goal is to decrease this gap on the research area by implementing a functional predictive model in quality assurance for an assembly process and describing the lesson learned during this implementation.
+Considering the lack of literature, our goal is to decrease this gap on the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation.
 
@@
 
-In our work we applied a case-based research approach \cite{yin2017case} to answer the research question. 
+To test our theories, we need to select the right testing platform.
+This platform should represent real industrial applications and be able to handle a certain level of complexity.
+In our work, we applied a case-based research approach \cite{yin2017case} in order to answer the research question.
 One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
 %This sentence can be deleted if needed.
-In addition case-based research approaches have already been successfully applied in the area of quality prediction based on process parameters (see, for example, ....).
-% @Lennart: hier müssen entsprechend Beispiele eingetragen werden
-\AP{ 
-       - How does the previous sentences apply to the democell?
-       - This suits better in the methods section}
-       - Review
 
@@
 
-The continuous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations.
+The continuous data collection and the clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations.
 With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner.
@@
 The data was manually collected by using the software "UAExperts".
-Aproximately 15 hours of data was collected, by equally sampling each use case during the data acquisition time.
+Approximately 15 hours of data was collected, by equally sampling each use case during the data acquisition time.
 
@@
                      \item OK-NOK label
-                     \item $xy$ disk deviation from center point
+                     \item $xy$ disk deviation from the center point
                      \item Absolute disk deviation
@@
        \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
-                Random Forest classification on our annomaly detection task. 
+                Random Forest classification on our anomaly detection task. 
                 The first row shows the performance of naively predicting a broken piece

### 2020-12-01 02_Paper/paper.tex
Introduction

@@
 
-\AP{\begin{itemize}
-       \item	Products’ quality must always be guaranteed.
-       \item	In certain cases (especially in series assembly production) there is a delay between quality inspection
-              and end of the production process high potential for producing scrap 
-       \item	By doing quality inspection based on samples, there is still a risk of sending NOK parts to customers
-       \item	The cost of quality checks might be expensive
-       \item	Quality assurance is normally done at the end of production (for assembly processes)   
-       \item	Early prediction of the production’s quality  would help to decrease the amount of scrap  and the risk of sending NOK parts to customers
-       \item	Variable predictions by using machine learning models is currently widely used in diverse fields due to its accurate predictions with the data collected from the machines, 
-              prediction models can be implemented for specific predicted values
-\end{itemize}}
+Product features such as reliability, durability, or complete functionality determine to a large extent the success and profit of companies on the market.
+That is why it is highly important for companies to ensure that every product meet the expected requirements.
+Throughout the years, diverse methods for quality control (QC) have been presented and implemented in production.
+Some of those methods prove to be highly effective, but costly, i.e.
+the revision of every produced piece, either by automated or manual methods, or by doing quality inspections based on a portion of the produced pieces and extend the results based on statistical methods.
+Which still has a considerable risk of not detecting NOK parts and sending them to costumers \cite{mitra2016fundamentals, fox1993quality, kahle2013zuverlaessigkeitsanalyse}.
 
-Product features such as reliability and durability or complete functionality determine to a large extent the success and profit of a company on the market.
-In addition, product quality is a company's showcase. Therefore, the established standard must be ensured by careful quality assurance.
-Traditional methods of quality control, such as 100\% control, may conflict with other production goals, such as production speed and low reject rates.
-When choosing the right quality control tools, a compromise must be made in most cases. For example, a higher production speed requires statistical quality control. Statistical methods, however,
-do not provide one hundred percent certainty that the required product quality will be achieved.
-A new approach based on quality prediction using ML algorithms provides a remedy here.
+Whenever a QC method is selected, it is important to remark that compromises must be made in most cases.
+For example, traditional methods like controlling every produced piece might affect the production goals by delaying the production speed at the cost of lower rejection rates On the other hand, higher production speeds normally requires statistical quality control methods.
+However, those methods do not provide one hundred percent certainty that the required product quality will be achieved \cite{selvamuthu2018introduction, kurniati2015quality}.
 
-The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
-the collection and processing of the data from the process parameters in continuous and a few different ML algorithms are used for prediction, 
-in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
-In addition, it is described in detail how the collected data was collected, prepared and processed.
+With the evolution of machine learning (ML) applications, we expect to enhance the QC by predicting the product quality at the initial stage of production.
+This will not only reduce cost in production, and strengthen the QC process, it will also be part of the predictive analytics tools found in production, which is currently widely used in diverse fields due to its accurate predictions \cite{bishop2006pattern, krauss2019machine}.
 

### 2020-12-01 02_Paper/paper.tex
lesons learnt
Added confusion matrix

@@
 \usepackage{adjustbox}
+\usepackage{multirow}
+\usepackage{caption}
+\usepackage{subcaption}
 \usepgfplotslibrary{groupplots}
@@
 code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
+
 \begin{table}
@@
 
-\begin{figure}
-\caption{\MW{TODO: Add confusion matrix.}}
-\end{figure}
+\begin{table}
+       \begin{subtable}[h]{0.3\textwidth}
+              \centering
+              \begin{adjustbox}{width=1.6\textwidth}
+              \begin{tabular}{l|l|c|c|c}
+                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
+                     \cline{3-4}
+                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
+                     \cline{2-4}
+                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
+                     \cline{2-4}
+                     & NOK & $8$ & $24$ & $8+24 = 32$\\
+                     \cline{2-4}
+                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+8 = 26$} & \multicolumn{    1}{c}{$0+24 = 24$} & \multicolumn{1}{c}{$50$}\\
+              \end{tabular}
+              \end{adjustbox}
+              \caption{SVM.}
+              \label{tab:SVM_conf_matrix}
+       \end{subtable}
+       \begin{subtable}[h]{0.3\textwidth}
+              \centering
+              \begin{adjustbox}{width=1.6\textwidth}
+              \begin{tabular}{l|l|c|c|c}
+                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
+                     \cline{3-4}
+                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
+                     \cline{2-4}
+                     \multirow{2}{*}{Predicted Values}& OK & $18$ & $0$ & $18+0 = 18$\\
+                     \cline{2-4}
+                     & NOK & $6$ & $26$ & $6+26 = 32$\\
+                     \cline{2-4}
+                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$18+6 = 24$} & \multicolumn{    1}{c}{$0+26 = 26$} & \multicolumn{1}{c}{$50$}\\
+              \end{tabular}
+              \end{adjustbox}
+              \caption{MLP.}
+              \label{tab:MPL_conf_matrix}
+       \end{subtable}
+       \begin{subtable}[h]{0.3\textwidth}
+              \centering
+              \begin{adjustbox}{width=1.6\textwidth}
+              \begin{tabular}{l|l|c|c|c}
+                     \multicolumn{2}{c}{}&\multicolumn{2}{c}{True Values}&\\
+                     \cline{3-4}
+                     \multicolumn{2}{c|}{}& OK & NOK &\multicolumn{1}{c}{Total}\\
+                     \cline{2-4}
+                     \multirow{2}{*}{Predicted Values}& OK & $17$ & $1$ & $17+1 = 18$\\
+                     \cline{2-4}
+                     & NOK & $0$ & $32$ & $0+32 = 32$\\
+                     \cline{2-4}
+                     \multicolumn{1}{c}{} & \multicolumn{1}{c}{Total} & \multicolumn{1}{c}{$17+0 = 17$} & \multicolumn{    1}{c}{$1+32 = 33$} & \multicolumn{1}{c}{$50$}\\
+              \end{tabular}
+              \end{adjustbox}
+              \caption{Decision Tree.}
+              \label{tab:Tree_conf_matrix}
+       \end{subtable}
+       \caption{Confusion matrix result of the prediction of 50 data-points.}
+       \label{tab:Confusion_matrix}
+\end{table}
 
@@
 In Table~\ref{tab:class_comp}, we observe that this is indeed the case for all three approaches evaluated here.
-\MW{discuss confusion matrix.}
+
+Based on the MLP prediction results presented on Table.~\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
+The false-negative results represents the 12\% of the test sample and the true predictions constitute a 88\% of the test data.
+
+Based on the prediction results presented on Table,~\subref{tab:SVM_conf_matrix , tab:MPL_conf_matrix, tab:Tree_conf_matrix}
+
 We found the random forest performed best followed by the multilinear
@@
 \textbf{Dataset size}; as the starting point we collected as many data points as the ones found in the iris Dataset \cite{fisher_1936}.
-The next step was to double the samples, until we progressively increased the dataset size by indexing the new samples to the older data.
+The next step was to collect batches of data of around 30 minutes per use case.
+This process was repeated until accumulate around 15 hours of data.
 

### 2020-12-01 02_Paper/paper.tex
Include confusion matrix in conclusion

@@
 
-Based on the prediction results presented on Table,~\subref{tab:SVM_conf_matrix , tab:MPL_conf_matrix, tab:Tree_conf_matrix}
-
-We found the random forest performed best followed by the multilinear
-perceptron and the support vector machine.
+The outcome of the models shows that the random forest performed best followed by the multilinear perceptron and the support vector machine.
+However, by reviewing the confusion matrices presented on Table,~\ref{tab:Confusion_matrix}, multilinear perceptron would be the option of choice to be implemented at industrial applications due to the 0\% ratio in false-positive results.
 
@@
 By implementing ML models capable to predict the quality of the product, just by the initial conditions of the process would be a great asset for the industrial processes.
-Within the limits of our work, we are able to predict with 98\% certainty the product quality by implementing a supported-vector-machine with a 6-variables vector as input.
+Within the limits of our work, we are able to predict with 98\% certainty the product quality by implementing a decision tree model with a 6-variables vector as input.
+However, our decision for industrial applications would be the MLP with 88\% accuracy as to guarantee the QC and avoid labeling a NOK piece as OK.
 For further work, we expect to increase the certainty of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.

### 2020-12-01 02_Paper/paper.tex
Confusion matrix

@@
        \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
-       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
+       \item \textbf{Conclusion}, express the remarks and diskoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
 \end{itemize}
@@
 Once the data is clean and compiled in one directory, the next step would be to split the data based on the assembly cycle.
-For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset \ref{tab:data_source}.
-Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so.
+For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}.
+Subsequently, each data-sample is automatically checked for missing sensor values and diskarded if so.
 At this point we have a series de data-samples, which each of them is based in time series.
@@
 
-The robot's position at disc drop is marked in 
+The robot's position at disk drop is marked in 
 Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
 framed as a classification task. The input vectors which we feed into our
-classifiers consists of the arm positions at the disc drops for both
-discs in three dimensions, as well as the largest recorded belt speed
+classifiers consists of the arm positions at the disk drops for both
+disks in three dimensions, as well as the largest recorded belt speed
 of all three belts. The interpretation of the quality measurement is 
@@
 Based on the MLP prediction results presented on Table.~\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
-The false-negative results represents the 12\% of the test sample and the true predictions constitute a 88\% of the test data.
+The false-negative results represents the 12\% of the test sample and the true predictions constitute 88\% of the test data.
 
@@
 
-Quality assurance is an important topic in production.
+% Quality assurance is an important topic in production.
 Quality assurance methods in production might diverge one from each other, however, all of them seek to prove the product quality in one way or another.

### 2020-12-03 02_Paper/paper.tex
Fixing corresponding author
intro

@@
 \author[a]{Fabian Steinberg} 
-\author[a]{Alejandro R. Pérez M.}
+\author[a]{Alejandro R. Pérez M.*}
 \author[a]{Lennart Schmallenbach}
@@
        \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
-       \item \textbf{Conclusion}, express the remarks and diskoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
+       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
 \end{itemize}
@@
 For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}.
-Subsequently, each data-sample is automatically checked for missing sensor values and diskarded if so.
+Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so.
 At this point we have a series de data-samples, which each of them is based in time series.

### 2020-12-03 02_Paper/paper.tex
update bib style, introduction and acknowledgments

@@
 
-Product features such as reliability, durability, or complete functionality determine to a large extent the success and profit of companies on the market.
-That is why it is highly important for companies to ensure that every product meet the expected requirements.
+For companies aiming at quality leadership, the final quality of any goods produced is vital for market success.
+That is why it is highly important for companies to ensure that every product meets the expected requirements.
 Throughout the years, diverse methods for quality control (QC) have been presented and implemented in production.
 Some of those methods prove to be highly effective, but costly, i.e.
-the revision of every produced piece, either by automated or manual methods, or by doing quality inspections based on a portion of the produced pieces and extend the results based on statistical methods.
-Which still has a considerable risk of not detecting NOK parts and sending them to costumers \cite{mitra2016fundamentals, fox1993quality, kahle2013zuverlaessigkeitsanalyse}.
+the inspection of every produced piece (100\% control), either by automated or manual methods, by doing quality inspections based on a portion of the produced pieces and extend the results based on statistical methods, or by reducing the risk of mistakes by intentionally modifying the process to avoid human errors.
+This bears a considerable risk of not detecting faulty-parts (NOK) and sending them to costumers \cite{fox1993quality, Robinson2011UsingPT}.
 
 Whenever a QC method is selected, it is important to remark that compromises must be made in most cases.
-For example, traditional methods like controlling every produced piece might affect the production goals by delaying the production speed at the cost of lower rejection rates On the other hand, higher production speeds normally requires statistical quality control methods.
+For example, traditional methods like controlling every produced piece might affect have a considerable impact in the production, due to the
+
+goals by delaying the production speed at the cost of lower rejection rates On the other hand, higher production speeds normally requires statistical quality control methods.
 However, those methods do not provide one hundred percent certainty that the required product quality will be achieved \cite{selvamuthu2018introduction, kurniati2015quality}.
@@
 
-\subsection{Quality check in production} \label{sec:qcp} % Basic books (find summarize) basic concepts
+\subsection{Quality control in production} \label{sec:qcp} % Basic books (find summarize) basic concepts
 
 The quality control of production processes and products is one fundamental part of general quality management.
-It contains the measures and activities needed to fulfill specific quality requirements \cite{illes2017new}.
+It contains the measures and activities needed to fulfill specific quality requirements.
 According to Illés, there are three established tools and methods of quality control \cite{illes2017new}:
@@
 \section*{Acknowledgments}
-This project was partly supported by the German and European IKT.NRW
-project "`ManuBrain"'
+This work was funded by the European Regional Development Fund (ERDF) with the project name "ManuBrain"
 
-\bibliographystyle{abbrv}
+\bibliographystyle{ieeetr} %elsarticle-harv} %abbrv
 \bibliography{bib}

### 2020-12-03 02_Paper/paper.tex
Lesson learned

@@
 In order to solve the issue, it was needed to write a time-stamp synchronization script that was deployed during the data preprocessing phase.
-Without harmonious time-stamps, the input data for the ML model would have been useless and the model inaccurate.
+Without harmonious time-stamps, determining the production cycle would have been impossible and the input data for the ML model would have been useless, and the model inaccurate.
 
-\textbf{Data interpretation}; complex, time-consuming, and fundamental step on any ML applications.
+\textbf{Data interpretation}; this process is considered complex, time-consuming, and fundamental step on any ML applications.
 It is fundamental to understand the assembly process, the timing from the machine movements, the boundaries of the machine's sensors, as well of a basic correlation within the presented data.

### 2020-12-03 02_Paper/paper.tex
ml update.

--- 2020-12-03 02_Paper/paper.tex
@@
 \subsection{Support Vector Machines}
-Support Vector Machines (SVM) offer a convex alternative to MLPs \cite{Suykens2002least}.
-A convex classifier is guaranteed to converge to a global solution regardless 
-of its initialization. 
-The Kernel trick allows SVM to solve non-linear classification problems \cite{Suykens2002least} by mapping implicitly mapping the inputs into a higher feature space.
+Support Vector Machines (SVM) attempt to separate data
+along hyperplanes \cite{aggarwal2015data}. 
+SVM offer a convex alternative to MLPs \cite{Suykens2002least}.
+A convex classifier is guaranteed to converge to a global solution
+regardless of its initialization.
+Non-separable data can become separable if projected to a different
+possibly high dimensional space trough a Kernel function.
+The Kernel trick allows SVM to solve some non-linear
+classification problems \cite{Suykens2002least}
 Radial basis functions (RBF) are commonly chosen as kernels
@@
 Decision trees are binary trees, these binary trees work with the input
-features at the roots, resulting decisions are found by moving
-trough the tree to top leaves. At every branch in the tree a decision
-is made, until one arrives at the final conclusion \cite{Marsland2015Machine}.
-Decision trees are trained using  
-\MW{Will write more tomorrow.}
+features at the roots, decisions are made by moving
+up the tree to top leaves. At every branch in the tree, a decision
+is made, until one arrives at the decision \cite{Marsland2015Machine}.
+For numerical input features, each decision partitions the data
+\cite{aggarwal2015data}. For example by comparison to a threshold value.
+To construct the tree these cutoff values have to be chosen
+at every branch. The construction problem turns into an optimization 
+problem when a split criterion is introduced. Common choices are 
+cross-entropy of Gini-coefficient \cite{aggarwal2015data}.
+During construction, the chosen function must be minimized.
 
@@
 For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}.
-Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so.
+Subsequently, each data-sample is automatically checked for missing sensor values and diskarded if so.
 At this point we have a series de data-samples, which each of them is based in time series.

### 2020-12-04 02_Paper/paper.tex
updates some grammar check - update table 4

@@
 Whenever a QC method is selected, it is important to remark that compromises must be made in most cases.
-For example, traditional methods like controlling every produced piece might affect have a considerable impact in the production, due to the
+For example, traditional methods like controlling every produced piece might affect have a considerable impact in the production, due to the \AP{review}
 
@@
 This paper is divided in 6 sections:
-
 \begin{itemize}
@@
 
-Industrial projects requires to work with a variety of sensors and controllers.
-Thus, it might occurs incompatibility between technologies.
-In order to avoid that problem, universal protocols are often implemented at industrial projects.
+Industrial projects require to work with a variety of sensors and controllers.
+Thus, might occur incompatibility between technologies.
+To avoid that problem, universal protocols are often implemented at industrial projects.
 This is the case for our industrial 4.0 demonstration cell, which shares data via protocol OPC-UA.
@@
 For our case, the data is shared independently from two OPC-UA servers.
-This in order to represent the interaction between multiple servers in real production environments.
+This represents the interaction between multiple servers in real production environments.
 
@@
 The second step is to determine the use cases of interest.
-On this research, we focussed on the data described on Table.~\ref{tab:data_source} and the six use cases described on Table.~\ref{tab:use_cases}.
+This research focussed on the data described in Table.~\ref{tab:data_source} and the six use cases described in Table.~\ref{tab:use_cases}.
 The data was manually collected by using the software "UAExperts".
@@
        \end{adjustbox}
-       \caption{Industriy 4.0 demonstration cell: Relevant data with its reference source server}
+       \caption{Industriy 4.0 demonstration cell: Relevant data linked with its reference source server.}
        \label{tab:data_source}
@@
        \includegraphics[width=.45\textwidth]{img/demozelle_conex_diagram.png}
-       \caption{Industry 4.0 demostration cell: Connection diagram (simplified)
+       \caption{Industry 4.0 demostration cell: Connection diagram (simplified).
              }
@@
               \end{adjustbox}
-              \caption{SVM.}
+              \caption{Support Vector Machine.}
               \label{tab:SVM_conf_matrix}
@@
               \end{adjustbox}
-              \caption{MLP.}
+              \caption{Multilayer Perceptron.}
               \label{tab:MPL_conf_matrix}
@@
        \end{subtable}
-       \caption{Confusion matrix result of the prediction of 50 data-points.}
+       \caption{Confusion matrices result of the prediction of 50 test data-points.
+We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs and predictions.
+The tables read from the upper left cell as: true-positive, false-positive, false-negative, true-negative.}
        \label{tab:Confusion_matrix}
@@
 
-\bibliographystyle{ieeetr} %elsarticle-harv} %abbrv
+\bibliographystyle{elsarticle-harv} %elsarticle-harv} %abbrv
 \bibliography{bib}

### 2020-12-04 02_Paper/paper.tex
data preprocessing update

@@
 Industrial projects require to work with a variety of sensors and controllers.
-Thus, might occur incompatibility between technologies.
+Thus, there is a risk of incompatibility between technologies.
 To avoid that problem, universal protocols are often implemented at industrial projects.
@@
 This research focussed on the data described in Table.~\ref{tab:data_source} and the six use cases described in Table.~\ref{tab:use_cases}.
-The data was manually collected by using the software "UAExperts".
-Approximately 15 hours of data was collected, by equally sampling each use case during the data acquisition time.
+The data was manually collected by using the software "UAExpert - v1.5.1".
+Approximately 15 hours of data were collected, while equally sampling each use case during the data acquisition time.
 
@@
        \end{tabular}
-       \caption{Industrial 4.0 demostration cell: Controlled use-cases.
-       Use cases with Robot position: NOK and Conveyor speed: Too Fast will result in NOK pieces.}
+       \caption{Industrial 4.0 demostration cell: Controlled Use-Cases.
+       Use-Cases which the value \textit{Robot position: NOK} and \textit{Conveyor speed: Too Fast} will result in NOK pieces.}
        \label{tab:use_cases}
@@
 Once enough data is collected, the next step is to clean the raw data and organize it accordingly.
-For our case, that means to merge the data collected from the two OPC-UA servers, synchronize the time stamps.
-Since our systems are not completely synchronized, it was needed to calculate the delta-time based between servers based on the base clock from each server.
+For our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp.
+Since our systems are not completely synchronized, it was needed to calculate the delta-time between servers by referencing each server's base clock.
 Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.
@@
 Data tags interpretation is an important step in the preprocessing process.
-The raw data collected from the sensors is sometimes tagged by an alphanumeric code.
-In order to work with the data, it was needed to implement diverse functions wich have the task to clean the raw data in a more human-readable form.
-This means to remove samples out of clear boundaries and missing values, as well as to translate the sensors code based in a predefined dictionary settle by the authors.
-This last step, could be optional in other implementations, however, it proves to be a great addition for testing purposes.
+The raw data collected from the sensors is sometimes tagged by an alphanumeric code predefined by the sensor manufacture.
+To work with the data, it was needed to implement diverse functions which have the task to clean the raw data in a more human-readable form.
+This means to remove samples out of clear boundaries and missing values, as well as to translate the sensor code tags based on a dictionary predefined by the authors.
+This last step, might be optional in other implementations, however, it proves to be a great addition for testing purposes.
 
-Once the data is clean and compiled in one directory, the next step would be to split the data based on the assembly cycle.
-For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}.
+Once the data is clean and compiled in one directory, our step was to split the data based on the assembly cycle.
+For our purpose, we split the dataset into individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}.
 Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so.
-At this point we have a series de data-samples, which each of them is based in time series.
-However, we are not interested in a time series analysis, therefore it would be needed to compress each time-series based data-sample in an atemporal data-sample.
-
-To eliminate time as a variable in our dataset, we defined a series of rules:
+At this point, we have a series of data-samples based on time series.
+However, we are not interested in a time series analysis, therefore it was needed to compress each time-series based data-sample in an atemporal data-sample.
+To eliminate time as a variable in our dataset, we defined a series of rules to be applied on each assembly cycle data-sample:
 
 \begin{itemize}
-       \item Robot position ($xyz$) while dropping the disk in the storage area
-       \item Mean conveyor speed per conveyor band
-       \item Absolute deviation ($xy$) at the quality control check
-       \item Absolute quality check result: OK - NOK
+       \item Value of the robot position ($xyz$) while dropping the disk in the storage area
+       \item Mean conveyor speed value per conveyor band
+       \item Absolute deviation ($xy$) value at the quality control check
+       \item Absolute quality control value: OK - NOK
 \end{itemize}
 
-Each time-series sample was evaluated based on the rules stated above, and the result of each evaluation was considered as our atemporal data-sample, which would be used by our classifier.
+Each time-series sample was evaluated based on the rules stated above, and the result of each evaluation was considered as our atemporal data-sample, which we used as the base for our classifier.
 

### 2020-12-04 02_Paper/paper.tex
Classifier optimization and testing update

@@
 framed as a classification task. The input vectors which we feed into our
-classifiers consists of the arm positions at the disk drops for both
+classifiers consist of the arm positions at the disk drops for both
 disks in three dimensions, as well as the largest recorded belt speed
 of all three belts. The interpretation of the quality measurement is 
-used as the training target. It can be good or bad which we encode as 
+used as the training target. It can be OK or NOK which we encode as 
 zero and one.
@@
 We work with a total of 528 measurements. Each containing arm and belt data
-logs of individual cell runs. 50 samples are set aside at random for testing 
+logs of individual cell run. 50 samples are set aside at random for testing 
 purposes, leaving 478 training samples. The random number generator seed is
@@
 structure. All three methods are trained using standard hyperparameters.
-\footnote{In order to allow exact reproduction of these results source
+\footnote{To allow exact reproduction of these results source
 code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
@@
 as faulty. Over the test set, we require to classify more than 64\% of the data correctly.
-We would therefore expect any naive classifier to produce at least 64\% accuracy, which we have to beat.
+We would therefore expect any naive classifier to produce at least 64\% accuracy, which we have to surpass.
 In Table~\ref{tab:class_comp}, we observe that this is indeed the case for all three approaches evaluated here.
@@
 Based on the MLP prediction results presented on Table.~\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
-The false-negative results represents the 12\% of the test sample and the true predictions constitute 88\% of the test data.
+The false-negative results represent the 12\% of the test sample and the true predictions constitute 88\% of the test data.
 
 The outcome of the models shows that the random forest performed best followed by the multilinear perceptron and the support vector machine.
-However, by reviewing the confusion matrices presented on Table,~\ref{tab:Confusion_matrix}, multilinear perceptron would be the option of choice to be implemented at industrial applications due to the 0\% ratio in false-positive results.
+However, by reviewing the confusion matrices presented in Table,~\ref{tab:Confusion_matrix}, multilinear perceptron would be the preferred solution to be implemented at industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
 

### 2020-12-04 02_Paper/paper.tex
Machine learning methods

@@
 
-We compare Support Vector Machines (SVM), Multilinear Perceptrons
-\cite{bishop2006pattern} as well as random forests in the task of
-quality prediction. All three will be introduced next.
+To study which implementation would be more suitable for industrial application, we compare Support Vector Machines (SVM), Multilinear Perceptrons as well as random forests on the task of quality prediction.
+All three will be introduced next.
+
+\subsection{Support Vector Machines}
+Support Vector Machines (SVM) attempt to separate data
+along hyperplanes \cite{aggarwal2015data}. 
+SVM offer a convex alternative to MLPs \cite{Suykens2002least}.
+A convex classifier is guaranteed to converge to a global solution
+regardless of its initialization.
+Non-separable data can become separable if projected to a different
+possibly high dimensional space through a Kernel function.
+The Kernel trick allows SVM to solve some non-linear
+classification problems \cite{Suykens2002least}.
+Radial basis functions (RBF) are commonly chosen as kernels
+\cite{Suykens2002least}, therefore, we choose to follow this practice as well.
 
@@
 
-\subsection{Support Vector Machines}
-Support Vector Machines (SVM) attempt to separate data
-along hyperplanes \cite{aggarwal2015data}. 
-SVM offer a convex alternative to MLPs \cite{Suykens2002least}.
-A convex classifier is guaranteed to converge to a global solution
-regardless of its initialization.
-Non-separable data can become separable if projected to a different
-possibly high dimensional space trough a Kernel function.
-The Kernel trick allows SVM to solve some non-linear
-classification problems \cite{Suykens2002least}
-Radial basis functions (RBF) are commonly chosen as kernels
-\cite{Suykens2002least} we choose to follow this practice as well.
-
 \subsection{Decision Tree}
-Decision trees are binary trees, these binary trees work with the input
+Decision trees are essentially binary trees, which work with the input
 features at the roots, decisions are made by moving
@@
 
-Based on the literature review, we observed that the hundred percent quality check method proves to be the most efficient method to guarantee the final product quality, however, the high implementation cost is its biggest draw back.
-On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each individual product until the next bach review might imply a considerable loss whenever NOK products are found.
-This based in the uncertainty of when did the error occurs and how many products are affected.
+Based on the literature review, we observed that the hundred percent quality check method proves to be the most efficient method to guarantee the final product quality, however, the high implementation cost is its biggest draw-back.
+On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each product until the next bach review might imply a considerable loss whenever NOK products are found.
+This is based on the uncertainty of when did the error occurs and how many products are affected.
 
 By implementing ML models capable to predict the quality of the product, just by the initial conditions of the process would be a great asset for the industrial processes.
-Within the limits of our work, we are able to predict with 98\% certainty the product quality by implementing a decision tree model with a 6-variables vector as input.
+Within the limits of our work, we predict with 98\% certainty the product quality by implementing a decision tree model with a 6-variables vector as input.
 However, our decision for industrial applications would be the MLP with 88\% accuracy as to guarantee the QC and avoid labeling a NOK piece as OK.
@@
 It is important to state that this prediction model is not yet ready to fully replace the statistical methods, not the hundred percent quality check method.
-However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this will somehow compensate one of the disadvantages from statistical methods.
+However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this will somehow compensate one disadvantage the statistical methods have.
 
@@
 
-\textbf{Data interpretation}; this process is considered complex, time-consuming, and fundamental step on any ML applications.
-It is fundamental to understand the assembly process, the timing from the machine movements, the boundaries of the machine's sensors, as well of a basic correlation within the presented data.
+\textbf{Data interpretation}; this process is considered complicate, time-consuming, and fundamental step on any ML applications.
+It is fundamental to understand the assembly process, the timing from the machine movements, the boundaries of the machine's sensors, as well a basic correlation within the presented data.
 
-\textbf{Missing values}; in order to minimize the risk of false results delivered by the ML model, it would be compulsory to carefully review the ML input data.
-Missing values can have a great impact in the ML prediction, that is the reason why we deliberately review all the input data and validate it with the expected output from the diverse sensors.
+\textbf{Missing values}; to minimize the risk of false results delivered by the ML model, it would be compulsory to carefully review the ML input data.
+Missing values can have a great impact on the ML prediction, that is the reason why we deliberately review all the input data and validate it with the expected output from the diverse sensors.
 Whenever there was missing data, and as long as we did not fabricate data, we employed statistical methods to fill the data gap.
@@
 of our cell-date was key to the successful application of all three algorithms.
-Without the labels the problem could not have been framed as a supervised 
+Without the labels, the problem could not have been framed as a supervised 
 classification problem.

### 2020-12-05 02_Paper/paper.tex
Predictive analytics

@@
 
-According to Delen and Damirkan, predictive analytics (PA) consist on unravel the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
+According to Delen and Damirkan, predictive analytics (PA) unravel the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
+PA offers a wide range of applications, and it can be implemented as long as the provided data are sufficiently available.
+By considering the industrial and production environment, PA would be a great asset due to the high flexibility and high amount of data available coming from processes, single machines or cells, products, and others.
+Some common industrial applications of PA in the industry are focused products (design and optimization), machines (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.
 
-PA offers a wide range of applications, and it can be implemented as long as there is enough data available.
-By considering the industrial and production environment, PA would be a great asset due to the high flexibility and high amount of data available coming from processes, single machines or cells, products, and others.
-Some common industrial applications of PA at the industry are focused products (design and optimization), machines (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.
-
-Applications that combines PA with QC might be a great improvement in the quality control process because it is an improvement compared with the earlier mentioned methods \ref{sec:qcp}, in terms of speed, accuracy and time delay.
-
-The outcome of an explorative literature review on this matter, shows that the findings that combines PA and QC are very scarce in the literature.
-This could be in great part, due to the novelty of the area \cite{aumi2012model, ritter1992neue}.
-Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.
+Applications that combine PA with QC might improve the current QC processes.
+By employing machine learning (ML) techniques \ref{sec:ML}, together with traditional methods \ref{sec:qcp}, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process.
 
 Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature.
-This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area.
-Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated}; product quality prediction in a process chain \cite{krauss2019machine}; model development for predictive quality control of batch processes \cite{aumi2012model}; and ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}.
-Considering the lack of literature, our goal is to decrease this gap on the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation.
+This could be in great part, due to computer power limitations in early research and the recent increase of ML applications in this area.
+Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}, and Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}.
+
+By considering the lack of literature, our goal is to decrease this gap in the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation.
+To do so, we need to select the right testing platform.
+This platform should represent real industrial applications and be able to handle a certain level of complexity.
+In our work, we applied a case-based research approach \cite{yin2017case} to answer the research question \AP{what research question?}.
+One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
+%This sentence can be deleted if needed.
 
@@
 
-To test our theories, we need to select the right testing platform.
-This platform should represent real industrial applications and be able to handle a certain level of complexity.
-In our work, we applied a case-based research approach \cite{yin2017case} in order to answer the research question.
-One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
-%This sentence can be deleted if needed.
-
-Our case of study is an abstraction of an assembly process at the industry.
-The industry 4.0 demonstration cell is composed by three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200.
-The assembly process done at this demonstration cell consist on stacking two disks of different size on the top of each other.
+Our case of study is an abstraction of an assembly process of the industry.
+The industry 4.0 demonstration cell is composed of three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200.
+The assembly process done at this demonstration cell consists in stacking two disks of different sizes on top of each other.
 The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disks Figure~\ref{fig:ind_cell}.
@@
 
-\section{Machine Learning Methods} %3/4 Page
+\section{Machine Learning Methods} \label{sec:ML} %3/4 Page
 

### 2020-12-05 02_Paper/paper.tex
Predictive analytics

@@
 To do so, we need to select the right testing platform.
-This platform should represent real industrial applications and be able to handle a certain level of complexity.
+It has to have a clear production process, complete access to sensor data, and flexible enough to reprogram the process if necessary
 In our work, we applied a case-based research approach \cite{yin2017case} to answer the research question \AP{what research question?}.

### 2020-12-07 02_Paper/paper.tex
The case industry 4.0 demonstration cell

@@
 Our case of study is an abstraction of an assembly process of the industry.
-The industry 4.0 demonstration cell is composed of three independent conveyor belts, a robotic assembly arm, a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200.
-The assembly process done at this demonstration cell consists in stacking two disks of different sizes on top of each other.
-The quality of the pseudo products is later evaluated by the laser scanner by evaluating the concentricity of both disks Figure~\ref{fig:ind_cell}.
-If the disk's concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it shall be classified as NOK.
-By considering that malfunctions can occur during real production processes at industries, our demonstration cell is able to simulate failures in diverse areas, such as:
+The industry 4.0 demonstration cell is composed of three independent conveyor belts, a robotic assembly arm (UR3), a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200, see Figure~\ref{fig:ind_cell}.
+The executed abstracted assembly process consists of stacking two disks of different sizes on top of each other.
+These pseudo product quality are later determined by the laser scanner by evaluating the concentricity of both disks.
+If the disks' concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it is classified as NOK.
+By considering that malfunctions can occur during industrial production processes, our demonstration cell can simulate failures in diverse areas, such as:
 
 \begin{itemize}
-       \item Assemble errors due to the robotic arm
-       \item Bearing damage on the conveyor belt
-       \item Resistance on the conveyor belt
-       \item Leakage in the compressed air system
-       \item Productivity limit reached
-       \item Missing material
+       \item Assembly errors due to the robotic arm: incorrectly positioned disks.
+       \item Bearing damage on the conveyor belts: vibration changes in the conveyor belt motors.
+       \item Resistance on the conveyor belts: temperature changes in the conveyor belt motors.
+       \item Malfunction of the gate door due to leakage in the compressed air system: cylinder stroke at the assembly barrier is slower.
+       \item Faster operating point: disks shift position due to the high belt speeds.
+       \item Missing material at the end of the warehouse: production stop due to lack of material.
 \end{itemize}
 
-Those simulated failures have a real impact in the data collected by the sensors.
+Those simulated failures have an impact in the data collected by the sensors.
 Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticeable shifting on pieces' position as well as the stop of the process.
 
-The continuous data collection and the clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations.
+The continuous data collection and the clear correlation between the machine parameters is the ideal play-ground to implement a sandbox for machine learning implementations.
 With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner.
-The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability.
+%Last paragraph to review. stn would likely remove it.
+We expect the findings gained with the demonstration cell to be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability.
 This would be a step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.

### 2020-12-07 02_Paper/paper.tex
Predictive analytics in production

@@
 
-According to Delen and Damirkan, predictive analytics (PA) unravel the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
-PA offers a wide range of applications, and it can be implemented as long as the provided data are sufficiently available.
-By considering the industrial and production environment, PA would be a great asset due to the high flexibility and high amount of data available coming from processes, single machines or cells, products, and others.
-Some common industrial applications of PA in the industry are focused products (design and optimization), machines (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.
+According to Delen and Damirkan, predictive analytics (PA) consists of unraveling the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
+PA offers a wide range of applications, and it can be implemented, as long as the provided data are sufficiently available \cite{bishop2006pattern}.
+According to Krauß, there is a wide range of applications for PA in the industrial and production environment.
+Some common industrial applications of PA in the industry are focused products (design and optimization), machines and assets (predictive maintenance, anomaly detection, self learning-machines) and process (scheduling, process design, predictive process control)\cite{krauss2019machine}
 
 Applications that combine PA with QC might improve the current QC processes.
-By employing machine learning (ML) techniques \ref{sec:ML}, together with traditional methods \ref{sec:qcp}, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process.
+By employing machine learning (ML) techniques \ref{sec:ML}, together with traditional methods \ref{sec:qcp}, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
 
@@
 This could be in great part, due to computer power limitations in early research and the recent increase of ML applications in this area.
-Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}, and Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}.
+Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model},Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}, and others focused on one product quality analysis \cite{Selmaier2019PQXray, Sohnius2019PASurfacequality}.
 

### 2020-12-08 02_Paper/paper.tex
related works and introduction

@@
 
-This paper is divided in 6 sections:
-\begin{itemize}
-       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
-       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
-       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project.
+% This paper is divided in 6 sections:
+% \begin{itemize}
+%        \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
+%        \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
+%        \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project.
 It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
-       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
-       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
-       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
-\end{itemize}
+%        \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
+%        \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
+%        \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
+% \end{itemize}
 
@@
 
-The quality control of production processes and products is one fundamental part of general quality management.
-It contains the measures and activities needed to fulfill specific quality requirements.
-According to Illés, there are three established tools and methods of quality control \cite{illes2017new}:
-The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
-The SPC is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes in the quality characteristics in the production process \cite{selvamuthu2018introduction}.
-SPC methods can also take place before the actual manufacturing process, this is commonly known as "off-line SPC".
+The quality control of production processes and products is one fundamental part of general quality management. It contains the measures and activities needed to fulfill specific quality requirements.
+% According to Illés, there are three established tools and methods of quality control:
+% The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC) \cite{illes2017new}. 
+According to Illés, there are diverse established tools and methods of quality control.
+Those methods would have a specific level of focus, from the product level, to the process-management level \cite{illes2017new}.
+In this paper, we focused on the methods related to the QC at the product level.
 
+The Statistical Process Control (SPC) method is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes in the quality characteristics in the production process.
+SPC methods can also take place before the actual manufacturing process, this is commonly known as "off-line SPC" \cite{selvamuthu2018introduction}.
 During the design phase of a process or product, off-line SPC procedures are deployed.
-Those procedures aim to increase the quality of the outcoming product by choosing controllable products and  process parameter \cite{mitra2016fundamentals}.
-
+These procedures aim to increase the quality of the outcoming product by choosing conforming products and  process parameters \cite{mitra2016fundamentals}.
 The biggest advantage of working with SPC is that large batches can be checked without major time impact on the QC process, however, this would be only possible if the variance of the process product parameters is small enough, to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
+It is important to remark that statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and the hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
+Which means, if a batch is labeled as NOK, there is no specific reference of when did the error occurs and how many pieces are affected.
 
 Another conservative technique to perform the quality check would be to check 100\% of the produced parts.
-On this method, every product is controlled and binary sorted as an OK or Non-OK part.
-However, this has the disadvantage of high cost related to personal or specialized material and in certain cases, could lead to a delay in production.
+In this method, every product is controlled and sorted at designated quality levels.
+However, this has the disadvantage of high cost related to personal or specialized material.
+Generally, this method is used when the consequences of letting a defective item through could be severe, e.g., for specialized equipment or when the cost of delivering faulty products is very high \cite{Hinckley1997QC}.
 
-Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
+% Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
 This method is executed by
-an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
+% an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
 In a further step, the findings would be later corrected by another person rather than the auditor \cite{fox1993quality}.
@@
 
-Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and the hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
+% While the SPC mostly optimizes the capability of the process, for example, the acceptance plan prevents the nonconforming product to be passed and then delivered to the next process or the customer \cite{kurniati2015quality}.
+% In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
 
-While the SPC mostly optimizes the capability of the process, for example the acceptance plan prevents the nonconforming product to be pass and then delivered to the next process or the customer \cite{kurniati2015quality}.
-In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
-Generally, statistical methods are faster than the hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
+% Generally, statistical methods are faster than the hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
 those assumptions might lead to errors if the variance of the product quality higher than expected.
 
-The concept of TQC is to extend the scope of quality control to the whole company and product life cycle, by involving all departments of the organization \cite{illes2017new}.
+% The concept of TQC is to extend the scope of quality control to the whole company and product life cycle, by involving all departments of the organization \cite{illes2017new}.
+
 The quality characteristics of a product can be classified as variables or attributes.
@@
 This could be in great part, due to computer power limitations in early research and the recent increase of ML applications in this area.
-Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model},Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}, and others focused on one product quality analysis \cite{Selmaier2019PQXray, Sohnius2019PASurfacequality}.
+Most of the related works found, tends to be from recent years \cite{krauss2020automated, krauss2019machine, aumi2012model,Selmaier2019PQXray, Sohnius2019PASurfacequality, ritter1992neue}.
+% Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model},Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}, and others focused on one product quality analysis \cite{Selmaier2019PQXray, Sohnius2019PASurfacequality}.
 
@@
 It has to have a clear production process, complete access to sensor data, and flexible enough to reprogram the process if necessary
-In our work, we applied a case-based research approach \cite{yin2017case} to answer the research question \AP{what research question?}.
+In our work, we applied a case-based research approach \cite{yin2017case} 
+% to answer the research question \AP{what research question?}.
+for our implementation.
 One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
@@
 %Last paragraph to review. stn would likely remove it.
-We expect the findings gained with the demonstration cell to be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability.
+% We expect the findings gained with the demonstration cell to be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability.
 This would be a step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.

### 2020-12-08 02_Paper/paper.tex
Quality control in production

@@
 The quality characteristics of a product can be classified as variables or attributes.
-Variables are measurable characteristics, which are shown as numbers.
-On the contrary, attributes are not measurable and can only take the binary values like "go" or "no-go" \cite{mitra2016fundamentals}.
-The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters.
-This allows the desired quality to be restored. With that in mind, predictive quality control is a promising solution.
+Attributes are qualitative measurable characteristics, i.e, color, texture, other. Variables are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}. 
+The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the the posibility of observing trends in the collected data.
+This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place.
+With that in mind, predictive quality control is a promising solution.
 

### 2020-12-08 02_Paper/paper.tex
Introduction and QC

@@
 
-For companies aiming at quality leadership, the final quality of any goods produced is vital for market success.
+% For companies aiming at quality leadership, the final quality of any goods produced is vital for market success.
 That is why it is highly important for companies to ensure that every product meets the expected requirements.
@@
 
-Whenever a QC method is selected, it is important to remark that compromises must be made in most cases.
+% Whenever a QC method is selected, it is important to remark that compromises must be made in most cases.
 For example, traditional methods like controlling every produced piece might affect have a considerable impact in the production, due to the \AP{review}
 
-goals by delaying the production speed at the cost of lower rejection rates On the other hand, higher production speeds normally requires statistical quality control methods.
+% goals by delaying the production speed at the cost of lower rejection rates On the other hand, higher production speeds normally requires statistical quality control methods.
 However, those methods do not provide one hundred percent certainty that the required product quality will be achieved \cite{selvamuthu2018introduction, kurniati2015quality}.
 
-With the evolution of machine learning (ML) applications, we expect to enhance the QC by predicting the product quality at the initial stage of production.
+% With the evolution of machine learning (ML) applications, we expect to enhance the QC by predicting the product quality at the initial stage of production.
 This will not only reduce cost in production, and strengthen the QC process, it will also be part of the predictive analytics tools found in production, which is currently widely used in diverse fields due to its accurate predictions \cite{bishop2006pattern, krauss2019machine}.
@@
 
-\section{Related Works} % 1 Page \Lennart
-
-\subsection{Quality control in production} \label{sec:qcp} % Basic books (find summarize) basic concepts
-
-The quality control of production processes and products is one fundamental part of general quality management. It contains the measures and activities needed to fulfill specific quality requirements.
+The quality control (QC) of production processes and products is one fundamental part of general quality management.
+It contains the measures and activities needed to fulfill specific quality requirements.
 % According to Illés, there are three established tools and methods of quality control:
@@
 The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the the posibility of observing trends in the collected data.
+This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place.
+With that in mind, predictive quality control is a promising solution.
+
+With the evolution of machine learning (ML) applications, we expect to enhance the QC by predicting the product quality at the initial stage of production.
+This will not only reduce cost in production, and strengthen the QC process, it will also be part of the predictive analytics tools found in production, which is currently widely used in diverse fields due to its accurate predictions \cite{bishop2006pattern, krauss2019machine}.
+
+This paper is divided in 6 sections:
+\begin{itemize}
+       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
+       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
+       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project.
+It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
+       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
+       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
+       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
+\end{itemize}
+
+\section{Related Works} % 1 Page
+
+% \subsection{Quality control in production} \label{sec:qcp} % Basic books (find summarize) basic concepts
+
+% The quality control of production processes and products is one fundamental part of general quality management.
+It contains the measures and activities needed to fulfill specific quality requirements.
+% % According to Illés, there are three established tools and methods of quality control:
+% % The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC) \cite{illes2017new}. 
+% According to Illés, there are diverse established tools and methods of quality control.
+Those methods would have a specific level of focus, from the product level, to the process-management level \cite{illes2017new}.
+In this paper, we focused on the methods related to the QC at the product level.
+
+% The Statistical Process Control (SPC) method is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes in the quality characteristics in the production process.
+SPC methods can also take place before the actual manufacturing process, this is commonly known as "off-line SPC" \cite{selvamuthu2018introduction}.
+% During the design phase of a process or product, off-line SPC procedures are deployed.
+These procedures aim to increase the quality of the outcoming product by choosing conforming products and  process parameters \cite{mitra2016fundamentals}.
+% The biggest advantage of working with SPC is that large batches can be checked without major time impact on the QC process, however, this would be only possible if the variance of the process product parameters is small enough, to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
+% It is important to remark that statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and the hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
+Which means, if a batch is labeled as NOK, there is no specific reference of when did the error occurs and how many pieces are affected.
+
+% Another conservative technique to perform the quality check would be to check 100\% of the produced parts.
+In this method, every product is controlled and sorted at designated quality levels.
+However, this has the disadvantage of high cost related to personal or specialized material.
+Generally, this method is used when the consequences of letting a defective item through could be severe, e.g., for specialized equipment or when the cost of delivering faulty products is very high \cite{Hinckley1997QC}.
+
+% % Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
+This method is executed by
+% % an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
+In a further step, the findings would be later corrected by another person rather than the auditor \cite{fox1993quality}.
+
+% %Both statistical methods and hundred percent controls can be applied as an audit tool.
+
+% % While the SPC mostly optimizes the capability of the process, for example, the acceptance plan prevents the nonconforming product to be passed and then delivered to the next process or the customer \cite{kurniati2015quality}.
+% % In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
+
+% % Generally, statistical methods are faster than the hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
+those assumptions might lead to errors if the variance of the product quality higher than expected.
+
+% % The concept of TQC is to extend the scope of quality control to the whole company and product life cycle, by involving all departments of the organization \cite{illes2017new}.
+
+% The quality characteristics of a product can be classified as variables or attributes.
+% Attributes are qualitative measurable characteristics, i.e, color, texture, other. Variables are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}. 
+% The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the the posibility of observing trends in the collected data.
 This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place.

### 2020-12-08 02_Paper/paper.tex
introduction

@@
 
-% With the evolution of machine learning (ML) applications, we expect to enhance the QC by predicting the product quality at the initial stage of production.
-This will not only reduce cost in production, and strengthen the QC process, it will also be part of the predictive analytics tools found in production, which is currently widely used in diverse fields due to its accurate predictions \cite{bishop2006pattern, krauss2019machine}.
-
-% This paper is divided in 6 sections:
-% \begin{itemize}
-%        \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
-%        \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
-%        \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project.
-It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
-%        \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
-%        \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
-%        \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
-% \end{itemize}
-
+For companies aiming at quality leadership, the final quality of any goods produced is vital for market success.
+That is why it is highly important for companies to ensure that every product meets the expected requirements.
 The quality control (QC) of production processes and products is one fundamental part of general quality management.
 It contains the measures and activities needed to fulfill specific quality requirements.
-% According to Illés, there are three established tools and methods of quality control:
-% The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC) \cite{illes2017new}. 
 According to Illés, there are diverse established tools and methods of quality control.
@@
 This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place.
-With that in mind, predictive quality control is a promising solution.
+% With that in mind, predictive quality control is a promising solution.
 
@@
 
-This paper is divided in 6 sections:
-\begin{itemize}
-       \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
-       \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
-       \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project.
+The aim of this paper is to implement a functional predictive model in quality assurance for an assembly process in a controlled environment.
+Within the scope of the implementation, we compare three different ML models accuracy, as well as their plausibility at industrial applications.
+As result, we expect to to decrease the gap in literature on this research area, as well as to describe the based of our experiences for future works by describing the lesson learned during this implementation.
+In our work, we applied a case-based research approach \cite{yin2017case} 
+% to answer the research question \AP{what research question?}.
+for our implementation.
+One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
+%This sentence can be deleted if needed
+
+Our paper is structured as follow.
+Section.~\ref{sec:related_works} covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
+Section.~\ref{sec:democell} describe the demonstration cell used on this project.
 It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
-       \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
-       \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
-       \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
-\end{itemize}
+Section.~\ref{sec:ML} explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
+Section.~\ref{sec:experiment} describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
+Finally Section.~\ref{sec:conclusion} express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
 
-\section{Related Works} % 1 Page
+% This paper is divided in 6 sections:
+% \begin{itemize}
+%        \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
+%        \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
+%        \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project.
+It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
+%        \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
+%        \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
+%        \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
+% \end{itemize}
+
+\section{Related Works} \label{sec:related_works}% 1 Page
 
@@
 Applications that combine PA with QC might improve the current QC processes.
-By employing machine learning (ML) techniques \ref{sec:ML}, together with traditional methods \ref{sec:qcp}, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
+By employing machine learning (ML) techniques, see Sec.~\ref{sec:ML}, together with traditional methods, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
 
@@
 
-By considering the lack of literature, our goal is to decrease this gap in the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation.
+% By considering the lack of literature, our goal is to decrease this gap in the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation.
 To do so, we need to select the right testing platform.
-It has to have a clear production process, complete access to sensor data, and flexible enough to reprogram the process if necessary
-In our work, we applied a case-based research approach \cite{yin2017case} 
-% to answer the research question \AP{what research question?}.
-for our implementation.
-One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
+It has to have a clear production process, complete access to sensor data, and flexible enough to reprogram the process if necessary.
+% In our work, we applied a case-based research approach \cite{yin2017case} 
+% % to answer the research question \AP{what research question?}.
+% for our implementation.
+% One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
 %This sentence can be deleted if needed.
 
-\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page
+\section{The case industry 4.0 demonstration cell}  \label{sec:democell}% (taken from title) % 3/4 Page
 
@@
 
-\section{Experiments}
+\section{Experiments} \label{sec:experiment}
 
@@
 
-\section{Conclusion}
+\section{Conclusion} \label{sec:conclusion}
 
@@
 
-\bibliographystyle{elsarticle-harv} %elsarticle-harv} %abbrv
+\bibliographystyle{elsarticle-harv} %elsarticle-harv} %abbrv %IEEEtran
 \bibliography{bib}

### 2020-12-09 02_Paper/paper.tex
Conclusion

@@
 
-Based on the literature review, we observed that the hundred percent quality check method proves to be the most efficient method to guarantee the final product quality, however, the high implementation cost is its biggest draw-back.
-On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each product until the next bach review might imply a considerable loss whenever NOK products are found.
+Based on the explorative literature review, we observed that the hundred percent quality check method proves to be the most efficient method to guarantee the final product quality, however, the high implementation cost is its biggest draw-back.
+On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each product until the next bach review might imply a considerable loss of the produced products whenever NOK products are found.
 This is based on the uncertainty of when did the error occurs and how many products are affected.
 
-By implementing ML models capable to predict the quality of the product, just by the initial conditions of the process would be a great asset for the industrial processes.
+By implementing ML models capable to predict the quality of the product, based on just the initial conditions of the process would be a great asset for the industrial processes.
 Within the limits of our work, we predict with 98\% certainty the product quality by implementing a decision tree model with a 6-variables vector as input.
-However, our decision for industrial applications would be the MLP with 88\% accuracy as to guarantee the QC and avoid labeling a NOK piece as OK.
-For further work, we expect to increase the certainty of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.
+However, our decision for industrial applications would be the MLP with 88\% accuracy as to guarantee that all passed parts are OK and avoid labeling a NOK piece as OK.
+For further work, we expect to increase the accuracy of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.
 
-It is important to state that this prediction model is not yet ready to fully replace the statistical methods, not the hundred percent quality check method.
-However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this will somehow compensate one disadvantage the statistical methods have.
+It is important to state that this prediction model is not yet ready to fully replace the statistical methods, not the hundred percent quality check method, since this research is still on its early stages and need further development.
+However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this might compensate one disadvantage of the statistical methods.
 

### 2020-12-09 02_Paper/paper.tex
Data acquisition

@@
 To avoid that problem, universal protocols are often implemented at industrial projects.
-This is the case for our industrial 4.0 demonstration cell, which shares data via protocol OPC-UA.
+This is the case for our industrial 4.0 demonstration cell, which shares data via the protocol OPC-UA.
 
 Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell.
-For our case, the data is shared independently from two OPC-UA servers.
+For our case, the data is acquired independently from two OPC-UA servers.
 This represents the interaction between multiple servers in real production environments.
 
-The first step to collect the data is to list all the variables of interest and to map their source.
-The second step is to determine the use cases of interest.
-This research focussed on the data described in Table.~\ref{tab:data_source} and the six use cases described in Table.~\ref{tab:use_cases}.
+In our implementation, we acquired the data in two steps.
+The first step was list all the variables of interest and to map their source.
+The second step was to determine the use cases of interest.
+Our study focussed on the data described in Table.~\ref{tab:data_source} and the six use cases described in Table.~\ref{tab:use_cases}.
 The data was manually collected by using the software "UAExpert - v1.5.1".

### 2020-12-09 02_Paper/paper.tex
Data preprocessing

@@
 
-Once enough data is collected, the next step is to clean the raw data and organize it accordingly.
+Once enough data is collected, the next step is to clean the raw data and organize it accordingly \cite{goodfellow2016deep}.
 For our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp.
@@
 
-Data tags interpretation is an important step in the preprocessing process.
-The raw data collected from the sensors is sometimes tagged by an alphanumeric code predefined by the sensor manufacture.
+Data tags interpretation is an important step in the preprocessing process \cite{goodfellow2016deep}.
+The raw data collected from the sensors is usually tagged by an alphanumeric code predefined by the sensor manufacture.
 To work with the data, it was needed to implement diverse functions which have the task to clean the raw data in a more human-readable form.
@@
 At this point, we have a series of data-samples based on time series.
-However, we are not interested in a time series analysis, therefore it was needed to compress each time-series based data-sample in an atemporal data-sample.
-To eliminate time as a variable in our dataset, we defined a series of rules to be applied on each assembly cycle data-sample:
+However, we are not interested in a time series analysis since we want to focus on ML methods based on an atemporal vector approach, therefore it was needed to compress each time-series based data-sample in an atemporal data-sample.
+To eliminate time as a variable in our dataset, we defined a series of rules to be applied in each assembly cycle data-sample:
 

### 2020-12-09 02_Paper/paper.tex
ML methods

@@
 
-To study which implementation would be more suitable for industrial application, we compare Support Vector Machines (SVM), Multilinear Perceptrons as well as random forests on the task of quality prediction.
+To study which implementation would be more suitable for industrial applications, we compare Multilinear Perceptrons (MLPs), Support Vector Machines (SVM), as well as random forests on the task of quality prediction.
 All three will be introduced next.
-
-\subsection{Support Vector Machines}
-Support Vector Machines (SVM) attempt to separate data
-along hyperplanes \cite{aggarwal2015data}. 
-SVM offer a convex alternative to MLPs \cite{Suykens2002least}.
-A convex classifier is guaranteed to converge to a global solution
-regardless of its initialization.
-Non-separable data can become separable if projected to a different
-possibly high dimensional space through a Kernel function.
-The Kernel trick allows SVM to solve some non-linear
-classification problems \cite{Suykens2002least}.
-Radial basis functions (RBF) are commonly chosen as kernels
-\cite{Suykens2002least}, therefore, we choose to follow this practice as well.
 
@@
 classifier.
+
+\subsection{Support Vector Machines}
+Support Vector Machines (SVM) attempt to separate data
+along hyperplanes \cite{aggarwal2015data}. 
+SVM offer a convex alternative to MLPs \cite{Suykens2002least}.
+A convex classifier is guaranteed to converge to a global solution
+regardless of its initialization.
+Non-separable data can become separable if projected to a different
+possibly high dimensional space through a Kernel function.
+The Kernel trick allows SVM to solve some non-linear
+classification problems \cite{Suykens2002least}.
+Radial basis functions (RBF) are commonly chosen as kernels
+\cite{Suykens2002least}, therefore, we choose to follow this practice as well.
 

### 2020-12-09 02_Paper/paper.tex
chapter 1 and 2

@@
 For companies aiming at quality leadership, the final quality of any goods produced is vital for market success.
-That is why it is highly important for companies to ensure that every product meets the expected requirements.
+Thus, it is highly important for companies to ensure that every product meets the expected customer and legal requirements.
 The quality control (QC) of production processes and products is one fundamental part of general quality management.
-It contains the measures and activities needed to fulfill specific quality requirements.
-According to Illés, there are diverse established tools and methods of quality control.
-Those methods would have a specific level of focus, from the product level, to the process-management level \cite{illes2017new}.
-In this paper, we focused on the methods related to the QC at the product level.
+It contains the measures and activities needed to fulfill specific quality requirements \cite{mitra2016fundamentals}.
+
+Over the years, diverse methods to ensure the quality of products have been developed.
+Those methods can be grouped on process-oriented or product-oriented \cite{mitra2016fundamentals}.
+Among the most used process-oriented methods, we have auditing, Total Quality Control (TCQ) \cite{illes2017new}, and Poka-Yoke Techniques \cite{Robinson2011UsingPT}.
+For the product-oriented methods, we have the 100\% revision of each produced product \cite{Hinckley1997QC}, and statistical methods like the Statistical Process Control (SPC) \cite{selvamuthu2018introduction}.
+
+With the evolution of machine learning (ML) applications, we expect to enhance the QC by predicting the product quality at the initial stage of production.
+This will not only reduce cost in production, and strengthen the QC process, it will also be part of the predictive analytics tools found in production, which is currently widely used in diverse fields due to its accurate predictions \cite{bishop2006pattern, krauss2019machine}.
+
+The aim of this paper is to implement a functional predictive model in quality assurance for an assembly process in a controlled environment.
+Within the scope of the implementation, we compare three different ML models accuracy, as well as their plausibility at industrial applications.
+As result, we expect to to decrease the gap in literature on this research area, as well as to describe the based of our experiences for future works by describing the lesson learned during this implementation.
+In our work, we applied a case-based research approach \cite{yin2017case} 
+% to answer the research question \AP{what research question?}.
+for our implementation.
+One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
+%This sentence can be deleted if needed
+
+Our paper is structured as follow.
+Section.~\ref{sec:related_works} covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
+Section.~\ref{sec:democell} describe the demonstration cell used on this project.
+It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
+Section.~\ref{sec:ML} explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
+Section.~\ref{sec:experiment} describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
+Finally Section.~\ref{sec:conclusion} express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
+
+\section{Related Works} \label{sec:related_works}% 1 Page
+
+\subsection{Quality control in production} \label{sec:qcp} % Basic books (find summarize) basic concepts
+
+% % Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
+This method is executed by
+% % an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
+In a further step, the findings would be later corrected by another person rather than the auditor \cite{fox1993quality}.
+
+% %Both statistical methods and hundred percent controls can be applied as an audit tool.
+
+% % While the SPC mostly optimizes the capability of the process, for example, the acceptance plan prevents the nonconforming product to be passed and then delivered to the next process or the customer \cite{kurniati2015quality}.
+% % In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
+
+% % Generally, statistical methods are faster than the hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
+those assumptions might lead to errors if the variance of the product quality higher than expected.
+
+% % The concept of TQC is to extend the scope of quality control to the whole company and product life cycle, by involving all departments of the organization \cite{illes2017new}.
+
+In this paper, we focused on the product-oriented methods at the product level.
 
@@
 Attributes are qualitative measurable characteristics, i.e, color, texture, other. Variables are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}. 
-The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the the posibility of observing trends in the collected data.
+The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the possibility of observing trends in the collected data.
 This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place.
 % With that in mind, predictive quality control is a promising solution.
-
-With the evolution of machine learning (ML) applications, we expect to enhance the QC by predicting the product quality at the initial stage of production.
-This will not only reduce cost in production, and strengthen the QC process, it will also be part of the predictive analytics tools found in production, which is currently widely used in diverse fields due to its accurate predictions \cite{bishop2006pattern, krauss2019machine}.
-
-The aim of this paper is to implement a functional predictive model in quality assurance for an assembly process in a controlled environment.
-Within the scope of the implementation, we compare three different ML models accuracy, as well as their plausibility at industrial applications.
-As result, we expect to to decrease the gap in literature on this research area, as well as to describe the based of our experiences for future works by describing the lesson learned during this implementation.
-In our work, we applied a case-based research approach \cite{yin2017case} 
-% to answer the research question \AP{what research question?}.
-for our implementation.
-One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
-%This sentence can be deleted if needed
-
-Our paper is structured as follow.
-Section.~\ref{sec:related_works} covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
-Section.~\ref{sec:democell} describe the demonstration cell used on this project.
-It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
-Section.~\ref{sec:ML} explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
-Section.~\ref{sec:experiment} describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
-Finally Section.~\ref{sec:conclusion} express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
-
-% This paper is divided in 6 sections:
-% \begin{itemize}
-%        \item \textbf{Introduction}, states the motivation of the project as well as the problem it intended to be addressed.
-%        \item \textbf{Related Works}, covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
-%        \item \textbf{The case industry 4.0 demonstration cell}, describe the demonstration cell used on this project.
-It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
-%        \item \textbf{Machine learning Methods}, explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
-%        \item \textbf{Experiments}, describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
-%        \item \textbf{Conclusion}, express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
-% \end{itemize}
-
-\section{Related Works} \label{sec:related_works}% 1 Page
-
-% \subsection{Quality control in production} \label{sec:qcp} % Basic books (find summarize) basic concepts
-
-% The quality control of production processes and products is one fundamental part of general quality management.
-It contains the measures and activities needed to fulfill specific quality requirements.
-% % According to Illés, there are three established tools and methods of quality control:
-% % The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC) \cite{illes2017new}. 
-% According to Illés, there are diverse established tools and methods of quality control.
-Those methods would have a specific level of focus, from the product level, to the process-management level \cite{illes2017new}.
-In this paper, we focused on the methods related to the QC at the product level.
-
-% The Statistical Process Control (SPC) method is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes in the quality characteristics in the production process.
-SPC methods can also take place before the actual manufacturing process, this is commonly known as "off-line SPC" \cite{selvamuthu2018introduction}.
-% During the design phase of a process or product, off-line SPC procedures are deployed.
-These procedures aim to increase the quality of the outcoming product by choosing conforming products and  process parameters \cite{mitra2016fundamentals}.
-% The biggest advantage of working with SPC is that large batches can be checked without major time impact on the QC process, however, this would be only possible if the variance of the process product parameters is small enough, to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
-% It is important to remark that statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and the hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
-Which means, if a batch is labeled as NOK, there is no specific reference of when did the error occurs and how many pieces are affected.
-
-% Another conservative technique to perform the quality check would be to check 100\% of the produced parts.
-In this method, every product is controlled and sorted at designated quality levels.
-However, this has the disadvantage of high cost related to personal or specialized material.
-Generally, this method is used when the consequences of letting a defective item through could be severe, e.g., for specialized equipment or when the cost of delivering faulty products is very high \cite{Hinckley1997QC}.
-
-% % Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
-This method is executed by
-% % an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
-In a further step, the findings would be later corrected by another person rather than the auditor \cite{fox1993quality}.
-
-% %Both statistical methods and hundred percent controls can be applied as an audit tool.
-
-% % While the SPC mostly optimizes the capability of the process, for example, the acceptance plan prevents the nonconforming product to be passed and then delivered to the next process or the customer \cite{kurniati2015quality}.
-% % In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
-
-% % Generally, statistical methods are faster than the hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
-those assumptions might lead to errors if the variance of the product quality higher than expected.
-
-% % The concept of TQC is to extend the scope of quality control to the whole company and product life cycle, by involving all departments of the organization \cite{illes2017new}.
-
-% The quality characteristics of a product can be classified as variables or attributes.
-% Attributes are qualitative measurable characteristics, i.e, color, texture, other. Variables are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}. 
-% The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the the posibility of observing trends in the collected data.
-This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place.
-With that in mind, predictive quality control is a promising solution.
 

### 2020-12-09 02_Paper/paper.tex
Introduction

@@
 
-Over the years, diverse methods to ensure the quality of products have been developed.
-Those methods can be grouped on process-oriented or product-oriented \cite{mitra2016fundamentals}.
-Among the most used process-oriented methods, we have auditing, Total Quality Control (TCQ) \cite{illes2017new}, and Poka-Yoke Techniques \cite{Robinson2011UsingPT}.
-For the product-oriented methods, we have the 100\% revision of each produced product \cite{Hinckley1997QC}, and statistical methods like the Statistical Process Control (SPC) \cite{selvamuthu2018introduction}.
+Over the years, diverse methods to ensure the quality of products have been developed \cite{mitra2016fundamentals}.
+Among the most used methods, we have Auditing, Total Quality Control (TCQ) \cite{illes2017new}, Poka-Yoke Techniques \cite{Robinson2011UsingPT}, the 100\% revision of each produced product \cite{Hinckley1997QC}, and statistical methods like the Statistical Process Control (SPC) \cite{selvamuthu2018introduction}.
+Independently of the method used, the goal is the same, identify and removed any defect or faulty pieces on the produced products before sending them to costumers \cite{mitra2016fundamentals}.
+However, the relationship between cost-efficiency vary from one method to another.
+This is noticeable, e.g., at the cost of highly specialized equipment for the products evaluation, or the cost of employes performing a manual inspection of the produced products versus the accuracy of detecting all faulty products \cite{Diego1998QCCost}.
 
-With the evolution of machine learning (ML) applications, we expect to enhance the QC by predicting the product quality at the initial stage of production.
-This will not only reduce cost in production, and strengthen the QC process, it will also be part of the predictive analytics tools found in production, which is currently widely used in diverse fields due to its accurate predictions \cite{bishop2006pattern, krauss2019machine}.
+In general, the quality characteristics of a product can be classified as variables or attributes.
+"Attributes" are qualitative measurable characteristics, i.e, color, texture, other.
+On the other hand, "variables" are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}.
+The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the possibility of observing trends in the collected data.
+This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place \cite{bishop2006pattern, krauss2019machine}.
 
-The aim of this paper is to implement a functional predictive model in quality assurance for an assembly process in a controlled environment.
-Within the scope of the implementation, we compare three different ML models accuracy, as well as their plausibility at industrial applications.
-As result, we expect to to decrease the gap in literature on this research area, as well as to describe the based of our experiences for future works by describing the lesson learned during this implementation.
-In our work, we applied a case-based research approach \cite{yin2017case} 
-% to answer the research question \AP{what research question?}.
-for our implementation.
-One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
+% Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model},Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}, and others focused on one product quality analysis \cite{Selmaier2019PQXray, Sohnius2019PASurfacequality}.
+
+With the evolution of machine learning (ML) applications \cite{goodfellow2016deep}, related works which combines QC and predictive models are becoming more relevant.
+The applications diversify from the analysis of the produced piece in search for defects \cite{Selmaier2019PQXray, Sohnius2019PASurfacequality}, to process oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}.
+
+Considering the high amount of data available at today industries, an approach to improve the existent relationship between cost-efficiency and QC accuracy would be to implement a ML model capable to predict the product quality based on the initial state of the machine.
+This will not only help to detect faulty pieces before the QC process is done, it would also strengthen the current QC methods by combining them as to compensate their weakness.
+While implementing ML models to QC, several challenges arise that have not yet been solved.
+In this paper, we address the following questions:
+
+\begin{itemize}
+       \item Where to test predictive analytics models in a controlled industrial environment?
+       \item What to consider when evaluating the output from ML models for industrial applications? Accuracy vs Applicability
+       \item What steps should be follow as to prepared the data for predictive QC methods?
+       \item What findings and lessons are worth to consider for further applications in the area?
+\end{itemize}
+
+%% Next paragraph: not relevant based on kkb : "First of all, you do not use a CBR approach because those have a clear methodology to follow with the minimum requirement to explain how your findings relate to further cases which i do not find in the paper.
+Then, you never pick up that though again after this point, so why mention it at all?
+I suggest you throw it out."
+% For this, we applied a case-based research approach \cite{yin2017case} to answer the research questions.
+% One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
 %This sentence can be deleted if needed
 
-Our paper is structured as follow.
+For this, we cover the methods used in quality check in production, as well as the bases of predictive analytics in production (Section.~\ref{sec:related_works}). 
+We describe a suitable insdustrial platform to implement the ML models (Section.~\ref{sec:democell}).
+Then we explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
+Finally we describe the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:conclusion}).
+
+% Our paper is structured as follow.
 Section.~\ref{sec:related_works} covers the methods used in quality check in production, as well as the bases of predictive analytics in production.

### 2020-12-09 02_Paper/paper.tex
Introduction

@@
 Considering the high amount of data available at today industries, an approach to improve the existent relationship between cost-efficiency and QC accuracy would be to implement a ML model capable to predict the product quality based on the initial state of the machine.
-This will not only help to detect faulty pieces before the QC process is done, it would also strengthen the current QC methods by combining them as to compensate their weakness.
+This will not only help to detect faulty products before the QC process is done, it would also strengthen the current QC methods by combining them with QC predictive models as to compensate their current weakness.
 While implementing ML models to QC, several challenges arise that have not yet been solved.
@@
 We describe a suitable insdustrial platform to implement the ML models (Section.~\ref{sec:democell}).
-Then we explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
+Then, we explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
 Finally we describe the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:conclusion}).
@@
 
-% Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
-This method is executed by
-% an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
-In a further step, the findings would be later corrected by another person rather than the auditor \cite{fox1993quality}.
-
-%Both statistical methods and hundred percent controls can be applied as an audit tool.
-
-% While the SPC mostly optimizes the capability of the process, for example, the acceptance plan prevents the nonconforming product to be passed and then delivered to the next process or the customer \cite{kurniati2015quality}.
-% In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
-
-% Generally, statistical methods are faster than the hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
-those assumptions might lead to errors if the variance of the product quality higher than expected.
-
-% The concept of TQC is to extend the scope of quality control to the whole company and product life cycle, by involving all departments of the organization \cite{illes2017new}.
-
 The quality characteristics of a product can be classified as variables or attributes.
@@
 Most of the related works found, tends to be from recent years \cite{krauss2020automated, krauss2019machine, aumi2012model,Selmaier2019PQXray, Sohnius2019PASurfacequality, ritter1992neue}.
-% Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model},Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}, and others focused on one product quality analysis \cite{Selmaier2019PQXray, Sohnius2019PASurfacequality}.
-
-% By considering the lack of literature, our goal is to decrease this gap in the research area by implementing a functional predictive model in quality assurance for an assembly process, as well as describing the lesson learned during this implementation.
-To do so, we need to select the right testing platform.
-It has to have a clear production process, complete access to sensor data, and flexible enough to reprogram the process if necessary.
-% In our work, we applied a case-based research approach \cite{yin2017case} 
-% % to answer the research question \AP{what research question?}.
-% for our implementation.
-% One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
-%This sentence can be deleted if needed.
 

### 2020-12-09 02_Paper/paper.tex
Related works

@@
 
-% For companies aiming at quality leadership, the final quality of any goods produced is vital for market success.
-That is why it is highly important for companies to ensure that every product meets the expected requirements.
-Throughout the years, diverse methods for quality control (QC) have been presented and implemented in production.
-Some of those methods prove to be highly effective, but costly, i.e.
-the inspection of every produced piece (100\% control), either by automated or manual methods, by doing quality inspections based on a portion of the produced pieces and extend the results based on statistical methods, or by reducing the risk of mistakes by intentionally modifying the process to avoid human errors.
-This bears a considerable risk of not detecting faulty-parts (NOK) and sending them to costumers \cite{fox1993quality, Robinson2011UsingPT}.
-
-% Whenever a QC method is selected, it is important to remark that compromises must be made in most cases.
-For example, traditional methods like controlling every produced piece might affect have a considerable impact in the production, due to the \AP{review}
-
-% goals by delaying the production speed at the cost of lower rejection rates On the other hand, higher production speeds normally requires statistical quality control methods.
-However, those methods do not provide one hundred percent certainty that the required product quality will be achieved \cite{selvamuthu2018introduction, kurniati2015quality}.
-
 For companies aiming at quality leadership, the final quality of any goods produced is vital for market success.
@@
 
-% Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}, Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model},Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}, and others focused on one product quality analysis \cite{Selmaier2019PQXray, Sohnius2019PASurfacequality}.
-
 With the evolution of machine learning (ML) applications \cite{goodfellow2016deep}, related works which combines QC and predictive models are becoming more relevant.
-The applications diversify from the analysis of the produced piece in search for defects \cite{Selmaier2019PQXray, Sohnius2019PASurfacequality}, to process oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}.
+The applications diversify from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}.
 
@@
 
-%% Next paragraph: not relevant based on kkb : "First of all, you do not use a CBR approach because those have a clear methodology to follow with the minimum requirement to explain how your findings relate to further cases which i do not find in the paper.
-Then, you never pick up that though again after this point, so why mention it at all?
-I suggest you throw it out."
-% For this, we applied a case-based research approach \cite{yin2017case} to answer the research questions.
-% One central motivation for a case-based research approach is to gain insights for real needs, rather than to develop theories without practical relevance \cite{cutcheon1993case}.
-%This sentence can be deleted if needed
-
 For this, we cover the methods used in quality check in production, as well as the bases of predictive analytics in production (Section.~\ref{sec:related_works}). 
@@
 
-% Our paper is structured as follow.
-Section.~\ref{sec:related_works} covers the methods used in quality check in production, as well as the bases of predictive analytics in production.
-Section.~\ref{sec:democell} describe the demonstration cell used on this project.
-It answer the question of where to test predictive analytics in a controlled environment and why our system is a valid platform for this implementation.
-Section.~\ref{sec:ML} explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree.
-Section.~\ref{sec:experiment} describe the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing.
-Finally Section.~\ref{sec:conclusion} express the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations.
-
 \section{Related Works} \label{sec:related_works}% 1 Page
-
-\subsection{Quality control in production} \label{sec:qcp} % Basic books (find summarize) basic concepts
-
-% % Product and process auditing is the independent examination of product and process quality to provide information and it is considered the most fundamental quality control technique.
-This method is executed by
-% % an independent auditor, who based on sampling or checking records limits the finding on reporting incorrect processes procedures or products documentation.
-In a further step, the findings would be later corrected by another person rather than the auditor \cite{fox1993quality}.
-
-% %Both statistical methods and hundred percent controls can be applied as an audit tool.
-
-% % While the SPC mostly optimizes the capability of the process, for example, the acceptance plan prevents the nonconforming product to be passed and then delivered to the next process or the customer \cite{kurniati2015quality}.
-% % In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
-
-% % Generally, statistical methods are faster than the hundred percent controls, however, their disadvantage is that those methods are based on assumptions.
-those assumptions might lead to errors if the variance of the product quality higher than expected.
-
-% % The concept of TQC is to extend the scope of quality control to the whole company and product life cycle, by involving all departments of the organization \cite{illes2017new}.
-
-In this paper, we focused on the product-oriented methods at the product level.
-
-The Statistical Process Control (SPC) method is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes in the quality characteristics in the production process.
-SPC methods can also take place before the actual manufacturing process, this is commonly known as "off-line SPC" \cite{selvamuthu2018introduction}.
-During the design phase of a process or product, off-line SPC procedures are deployed.
-These procedures aim to increase the quality of the outcoming product by choosing conforming products and  process parameters \cite{mitra2016fundamentals}.
-The biggest advantage of working with SPC is that large batches can be checked without major time impact on the QC process, however, this would be only possible if the variance of the process product parameters is small enough, to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
-It is important to remark that statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and the hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
-Which means, if a batch is labeled as NOK, there is no specific reference of when did the error occurs and how many pieces are affected.
-
-Another conservative technique to perform the quality check would be to check 100\% of the produced parts.
-In this method, every product is controlled and sorted at designated quality levels.
-However, this has the disadvantage of high cost related to personal or specialized material.
-Generally, this method is used when the consequences of letting a defective item through could be severe, e.g., for specialized equipment or when the cost of delivering faulty products is very high \cite{Hinckley1997QC}.
-
-The quality characteristics of a product can be classified as variables or attributes.
-Attributes are qualitative measurable characteristics, i.e, color, texture, other. Variables are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}. 
-The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the possibility of observing trends in the collected data.
-This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place.
-% With that in mind, predictive quality control is a promising solution.
-
-\subsection{Predictive analytics in production}
 
@@
 According to Krauß, there is a wide range of applications for PA in the industrial and production environment.
-Some common industrial applications of PA in the industry are focused products (design and optimization), machines and assets (predictive maintenance, anomaly detection, self learning-machines) and process (scheduling, process design, predictive process control)\cite{krauss2019machine}
+Some common industrial applications of PA in the industry are focused products (design and optimization), machines and assets (predictive maintenance, anomaly detection, self learning-machines) and process (scheduling, process design, predictive process control) \cite{krauss2019machine}.
+
+An explorative literature review on this matter reveals that publications that combine PA and QC became more relevant in the last 6 years.
+This could be in great part, due to computer power limitations in early research phase and the recent increase of ML applications in this area.
+Related works are mostly allocated into two groups, defects analysis of produced pieces and process oriented QC.
+Due to the recent advances in ML approaches specialized in image and patterns recognition \cite{bishop2006pattern}, a great number of publications are focused on the products analysis based on images from cameras during the production process,
+e.g., Escobar employs pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focus on defect predection within a printed layers by employing a surpervised models based on features extracted directly from the machine code and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
+Other authors focus their research into process oriented QC, e.g., 
+Krauß focused on describing the ML pipeline to implement automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}; Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model},Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}
 
@@
 By employing machine learning (ML) techniques, see Sec.~\ref{sec:ML}, together with traditional methods, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
-
-Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature.
-This could be in great part, due to computer power limitations in early research and the recent increase of ML applications in this area.
-Most of the related works found, tends to be from recent years \cite{krauss2020automated, krauss2019machine, aumi2012model,Selmaier2019PQXray, Sohnius2019PASurfacequality, ritter1992neue}.
+However, before implementing these techniques, it is important to define the platform where these predictive analytics models will be implemented in a controlled and transparent industrial environment.
 
@@
 Our case of study is an abstraction of an assembly process of the industry.
+This platform is highly flexible and transparent regarding software and hardware access and manipulation.
 The industry 4.0 demonstration cell is composed of three independent conveyor belts, a robotic assembly arm (UR3), a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200, see Figure~\ref{fig:ind_cell}.

### 2020-12-09 02_Paper/paper.tex
minor word changes

@@
 \begin{itemize}
-       \item Where to test predictive analytics models in a controlled industrial environment?
+       % \item Where to test predictive analytics models in a controlled industrial environment?
        \item What to consider when evaluating the output from ML models for industrial applications? Accuracy vs Applicability
@@
 
-An explorative literature review on this matter reveals that publications that combine PA and QC became more relevant in the last 6 years.
-This could be in great part, due to computer power limitations in early research phase and the recent increase of ML applications in this area.
+An explorative literature review on this matter reveals that publications that combine PA and QC became more relevant in the last six years.
+This could be in great part, due to computer power limitations in the early research phase and the recent increase of ML applications in this area.
 Related works are mostly allocated into two groups, defects analysis of produced pieces and process oriented QC.
@@
 Other authors focus their research into process oriented QC, e.g., 
-Krauß focused on describing the ML pipeline to implement automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}; Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model},Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}
+Krauß focused on describing the ML pipeline to implement automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}; Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}; Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}.
 
 Applications that combine PA with QC might improve the current QC processes.
-By employing machine learning (ML) techniques, see Sec.~\ref{sec:ML}, together with traditional methods, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
+By employing machine learning (ML) techniques (Section.~\ref{sec:ML}), together with traditional methods, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
 However, before implementing these techniques, it is important to define the platform where these predictive analytics models will be implemented in a controlled and transparent industrial environment.

### 2020-12-10 02_Paper/paper.tex
update author name
Chapter 1 and 2

@@
 \author[a]{Johannes Wagner}
-\author[a]{Benjamin Koke}
+\author[a]{Benjamin Heinbach}
 \author[a]{Fabian Steinberg} 
@@
 For companies aiming at quality leadership, the final quality of any goods produced is vital for market success.
-Thus, it is highly important for companies to ensure that every product meets the expected customer and legal requirements.
+Thus, companies need to ensure that every product meets the expected customer and legal requirements.
 The quality control (QC) of production processes and products is one fundamental part of general quality management.
@@
 Over the years, diverse methods to ensure the quality of products have been developed \cite{mitra2016fundamentals}.
-Among the most used methods, we have Auditing, Total Quality Control (TCQ) \cite{illes2017new}, Poka-Yoke Techniques \cite{Robinson2011UsingPT}, the 100\% revision of each produced product \cite{Hinckley1997QC}, and statistical methods like the Statistical Process Control (SPC) \cite{selvamuthu2018introduction}.
-Independently of the method used, the goal is the same, identify and removed any defect or faulty pieces on the produced products before sending them to costumers \cite{mitra2016fundamentals}.
-However, the relationship between cost-efficiency vary from one method to another.
-This is noticeable, e.g., at the cost of highly specialized equipment for the products evaluation, or the cost of employes performing a manual inspection of the produced products versus the accuracy of detecting all faulty products \cite{Diego1998QCCost}.
+Among the most used methods, we have Auditing, Total Quality Control (TCQ) \cite{illes2017new}, Poka-Yoke Techniques \cite{Robinson2011UsingPT}, the 100\% control of each produced product \cite{Hinckley1997QC}, and statistical methods like the Statistical Process Control (SPC) \cite{selvamuthu2018introduction}.
+Independently of the method used, the goal is the same, to avoid the production, or to identify and remove faulty products before delivering those to the customer.\cite{mitra2016fundamentals}.
+However, the relationship between cost and efficiency varies from one method to another.
+This is noticeable, e.g., at the cost of highly specialized equipment for automated inspection, or the cost of employes performing a manual inspection of the produced products versus the accuracy of detecting all faulty products \cite{Diego1998QCCost}.
 
-In general, the quality characteristics of a product can be classified as variables or attributes.
-"Attributes" are qualitative measurable characteristics, i.e, color, texture, other.
-On the other hand, "variables" are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}.
+In general, the quality characteristics of a product can be classified as attributes or variables.
+\textit{Attributes} are qualitative measurable characteristics, i.e., color or texture.
+On the other hand, \textit{variables} are quantitative measurable characteristics, which are shown as numbers, i.e., length or width \cite{mitra2016fundamentals}.
 The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the possibility of observing trends in the collected data.
@@
 
-With the evolution of machine learning (ML) applications \cite{goodfellow2016deep}, related works which combines QC and predictive models are becoming more relevant.
-The applications diversify from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}.
+With the evolution of machine learning (ML) applications \cite{goodfellow2016deep}, approaches combining QC and predictive models are becoming more relevant.
+The applications diversify from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process-oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}, see Section.~\ref{sec:related_works}.
+Independently of the research group previous stated, within the scope of the related works, there is no evidence of an evaluation framework for diverse ML techniques applied in QC process.
 
-Considering the high amount of data available at today industries, an approach to improve the existent relationship between cost-efficiency and QC accuracy would be to implement a ML model capable to predict the product quality based on the initial state of the machine.
-This will not only help to detect faulty products before the QC process is done, it would also strengthen the current QC methods by combining them with QC predictive models as to compensate their current weakness.
-While implementing ML models to QC, several challenges arise that have not yet been solved.
-In this paper, we address the following questions:
+Considering the high amount of data available in today's industries, one possible approach to reduce the inspection costs and simultaneously  increase the accuracy would be to implement an ML model capable to predict the product quality based on the initial state of the machine.
+This will not only help to detect faulty products before the QC process is performed, it would also strengthen the current QC methods by combining them with QC predictive models to compensate for their current weakness.
 
-\begin{itemize}
-       % \item Where to test predictive analytics models in a controlled industrial environment?
-       \item What to consider when evaluating the output from ML models for industrial applications? Accuracy vs Applicability
-       \item What steps should be follow as to prepared the data for predictive QC methods?
-       \item What findings and lessons are worth to consider for further applications in the area?
-\end{itemize}
-
+While implementing ML models to QC, several challenges arise that have not yet been completely addressed, e.g., what to consider while evaluating the output from ML models for industrial applications?
+(model accuracy vs applicability at industrial environments); what steps should be followed to prepare the data for predictive QC methods?; and what findings and lessons are worth to consider for further applications in the area?.
 For this, we cover the methods used in quality check in production, as well as the bases of predictive analytics in production (Section.~\ref{sec:related_works}). 
-We describe a suitable insdustrial platform to implement the ML models (Section.~\ref{sec:democell}).
+We describe a suitable industrial platform to implement the ML models (Section.~\ref{sec:democell}).
 Then, we explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
-Finally we describe the remarks and discoveries achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:conclusion}).
+Finally, we describe the remarks and findings achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:conclusion}).
 
@@
 This could be in great part, due to computer power limitations in the early research phase and the recent increase of ML applications in this area.
-Related works are mostly allocated into two groups, defects analysis of produced pieces and process oriented QC.
-Due to the recent advances in ML approaches specialized in image and patterns recognition \cite{bishop2006pattern}, a great number of publications are focused on the products analysis based on images from cameras during the production process,
-e.g., Escobar employs pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focus on defect predection within a printed layers by employing a surpervised models based on features extracted directly from the machine code and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
-Other authors focus their research into process oriented QC, e.g., 
+Related works are mostly allocated into two groups, defects analysis of produced pieces and process-oriented QC.
+Due to the recent advances in ML approaches specialized in image and patterns recognition \cite{bishop2006pattern}, a great number of publications are focused on the products-analysis based on images from cameras during the production process,
+e.g., Escobar employs pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focus on defect prediction within printed layers by employing supervised models based on features extracted directly from the machine code and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
+Other authors focus their research in process-oriented QC, e.g., 
 Krauß focused on describing the ML pipeline to implement automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}; Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}; Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}.
@@
 Applications that combine PA with QC might improve the current QC processes.
-By employing machine learning (ML) techniques (Section.~\ref{sec:ML}), together with traditional methods, it would be possible to upgrade the currents QC methods, and improve the cost-efficiency relationship in the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
+However, based on the previous findings, there are no clear references to the impact of implementing ML models based just on model accuracy, together with industrial factors of the QC process.
+By employing machine learning (ML) techniques (Section.~\ref{sec:ML}), together with the QC traditional methods, it would be possible to upgrade, and to improve the relationship between inspection costs and the probability of detecting faulty products during the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
 However, before implementing these techniques, it is important to define the platform where these predictive analytics models will be implemented in a controlled and transparent industrial environment.
@@
 Our case of study is an abstraction of an assembly process of the industry.
-This platform is highly flexible and transparent regarding software and hardware access and manipulation.
+This case of study is a highly flexible and transparent platform regarding software and hardware access and manipulation.
 The industry 4.0 demonstration cell is composed of three independent conveyor belts, a robotic assembly arm (UR3), a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200, see Figure~\ref{fig:ind_cell}.
@@
 
-Those simulated failures have an impact in the data collected by the sensors.
+Those simulated failures have an impact on the data collected by the sensors.
 Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticeable shifting on pieces' position as well as the stop of the process.
@@
 \cite{aggarwal2015data}. For example by comparison to a threshold value.
-To construct the tree these cutoff values have to be chosen
-at every branch. The construction problem turns into an optimization 
-problem when a split criterion is introduced. Common choices are 
-cross-entropy of Gini-coefficient \cite{aggarwal2015data}.
+To construct the tree these cutoff values have to be chosen at every branch.
+The construction problem turns into an optimization problem when a split criterion is introduced.
+Common choices are cross-entropy of Gini-coefficient \cite{aggarwal2015data}.
 During construction, the chosen function must be minimized.
@@
 
-\textbf{Data interpretation}; this process is considered complicate, time-consuming, and fundamental step on any ML applications.
+\textbf{Data interpretation}; this process is considered complicated, time-consuming, and a fundamental step for any ML applications.
 It is fundamental to understand the assembly process, the timing from the machine movements, the boundaries of the machine's sensors, as well a basic correlation within the presented data.

### 2020-12-10 02_Paper/paper.tex
Fixed comments from DSt

@@
 However, the relationship between cost and efficiency varies from one method to another.
-This is noticeable, e.g., at the cost of highly specialized equipment for automated inspection, or the cost of employes performing a manual inspection of the produced products versus the accuracy of detecting all faulty products \cite{Diego1998QCCost}.
+This is noticeable, e.g., at the cost of highly specialized equipment for automated inspection, or the cost of employees performing a manual inspection of the produced products versus the accuracy of detecting all faulty products \cite{Diego1998QCCost}.
 
@@
 We describe a suitable industrial platform to implement the ML models (Section.~\ref{sec:democell}).
-Then, we explains the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
+Then, we explain the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
 Finally, we describe the remarks and findings achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:conclusion}).
@@
 The executed abstracted assembly process consists of stacking two disks of different sizes on top of each other.
-These pseudo product quality are later determined by the laser scanner by evaluating the concentricity of both disks.
+The corresponding pseudo product quality is later determined by the laser scanner by evaluating the concentricity of both disks.
 If the disks' concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it is classified as NOK.
@@
 
-The continuous data collection and the clear correlation between the machine parameters is the ideal play-ground to implement a sandbox for machine learning implementations.
+The continuous data collection and the clear correlation between the machine parameters and the quality of the product, is the ideal play-ground to implement a sandbox for machine learning implementations.
 With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner.
@@
 To avoid that problem, universal protocols are often implemented at industrial projects.
-This is the case for our industrial 4.0 demonstration cell, which shares data via the protocol OPC-UA.
+This is the case for our industry 4.0 demonstration cell, which shares data via the protocol OPC-UA.
 
@@
 In our implementation, we acquired the data in two steps.
-The first step was list all the variables of interest and to map their source.
+The first step consisted of listing all the variables of interest and mapping their source.
 The second step was to determine the use cases of interest.
@@
        \end{adjustbox}
-       \caption{Industriy 4.0 demonstration cell: Relevant data linked with its reference source server.}
+       \caption{Industry 4.0 demonstration cell: Relevant data linked with its reference source server.}
        \label{tab:data_source}
@@
        \end{tabular}
-       \caption{Industrial 4.0 demostration cell: Controlled Use-Cases.
-       Use-Cases which the value \textit{Robot position: NOK} and \textit{Conveyor speed: Too Fast} will result in NOK pieces.}
+       \caption{Industry 4.0 demostration cell: Controlled Use-Cases.
+       Use-Cases with the value \textit{Robot position: NOK} and \textit{Conveyor speed: Too Fast} will result in NOK pieces.}
        \label{tab:use_cases}
@@
 At this point, we have a series of data-samples based on time series.
-However, we are not interested in a time series analysis since we want to focus on ML methods based on an atemporal vector approach, therefore it was needed to compress each time-series based data-sample in an atemporal data-sample.
+However, we are not interested in a time series analysis, since having the time parameter would not neccesarily improve the prediction results, but rather make the approach more complex and more data would be needed, therefore it was needed to compress each time-series based data-sample in an atemporal data-sample.
 To eliminate time as a variable in our dataset, we defined a series of rules to be applied in each assembly cycle data-sample:
@@
        \caption{Confusion matrices result of the prediction of 50 test data-points.
-We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs and predictions.
+We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs predictions.
 The tables read from the upper left cell as: true-positive, false-positive, false-negative, true-negative.}
@@
 
-Based on the MLP prediction results presented on Table.~\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
+Based on the MLP prediction results presented on Table.~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
 The false-negative results represent the 12\% of the test sample and the true predictions constitute 88\% of the test data.
@@
 Based on the explorative literature review, we observed that the hundred percent quality check method proves to be the most efficient method to guarantee the final product quality, however, the high implementation cost is its biggest draw-back.
-On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each product until the next bach review might imply a considerable loss of the produced products whenever NOK products are found.
-This is based on the uncertainty of when did the error occurs and how many products are affected.
+On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each product until the next batch review might imply a considerable loss of the produced products whenever NOK products are found.
+This is based on the uncertainty of when did the error occur and how many products are affected.
 
@@
 \textbf{Machine Learning}; careful measurement and  meaningful preprocessing
-of our cell-date was key to the successful application of all three algorithms.
+of our cell-data was key to the successful application of all three algorithms.
 Without the labels, the problem could not have been framed as a supervised 

### 2020-12-10 02_Paper/paper.tex
Fixing typos

@@
 The outcome of the models shows that the random forest performed best followed by the multilinear perceptron and the support vector machine.
-However, by reviewing the confusion matrices presented in Table,~\ref{tab:Confusion_matrix}, multilinear perceptron would be the preferred solution to be implemented at industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
+However, by reviewing the confusion matrices presented in Table.~\ref{tab:Confusion_matrix}, multilinear perceptron would be the preferred solution to be implemented at industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
 

### 2020-12-11 02_Paper/paper.tex
Conclusions and lessons learnt

@@
 %% Example \runauth{C.V. Radhakrishnan et al.}
-\runauth{Author name}
+\runauth{Peter Burggräf et al.}
 
@@
 Then, we explain the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
-Finally, we describe the remarks and findings achieved after the finalization of this project phase, as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:conclusion}).
+Finally, we describe the remarks and findings achieved after the finalization of this project phase (Section.~\ref{sec:conclusion}), as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:lessons}).
 
@@
 
-\subsection{Lesson Learned} % 1/2 Page
+\section{Lesson Learned} \label{sec:lessons} % 1/2 Page
 
-\textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data within each other due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture.
+\textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture.
 To overcome the situation stated above, it was necessary to reprogram big sections of the machine control system.
 
-\textbf{Data synchronization}; two OPC-UA servers were used on this implementation. This lead to a series of data synchronization problems due to differences on the internal clock of both servers.
-In order to solve the issue, it was needed to write a time-stamp synchronization script that was deployed during the data preprocessing phase.
+\textbf{Data synchronization}; two OPC-UA servers were used on this implementation. This lead to a series of data synchronization problems due to differences in the internal clock of both servers.
+To solve the issue, it was needed to write a time-stamp synchronization script that was deployed during the data preprocessing phase.
 Without harmonious time-stamps, determining the production cycle would have been impossible and the input data for the ML model would have been useless, and the model inaccurate.
@@
 \textbf{Adapting the industry 4.0 demonstration cell}; the initial state of the demonstrator was very limited.
-Even though the process was well known, the lack of labels or flags whenever certain actions occurs, made complicated to have accurate data sampling from each assembly cycle.
-In order to overcome this uncertainty, we modify the machine program to raise specify flags whenever certain actions would be executed.
+Even though the process was well known, the lack of labels or flags whenever certain actions occur, made it complicated to have accurate data sampling from each assembly cycle.
+To overcome this uncertainty, we modified the machine program to raise specific flags whenever certain actions were executed.
 
@@
 \section*{Acknowledgments}
-This work was funded by the European Regional Development Fund (ERDF) with the project name "ManuBrain"
+This work was funded by the European Regional Development Fund (ERDF) within the project "ManuBrain".
 

### 2020-12-11 02_Paper/paper.tex
Conclusions

@@
 
-It is important to state that this prediction model is not yet ready to fully replace the statistical methods, not the hundred percent quality check method, since this research is still on its early stages and need further development.
-However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this might compensate one disadvantage of the statistical methods.
+It is important to state that this prediction model is not yet ready to fully replace the statistical methods, nor the hundred percent quality check method, since this research is still in its early stages and needs further development.
+However, a combination of SPC along prediction models could work well together, since the prediction model will evaluate each produced piece, and this might compensate for disadvantages of the statistical methods.
 

### 2020-12-11 02_Paper/paper.tex
5.1 and 5.2

@@
 
-Industrial projects require to work with a variety of sensors and controllers.
+Industrial projects require to work with a variety of sensors and controllers from different manufacturers.
 Thus, there is a risk of incompatibility between technologies.
-To avoid that problem, universal protocols are often implemented at industrial projects.
+To avoid that problem, universal protocols are often implemented in industrial projects.
 This is the case for our industry 4.0 demonstration cell, which shares data via the protocol OPC-UA.
 
-Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell.
-For our case, the data is acquired independently from two OPC-UA servers.
+The Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell.
+In our case, the data is acquired independently from two OPC-UA servers.
 This represents the interaction between multiple servers in real production environments.
 
-In our implementation, we acquired the data in two steps.
-The first step consisted of listing all the variables of interest and mapping their source.
-The second step was to determine the use cases of interest.
-Our study focussed on the data described in Table.~\ref{tab:data_source} and the six use cases described in Table.~\ref{tab:use_cases}.
+Before collecting the data, we need to find the variables of interest and mapping their source, as well as to determine the use cases of interest.
+Our study focussed on the data described in Table~\ref{tab:data_source} and the six use cases described in Table~\ref{tab:use_cases}.
 The data was manually collected by using the software "UAExpert - v1.5.1".
-Approximately 15 hours of data were collected, while equally sampling each use case during the data acquisition time.
+Approximately 15 hours of data were collected in different sessions, while equally sampling each use case during the data acquisition stage.
 
@@
 
-Once enough data is collected, the next step is to clean the raw data and organize it accordingly \cite{goodfellow2016deep}.
-For our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp.
-Since our systems are not completely synchronized, it was needed to calculate the delta-time between servers by referencing each server's base clock.
+Once the data was collected, the next step was to clean the raw data and organize it accordingly \cite{goodfellow2016deep}.
+In our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp.
+Since our systems were not completely synchronized, as common in practice, it was needed to calculate the delta-time between servers by referencing each server's base clock.
 Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.
@@
 Data tags interpretation is an important step in the preprocessing process \cite{goodfellow2016deep}.
-The raw data collected from the sensors is usually tagged by an alphanumeric code predefined by the sensor manufacture.
+The raw data collected from the sensors is usually tagged by an alphanumeric code predefined by the sensor manufacturer.
 To work with the data, it was needed to implement diverse functions which have the task to clean the raw data in a more human-readable form.
-This means to remove samples out of clear boundaries and missing values, as well as to translate the sensor code tags based on a dictionary predefined by the authors.
+This means to remove samples out of clear boundaries and missing values, as well as to translate the sensor code tags based on human-readable words predefined by the authors.
 This last step, might be optional in other implementations, however, it proves to be a great addition for testing purposes.
 
-Once the data is clean and compiled in one directory, our step was to split the data based on the assembly cycle.
-For our purpose, we split the dataset into individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}.
+Once the data is clean and compiled in one directory, the next step was to split the data based on the assembly cycle.
+For our purpose, we split the dataset into individual data-samples with help of the action tags included in the dataset Table~\ref{tab:data_source}.
 Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so.
 At this point, we have a series of data-samples based on time series.
-However, we are not interested in a time series analysis, since having the time parameter would not neccesarily improve the prediction results, but rather make the approach more complex and more data would be needed, therefore it was needed to compress each time-series based data-sample in an atemporal data-sample.
-To eliminate time as a variable in our dataset, we defined a series of rules to be applied in each assembly cycle data-sample:
+However, we are not interested in a time series analysis, since having the time parameter would not necessarily improve the prediction results, but rather make the approach more complex, and more data would be needed, therefore it was needed to compress each time-series based data-sample into atemporal data-samples.
+
+Each time-series sample collected is the result of data collected during one machine assembly cycle (MAC).
+The starting point of one MAC is the very first moment the robotic arm grabs the black disk from the store area and the ending point is before grabbing the next black disk in the same area.
+To eliminate time as a variable in our dataset, it was needed to acquire the data at specific moments of the MAC.
+For that reason, we defined a set of sampling-conditions that helped us to collect the relevant data during the MAC:
 
@@
 
-Each time-series sample was evaluated based on the rules stated above, and the result of each evaluation was considered as our atemporal data-sample, which we used as the base for our classifier.
+Each time-series sample was evaluated based this sampling-condition, and the result of each evaluation was considered as our atemporal data-sample, which we used as the base for our classifier.
 
@@
 
-Based on the MLP prediction results presented on Table.~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
+Based on the MLP prediction results presented on Table~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
 The false-negative results represent the 12\% of the test sample and the true predictions constitute 88\% of the test data.
@@
 The outcome of the models shows that the random forest performed best followed by the multilinear perceptron and the support vector machine.
-However, by reviewing the confusion matrices presented in Table.~\ref{tab:Confusion_matrix}, multilinear perceptron would be the preferred solution to be implemented at industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
+However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, multilinear perceptron would be the preferred solution to be implemented at industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
 

### 2020-12-11 02_Paper/paper.tex
5.3 based on wgn comments

@@
 For that reason, we defined a set of sampling-conditions that helped us to collect the relevant data during the MAC:
-
 \begin{itemize}
@@
                 position in the system. The changes in the grip flag are triggered,
-                when the gripper opens or closes. Zero indicates an open, while
-                one indicates a closed gripper. The position flags marks the state
+                when the gripper opens or closes. 0 indicates an open, while
+                one indicates a closed gripper. The position flags mark the state
                 of the cell's arm. 0 means the black disk is in store,
@@
 We compare a total of three different classifier architectures on the data.
-A Support Vector Machine (SVM), a multilinear perceptron (MLP) and a Random Forest
+A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Random Forest
 structure. All three methods are trained using standard hyperparameters.
@@
        \end{tabular}
-       \caption{Comparison of Support Vector Machine (SVM), Multilinear Perceptron and 
+       \caption{Comparison of Support Vector Machine (SVM), Multilayer Perceptron and 
                 Random Forest classification on our anomaly detection task. 
@@
 \end{table}
+
+\AP{According to Prof. Garcke, we should stick either with "Random Forest" or with "Decision Tree". I would like you, Moritz, to decide what would be the best for this case.}
 
@@
 We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs predictions.
-The tables read from the upper left cell as: true-positive, false-positive, false-negative, true-negative.}
+The tables read from the upper-left cell to the right-cell as: true-positive, false-positive, false-negative, true-negative.}
        \label{tab:Confusion_matrix}
@@
 
-Based on the MLP prediction results presented on Table~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} shows that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
+Based on the MLP prediction results presented on Table~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} show that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
 The false-negative results represent the 12\% of the test sample and the true predictions constitute 88\% of the test data.
 
-The outcome of the models shows that the random forest performed best followed by the multilinear perceptron and the support vector machine.
-However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, multilinear perceptron would be the preferred solution to be implemented at industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
+The outcome of the models shows that the random forest performed best followed by the multilayer perceptron and the support vector machine.
+However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, multilayer perceptron would be the preferred solution to be implemented in industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
 

### 2020-12-11 02_Paper/paper.tex
Minor changes

@@
 This paper presents a solution for predictive analytics in QA based on machine sensor values during
-production while employing machine-learning models based on logistic regression in a controlled environment. 
+production while employing specialized machine-learning models for classification in a controlled environment. 
 Furthermore, we present lessons learned while implementing this model, which helps to reduce complexity in
@@
 
-Our case of study is an abstraction of an assembly process of the industry.
-This case of study is a highly flexible and transparent platform regarding software and hardware access and manipulation.
+Our case study is an abstraction of an assembly process of the industry.
+This case study is a highly flexible and transparent platform regarding software and hardware access and manipulation.
 The industry 4.0 demonstration cell is composed of three independent conveyor belts, a robotic assembly arm (UR3), a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200, see Figure~\ref{fig:ind_cell}.
@@
 With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner.
-%Last paragraph to review. stn would likely remove it.
-% We expect the findings gained with the demonstration cell to be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability.
-This would be a step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.
 
@@
 \begin{itemize}
-       \item Value of the robot position ($xyz$) while dropping the disk in the storage area
+       \item Value of the robot position ($xyz$) while dropping both disks in the storage area
        \item Mean conveyor speed value per conveyor band

### 2020-12-11 02_Paper/paper.tex
Chair and institutes

@@
 \address[b]{Fraunhofer Institute for Algorithms and Scientific Computing (SCAI), Schloss Birlinghoven 1, Sankt Augustin- 53757, Germany}
-\address[c]{Institut for Numerical Simulation, Universität Bonn, Endenicher Allee 19b, 53115 Bonn}
-\address[d]{Institut for Computer Science, Universität Bonn, Endenicher Allee 19a, 53115 Bonn}
+\address[c]{Institute for Numerical Simulation, Universität Bonn, Endenicher Allee 19b, 53115 Bonn}
+\address[d]{Institute for Computer Science, Universität Bonn, Endenicher Allee 19a, 53115 Bonn}
 

### 2020-12-11 02_Paper/paper.tex
fix table 1.

@@
               Conveyor speed       & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
-              \begin{description}
-                     \item Conveyor: Gate
-                     \item Conveyor: QC
-                     \item Conveyor: Store
-                     \end{description}
+                     Conveyor: Gate \\
+                     Conveyor: QC \\
+                     Conveyor: Store
                      \end{minipage} \\ \hline
@@
               Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
-              \begin{description}
-                     \item UR3 gripper open/close
-                     \item Grab/drop disk based on disk type
-                     \end{description}
+                     UR3 gripper open/close \\
+                     Grab/drop disk based on disk type
                      \end{minipage} \\ \hline
               Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
-              \begin{description}
-                     \item OK-NOK label
-                     \item $xy$ disk deviation from the center point
-                     \item Absolute disk deviation
-                     \end{description}
+                     OK-NOK label \\
+                     $xy$ disk deviation from the center point \\
+                     Absolute disk deviation
                      \end{minipage} \\ \hline
               Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
-              \begin{description}
-                     \item Position
-                     \item Speed
-                     \item Safe to go
-                     \end{description}
+                     Position \\
+                     Speed \\
+                     Safe to go
                      \end{minipage} \\ \hline
               Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
-                     \begin{description}
-                     \item Disk Size
-                     \end{description}
+                     Disk Size
                      \end{minipage} \\ \bottomrule

### 2020-12-11 02_Paper/paper.tex
table 2.

@@
               Use Case 1  & \begin{minipage}[t]{0.25\textwidth}
-                            \begin{description}
-                                   \item Conveyor speed: Slow
-                                   \item Robot position: OK
-                            \end{description}
+                                   Conveyor speed: Slow \\
+                                   Robot position: OK
                             \end{minipage}  \\ \hline
               Use Case 2  & \begin{minipage}[t]{0.25\textwidth}
-                            \begin{description}
-                                   \item Conveyor speed: Slow
-                                   \item Robot position: NOK
-                            \end{description}
+                                   Conveyor speed: Slow \\
+                                   Robot position: NOK
                             \end{minipage}  \\ \hline
               Use Case 3  & \begin{minipage}[t]{0.25\textwidth}
-                            \begin{description}
-                                   \item Conveyor speed: Fast
-                                   \item Robot position: OK
-                            \end{description}
+                                   Conveyor speed: Fast \\
+                                   Robot position: OK
                             \end{minipage}  \\ \hline
               Use Case 4  & \begin{minipage}[t]{0.25\textwidth}
-                            \begin{description}
-                                   \item Conveyor speed: Fast
-                                   \item Robot position: NOK
-                            \end{description}
+                                   Conveyor speed: Fast \\
+                                   Robot position: NOK
                             \end{minipage}  \\ \hline
               Use Case 5  & \begin{minipage}[t]{0.25\textwidth}
-                            \begin{description}
-                                   \item Conveyor speed: Too Fast
-                                   \item Robot position: OK
-                            \end{description}
+                                   Conveyor speed: Too Fast \\
+                                   Robot position: OK
                             \end{minipage}  \\ \hline
               Use Case 6  & \begin{minipage}[t]{0.25\textwidth}
-                            \begin{description}
-                                   \item Conveyor speed: Too Fast
-                                   \item Robot position: NOK
-                            \end{description}
+                                   Conveyor speed: Too Fast \\
+                                   Robot position: NOK
                             \end{minipage}  \\ \bottomrule

### 2020-12-11 02_Paper/paper.tex
remove random forests.

@@
 
-To study which implementation would be more suitable for industrial applications, we compare Multilinear Perceptrons (MLPs), Support Vector Machines (SVM), as well as random forests on the task of quality prediction.
+To study which implementation would be more suitable for industrial applications, we compare Multilayer Perceptrons (MLPs), Support Vector Machines (SVM), as well as decision trees on the task of quality prediction.
 All three will be introduced next.
@@
 We compare a total of three different classifier architectures on the data.
-A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Random Forest
+A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
 structure. All three methods are trained using standard hyperparameters.
@@
        \caption{Comparison of Support Vector Machine (SVM), Multilayer Perceptron and 
-                Random Forest classification on our anomaly detection task. 
+                Decision Tree classification on our anomaly detection task. 
                 The first row shows the performance of naively predicting a broken piece
@@
 \end{table}
-
-\AP{According to Prof. Garcke, we should stick either with "Random Forest" or with "Decision Tree". I would like you, Moritz, to decide what would be the best for this case.}
 
@@
 
-The outcome of the models shows that the random forest performed best followed by the multilayer perceptron and the support vector machine.
+The outcome of the models shows that the decision tree performed best followed by the multilayer perceptron and the support vector machine.
 However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, multilayer perceptron would be the preferred solution to be implemented in industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.

### 2020-12-11 02_Paper/paper.tex
remove random forests.

@@
                      Conveyor: Store
-                     \end{minipage} \\ \hline
+                     \end{minipage} \vspace{0.1cm} \\ \hline
               UR3 Position         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
-              \begin{description}
-                     \item $xyz$ Gripper position
-                     \end{description}
-                     \end{minipage} \\ \hline
+                     $xyz$ Gripper position
+                     \end{minipage} \vspace{0.1cm} \\ \hline
               Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
@@
                      Grab/drop disk based on disk type
-                     \end{minipage} \\ \hline
+                     \end{minipage} \vspace{0.1cm} \\ \hline
               Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
@@
                      Absolute disk deviation
-                     \end{minipage} \\ \hline
+                     \end{minipage} \vspace{0.1cm} \\ \hline
               Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
@@
                      Safe to go
-                     \end{minipage} \\ \hline
+                     \end{minipage} \vspace{0.1cm} \\ \hline
               Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
@@
                                    Robot position: OK
-                            \end{minipage}  \\ \hline
+                            \end{minipage} \vspace{0.1cm}  \\ \hline
               Use Case 2  & \begin{minipage}[t]{0.25\textwidth}
@@
                                    Robot position: NOK
-                            \end{minipage}  \\ \hline
+                            \end{minipage} \vspace{0.1cm}  \\ \hline
               Use Case 3  & \begin{minipage}[t]{0.25\textwidth}
@@
                                    Robot position: OK
-                            \end{minipage}  \\ \hline
+                            \end{minipage} \vspace{0.1cm}  \\ \hline
               Use Case 4  & \begin{minipage}[t]{0.25\textwidth}
@@
                                    Robot position: NOK
-                            \end{minipage}  \\ \hline
+                            \end{minipage} \vspace{0.1cm}  \\ \hline
               Use Case 5  & \begin{minipage}[t]{0.25\textwidth}
@@
                                    Robot position: OK
-                            \end{minipage}  \\ \hline
+                            \end{minipage} \vspace{0.1cm}  \\ \hline
               Use Case 6  & \begin{minipage}[t]{0.25\textwidth}
@@
                                    Robot position: NOK
-                            \end{minipage}  \\ \bottomrule
+                            \end{minipage} \vspace{0.1cm} \\ \bottomrule
        \end{tabular}

### 2020-12-11 02_Paper/paper.tex
add FCML.

@@
 \author[a]{Lennart Schmallenbach}
-\author[b,c]{Jochen Garcke}
+\author[b,c,d]{Jochen Garcke}
 \author[b]{Daniela Steffes-lai}
-\author[b,d]{Moritz Wolter}
+\author[b,c,e]{Moritz Wolter}
 
@@
 \address[b]{Fraunhofer Institute for Algorithms and Scientific Computing (SCAI), Schloss Birlinghoven 1, Sankt Augustin- 53757, Germany}
-\address[c]{Institute for Numerical Simulation, Universität Bonn, Endenicher Allee 19b, 53115 Bonn}
-\address[d]{Institute for Computer Science, Universität Bonn, Endenicher Allee 19a, 53115 Bonn}
+\address[c]{Fraunhofer Center for Machine Learning, Schloss Birlinghoven 1, Sankt Augustin- 53757, Germany}
+\address[d]{Institute for Numerical Simulation, Universität Bonn, Endenicher Allee 19b, 53115 Bonn}
+\address[e]{Institute for Computer Science, Universität Bonn, Endenicher Allee 19a, 53115 Bonn}
 
@@
               Conveyor speed       & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
-                     Conveyor: Gate \\
-                     Conveyor: QC \\
-                     Conveyor: Store
+                     - Conveyor: Gate \\
+                     - Conveyor: QC \\
+                     - Conveyor: Store
                      \end{minipage} \vspace{0.1cm} \\ \hline
               UR3 Position         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
-                     $xyz$ Gripper position
+                     - $xyz$ Gripper position
                      \end{minipage} \vspace{0.1cm} \\ \hline
               Action Flags         & Siemens PLC       & \begin{minipage}[t]{0.2\textwidth}
-                     UR3 gripper open/close \\
-                     Grab/drop disk based on disk type
+                     - UR3 gripper open/close \\
+                     - Grab/drop disk based on type
                      \end{minipage} \vspace{0.1cm} \\ \hline
               Quality control      & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
-                     OK-NOK label \\
-                     $xy$ disk deviation from the center point \\
-                     Absolute disk deviation
+                     - OK-NOK label \\
+                     - $xy$ disk deviation from the center point \\
+                     - Absolute disk deviation
                      \end{minipage} \vspace{0.1cm} \\ \hline
               Gate position        & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
-                     Position \\
-                     Speed \\
-                     Safe to go
+                     - Position \\
+                     - Speed \\
+                     - Safe to go
                      \end{minipage} \vspace{0.1cm} \\ \hline
               Store       & SICK SIM4000      & \begin{minipage}[t]{0.2\textwidth}
-                     Disk Size
+                     - Disk Size
                      \end{minipage} \\ \bottomrule

### 2020-12-11 02_Paper/paper.tex
ML part update.

@@
 Since the linear parts of the ReLU and the linear matrix multiplication
-are differentiable we can employ gradient descent to train our 
-classifier.
+are differentiable we can employ stochastic gradient
+descent to train our classifier.
 
@@
 For numerical input features, each decision partitions the data
-\cite{aggarwal2015data}. For example by comparison to a threshold value.
+\cite{aggarwal2015data}, for example by comparison to a threshold value.
 To construct the tree these cutoff values have to be chosen at every branch.
@@
 Common choices are cross-entropy of Gini-coefficient \cite{aggarwal2015data}.
-During construction, the chosen function must be minimized.
+During construction splits minimizing the chosen function are chosen.
 

### 2020-12-11 02_Paper/paper.tex
parameter comment.
fixed legend Fig 3

@@
 \address[c]{Fraunhofer Center for Machine Learning, Schloss Birlinghoven 1, Sankt Augustin- 53757, Germany}
-\address[d]{Institute for Numerical Simulation, Universität Bonn, Endenicher Allee 19b, 53115 Bonn}
-\address[e]{Institute for Computer Science, Universität Bonn, Endenicher Allee 19a, 53115 Bonn}
+\address[d]{Institute for Numerical Simulation, Universität Bonn, Endenicher Allee 19b, 53115 Bonn, Germany}
+\address[e]{Institute for Computer Science, Universität Bonn, Endenicher Allee 19a, 53115 Bonn, Germany}
 
@@
 Each time-series sample collected is the result of data collected during one machine assembly cycle (MAC).
-The starting point of one MAC is the very first moment the robotic arm grabs the black disk from the store area and the ending point is before grabbing the next black disk in the same area.
+The starting point of one MAC is the very first moment the robotic arm grabs the white disk from the store area and the ending point is before grabbing the next white disk in the same area.
 To eliminate time as a variable in our dataset, it was needed to acquire the data at specific moments of the MAC.
@@
 A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
-structure. All three methods are trained using standard hyperparameters.
-\footnote{To allow exact reproduction of these results source
-code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
+structure.
+All three methods are trained using standard hyperparameters, which we found to work well.
+\footnote{To allow exact reproduction of these results source code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
 
@@
 Within the limits of our work, we predict with 98\% certainty the product quality by implementing a decision tree model with a 6-variables vector as input.
-However, our decision for industrial applications would be the MLP with 88\% accuracy as to guarantee that all passed parts are OK and avoid labeling a NOK piece as OK.
+However, our decision for industrial applications would be the MLP with 88\% accuracy, to guarantee that all passed parts are OK and avoid labeling a NOK piece as OK.
 For further work, we expect to increase the accuracy of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.
@@
 
+Difficulties at implementing ML models in production are also described by others authors \cite{paleyes2020challenges}.
+
 \section*{Acknowledgments}

### 2020-12-11 02_Paper/paper.tex
Introduction

@@
 Among the most used methods, we have Auditing, Total Quality Control (TCQ) \cite{illes2017new}, Poka-Yoke Techniques \cite{Robinson2011UsingPT}, the 100\% control of each produced product \cite{Hinckley1997QC}, and statistical methods like the Statistical Process Control (SPC) \cite{selvamuthu2018introduction}.
-Independently of the method used, the goal is the same, to avoid the production, or to identify and remove faulty products before delivering those to the customer.\cite{mitra2016fundamentals}.
+Independently of the method used, the goal is the same, to avoid the production of faulty products, or to identify and remove them, before delivering those to the customer.\cite{mitra2016fundamentals}.
 However, the relationship between cost and efficiency varies from one method to another.
@@
 
-In general, the quality characteristics of a product can be classified as attributes or variables.
+In general, the quality characteristics of a product can be classified as attributes or variables \cite{mitra2016fundamentals}. 
 \textit{Attributes} are qualitative measurable characteristics, i.e., color or texture.
-On the other hand, \textit{variables} are quantitative measurable characteristics, which are shown as numbers, i.e., length or width \cite{mitra2016fundamentals}.
-The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the possibility of observing trends in the collected data.
-This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place \cite{bishop2006pattern, krauss2019machine}.
+On the other hand, \textit{variables} are precise and measurable characteristics, which are shown as numbers, i.e., length or width.
+The advantage of quantitative measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable controlled adjustment of the process parameters, as well as the possibility of observing trends in the collected data.
+This  enables the employment of predictive models to determine the quality of the product before the QC process takes place \cite{bishop2006pattern, krauss2019machine}.
 
-With the evolution of machine learning (ML) applications \cite{goodfellow2016deep}, approaches combining QC and predictive models are becoming more relevant.
-The applications diversify from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process-oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}, see Section.~\ref{sec:related_works}.
-Independently of the research group previous stated, within the scope of the related works, there is no evidence of an evaluation framework for diverse ML techniques applied in QC process.
+With the evolution of machine learning (ML) applications \cite{bishop2006pattern, Burggraef2018AIinprod}, approaches combining QC and predictive models are becoming more relevant.
+The applications range from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process-oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}, see Section~\ref{sec:related_works}.
+Independently of the research area previously stated, within the scope of the related works, there is no evidence of an evaluation framework for diverse ML techniques applied in QC process.
 
-Considering the high amount of data available in today's industries, one possible approach to reduce the inspection costs and simultaneously  increase the accuracy would be to implement an ML model capable to predict the product quality based on the initial state of the machine.
-This will not only help to detect faulty products before the QC process is performed, it would also strengthen the current QC methods by combining them with QC predictive models to compensate for their current weakness.
+Considering the high amount of data available in nowadays industries, one approach to reduce the inspection costs and simultaneously  increase the accuracy of detecting faulty products would be to implement an ML model capable to predict the product quality based on the initial state of the machine.
+This will not only help to detect faulty products before the QC process is performed, it would also strengthen the current QC methods by combining them with QC predictive models.
 
-While implementing ML models to QC, several challenges arise that have not yet been completely addressed, e.g., what to consider while evaluating the output from ML models for industrial applications?
+While implementing ML models to QC, several challenges arise that have not yet been sufficiently addressed, e.g., what to consider while evaluating the output from ML models for industrial applications?
 (model accuracy vs applicability at industrial environments); what steps should be followed to prepare the data for predictive QC methods?; and what findings and lessons are worth to consider for further applications in the area?.
-For this, we cover the methods used in quality check in production, as well as the bases of predictive analytics in production (Section.~\ref{sec:related_works}). 
-We describe a suitable industrial platform to implement the ML models (Section.~\ref{sec:democell}).
-Then, we explain the three machine learning methods implemented on this work: Multilayer perceptrons, Support Vector Machines, Decision Tree (Section.~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section.~\ref{sec:experiment}).
-Finally, we describe the remarks and findings achieved after the finalization of this project phase (Section.~\ref{sec:conclusion}), as well as presents a list of lessons learned during the implementation of the project, which might be helpful on further implementations (Section.~\ref{sec:lessons}).
+For this, we cover the methods used in quality check in production, as well as the bases of predictive analytics in production (Section~\ref{sec:related_works}). 
+We describe a suitable industrial platform to implement the ML models (Section~\ref{sec:democell}).
+Then, we explain the three machine learning methods implemented in this work: Multilayer perceptrons, Support Vector Machines, and Decision Tree (Section~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section~\ref{sec:experiment}).
+Finally, we present the findings achieved after the finalization of this project phase (Section~\ref{sec:conclusion}), as well as present a list of lessons learned for the implementation of the project, which might be helpful on further implementations (Section~\ref{sec:lessons}).
 
@@
 However, based on the previous findings, there are no clear references to the impact of implementing ML models based just on model accuracy, together with industrial factors of the QC process.
-By employing machine learning (ML) techniques (Section.~\ref{sec:ML}), together with the QC traditional methods, it would be possible to upgrade, and to improve the relationship between inspection costs and the probability of detecting faulty products during the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
+By employing machine learning (ML) techniques (Section~\ref{sec:ML}), together with the QC traditional methods, it would be possible to upgrade, and to improve the relationship between inspection costs and the probability of detecting faulty products during the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
 However, before implementing these techniques, it is important to define the platform where these predictive analytics models will be implemented in a controlled and transparent industrial environment.

### 2020-12-11 02_Paper/paper.tex
related works

@@
 Then, we explain the three machine learning methods implemented in this work: Multilayer perceptrons, Support Vector Machines, and Decision Tree (Section~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section~\ref{sec:experiment}).
-Finally, we present the findings achieved after the finalization of this project phase (Section~\ref{sec:conclusion}), as well as present a list of lessons learned for the implementation of the project, which might be helpful on further implementations (Section~\ref{sec:lessons}).
+Finally, we present the findings achieved after the finalization of this project phase (Section~\ref{sec:conclusion}), as well as present a list of lessons learned for the implementation of the project, which might be helpful for further implementations (Section~\ref{sec:lessons}).
 
@@
 According to Delen and Damirkan, predictive analytics (PA) consists of unraveling the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
-PA offers a wide range of applications, and it can be implemented, as long as the provided data are sufficiently available \cite{bishop2006pattern}.
+PA offers a wide range of applications, and it can be implemented, as long as the sufficiently data are available \cite{bishop2006pattern}.
 According to Krauß, there is a wide range of applications for PA in the industrial and production environment. 
-Some common industrial applications of PA in the industry are focused products (design and optimization), machines and assets (predictive maintenance, anomaly detection, self learning-machines) and process (scheduling, process design, predictive process control) \cite{krauss2019machine}.
+Some common industrial applications of PA are focussed products (design and optimization), machines and assets (predictive maintenance, anomaly detection, self learning-machines) and process (scheduling, process design, predictive process control) \cite{krauss2019machine}.
 
 An explorative literature review on this matter reveals that publications that combine PA and QC became more relevant in the last six years.
-This could be in great part, due to computer power limitations in the early research phase and the recent increase of ML applications in this area.
-Related works are mostly allocated into two groups, defects analysis of produced pieces and process-oriented QC.
-Due to the recent advances in ML approaches specialized in image and patterns recognition \cite{bishop2006pattern}, a great number of publications are focused on the products-analysis based on images from cameras during the production process,
-e.g., Escobar employs pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focus on defect prediction within printed layers by employing supervised models based on features extracted directly from the machine code and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
+This could be due to computer power limitations in earlier research and the recent increase of ML applications in this area.
+Related works are mostly allocated into two groups, defect analysis of produced pieces and process-oriented QC.
+Due to the recent advances in ML approaches specialized in image and pattern recognition \cite{bishop2006pattern}, a great number of publications focus on product-analysis based on images from cameras during the production process,
+e.g., Escobar employs pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focussed on defect prediction within printed layers by employing supervised models based on features extracted directly from the machine code and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
 Other authors focus their research in process-oriented QC, e.g., 
-Krauß focused on describing the ML pipeline to implement automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}; Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}; Ritter studied the ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}.
+Krauß focussed on describing the ML pipeline to implement automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}; Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}; Ritter studied the ways of process modeling on quality prediction and assurance of chipboards \cite{ritter1992neue}.
 
@@
 However, based on the previous findings, there are no clear references to the impact of implementing ML models based just on model accuracy, together with industrial factors of the QC process.
-By employing machine learning (ML) techniques (Section~\ref{sec:ML}), together with the QC traditional methods, it would be possible to upgrade, and to improve the relationship between inspection costs and the probability of detecting faulty products during the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
+By employing machine learning (ML) techniques (Section~\ref{sec:ML}), together with the QC traditional methods, it would be possible to improve the relationship between inspection costs and the probability of detecting faulty products during the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
 However, before implementing these techniques, it is important to define the platform where these predictive analytics models will be implemented in a controlled and transparent industrial environment.

### 2020-12-11 02_Paper/paper.tex
fixed to 6 pages

@@
 Quality assurance (QA) is an important task in manufacturing to assess whether products 
-meet their specifications. However, QA might be expensive, time-consuming, incomplete, or delayed.
+meet their specifications. However, QA might be expensive, time-consuming, or incomplete.
 This paper presents a solution for predictive analytics in QA based on machine sensor values during
@@
 \begin{keyword}
-Machine-Learning \sep Predictive Quality \sep Production \sep Quality Assurance \sep Logistic Regression
+Machine-Learning \sep Predictive Quality \sep Production \sep Quality Assurance \sep Classification
 
@@
 Industrial projects require to work with a variety of sensors and controllers from different manufacturers.
-Thus, there is a risk of incompatibility between technologies.
-To avoid that problem, universal protocols are often implemented in industrial projects.
-This is the case for our industry 4.0 demonstration cell, which shares data via the protocol OPC-UA.
-
-The Figure~\ref{fig:robot_pos_cell} describes a simplified version of the real connection diagram of the demonstration cell.
+Thus, the risk of incompatibility between technologies increases.
+To avoid these problems, universal protocols are often implemented in industrial projects.
+Figure~\ref{fig:demo_conn_diag} describes a simplified version of the real connection diagram of the demonstration cell.
 In our case, the data is acquired independently from two OPC-UA servers.
@@
 
-Once the data was collected, the next step was to clean the raw data and organize it accordingly \cite{goodfellow2016deep}.
+Once the data was collected, the next step was to clean the raw data and organize it accordingly \cite{bishop2006pattern}.
 In our case, that means to merge the data collected from the two OPC-UA servers, and synchronize the time-stamp.
@@
 
-Data tags interpretation is an important step in the preprocessing process \cite{goodfellow2016deep}.
+Data tags interpretation is an important step in the preprocessing process \cite{bishop2006pattern}.
 The raw data collected from the sensors is usually tagged by an alphanumeric code predefined by the sensor manufacturer.
@@
 We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs predictions.
-The tables read from the upper-left cell to the right-cell as: true-positive, false-positive, false-negative, true-negative.}
+The tables read from the upper-left cell as: true-positive, false-positive, false-negative, true-negative.}
        \label{tab:Confusion_matrix}
@@
 
+\section{Lesson Learned} \label{sec:lessons} % 1/2 Page
+
 It is worth to mention the most important points learned during the project implementation. This might help as building blocks for further research in the area.
-
-\section{Lesson Learned} \label{sec:lessons} % 1/2 Page
 

### 2020-12-14 02_Paper/paper.tex
format
exp update.

@@
 structure.
-All three methods are trained using standard hyperparameters, which we found to work well.
-\footnote{To allow exact reproduction of these results source code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
+In this case, we chose to train all three models using standard hyperparameters, which we found to work well.
+\footnote{To allow exact reproduction of our results source code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
 
@@
 
-It is worth to mention the most important points learned during the project implementation. This might help as building blocks for further research in the area.
+It is worth to mention the most important points learned during the project implementation.
+This might help as building blocks for further research in the area.
+Difficulties at implementing ML models in production are also described by others authors \cite{paleyes2020challenges}.
+
+\vspace{0.2cm}
 
@@
 
-Difficulties at implementing ML models in production are also described by others authors \cite{paleyes2020challenges}.
-
 \section*{Acknowledgments}

### 2020-12-14 02_Paper/paper.tex
exp update.
Final revision. Added Author contribution

@@
 \author[a]{Benjamin Heinbach}
-\author[a]{Fabian Steinberg} 
-\author[a]{Alejandro R. Pérez M.*}
+\author[a]{Fabian Steinberg*} 
+\author[a]{Alejandro R. Pérez M.}
 \author[a]{Lennart Schmallenbach}
@@
 
-\address[a]{Chair of International Production Engineering and Management (IPEM), Universität Siegen, Paul-Bonatz-Straße 9-11, Siegen - 57076, Germany}
-\address[b]{Fraunhofer Institute for Algorithms and Scientific Computing (SCAI), Schloss Birlinghoven 1, Sankt Augustin- 53757, Germany}
-\address[c]{Fraunhofer Center for Machine Learning, Schloss Birlinghoven 1, Sankt Augustin- 53757, Germany}
+\address[a]{Chair of International Production Engineering and Management (IPEM), Universität Siegen, Paul-Bonatz-Straße 9-11, 57076 Siegen, Germany}
+\address[b]{Fraunhofer Institute for Algorithms and Scientific Computing (SCAI), Schloss Birlinghoven 1, 53757 Sankt Augustin, Germany}
+\address[c]{Fraunhofer Center for Machine Learning, Schloss Birlinghoven 1, 53757 Sankt Augustin, Germany}
 \address[d]{Institute for Numerical Simulation, Universität Bonn, Endenicher Allee 19b, 53115 Bonn, Germany}
@@
 
-\aucores{* Corresponding author. Tel.: +49-271-740-4509; fax: +49-271-740-2630. {\it E-mail address:} alejandro.perez@uni-siegen.de}
+\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-2630. {\it E-mail address:} fabian.steinberg@uni-siegen.de}
 
@@
 Over the years, diverse methods to ensure the quality of products have been developed \cite{mitra2016fundamentals}.
-Among the most used methods, we have Auditing, Total Quality Control (TCQ) \cite{illes2017new}, Poka-Yoke Techniques \cite{Robinson2011UsingPT}, the 100\% control of each produced product \cite{Hinckley1997QC}, and statistical methods like the Statistical Process Control (SPC) \cite{selvamuthu2018introduction}.
+Among the most used methods, we have Auditing, Total Quality Control (TCQ) \cite{illes2017new}, Poka-Yoke Techniques \cite{robinson1997using}, the 100\% control of each produced product \cite{Hinckley1997QC}, and statistical methods like the Statistical Process Control (SPC) \cite{selvamuthu2018introduction}.
 Independently of the method used, the goal is the same, to avoid the production of faulty products, or to identify and remove them, before delivering those to the customer.\cite{mitra2016fundamentals}.
@@
 
-Considering the high amount of data available in nowadays industries, one approach to reduce the inspection costs and simultaneously  increase the accuracy of detecting faulty products would be to implement an ML model capable to predict the product quality based on the initial state of the machine.
+Considering the high amount of data available in industries, one approach to reduce the inspection costs and simultaneously  increase the accuracy of detecting faulty products would be to implement an ML model capable to predict the product quality based on the initial state of the machine.
 This will not only help to detect faulty products before the QC process is performed, it would also strengthen the current QC methods by combining them with QC predictive models.
@@
 (model accuracy vs applicability at industrial environments); what steps should be followed to prepare the data for predictive QC methods?; and what findings and lessons are worth to consider for further applications in the area?.
-For this, we cover the methods used in quality check in production, as well as the bases of predictive analytics in production (Section~\ref{sec:related_works}). 
+For this, we cover the methods used for quality checks in production, as well as the bases of predictive analytics in production (Section~\ref{sec:related_works}). 
 We describe a suitable industrial platform to implement the ML models (Section~\ref{sec:democell}).
@@
 According to Delen and Damirkan, predictive analytics (PA) consists of unraveling the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
-PA offers a wide range of applications, and it can be implemented, as long as the sufficiently data are available \cite{bishop2006pattern}.
+PA offers a wide range of applications, and it can be implemented, as long as sufficient data are available \cite{bishop2006pattern}.
 According to Krauß, there is a wide range of applications for PA in the industrial and production environment. 
-Some common industrial applications of PA are focussed products (design and optimization), machines and assets (predictive maintenance, anomaly detection, self learning-machines) and process (scheduling, process design, predictive process control) \cite{krauss2019machine}.
+Some common industrial applications of PA are focussed in products (design and optimization), machines and assets (predictive maintenance, anomaly detection, self learning-machines) and process (scheduling, process design, predictive process control) \cite{krauss2019machine}.
 
@@
 This could be due to computer power limitations in earlier research and the recent increase of ML applications in this area.
-Related works are mostly allocated into two groups, defect analysis of produced pieces and process-oriented QC.
+Related works mostly belongs to two groups, defect analysis of produced pieces and process-oriented QC.
 Due to the recent advances in ML approaches specialized in image and pattern recognition \cite{bishop2006pattern}, a great number of publications focus on product-analysis based on images from cameras during the production process,
-e.g., Escobar employs pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focussed on defect prediction within printed layers by employing supervised models based on features extracted directly from the machine code and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
-Other authors focus their research in process-oriented QC, e.g., 
+e.g., Escobar employed pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focussed on defect prediction within printed layers by employing supervised models based on features extracted directly from the machine code and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
+Other authors focussed their research on process-oriented QC, e.g., 
 Krauß focussed on describing the ML pipeline to implement automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}; Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}; Ritter studied the ways of process modeling on quality prediction and assurance of chipboards \cite{ritter1992neue}.
@@
 
-\section{The case industry 4.0 demonstration cell}  \label{sec:democell}% (taken from title) % 3/4 Page
+\section{The case: industry 4.0 demonstration cell}  \label{sec:democell}% (taken from title) % 3/4 Page
 
@@
 The executed abstracted assembly process consists of stacking two disks of different sizes on top of each other.
-The corresponding pseudo product quality is later determined by the laser scanner by evaluating the concentricity of both disks.
+The corresponding pseudo product quality is later determined using the laser scanner and evaluating the concentricity of both disks.
 If the disks' concentricity is within a tolerance of 1.5mm, the piece is classified as OK, if not, it is classified as NOK.
@@
 The continuous data collection and the clear correlation between the machine parameters and the quality of the product, is the ideal play-ground to implement a sandbox for machine learning implementations.
-With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner.
+With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), before the actual quality check done by the laser scanner.
 
@@
 
-To study which implementation would be more suitable for industrial applications, we compare Multilayer Perceptrons (MLPs), Support Vector Machines (SVM), as well as decision trees on the task of quality prediction.
+To study which implementation would be more suitable for industrial applications, we compare Multilayer Perceptrons (MLPs), Support Vector Machines (SVM), as well as Decision Trees on the task of quality prediction.
 All three will be introduced next.
@@
 which adds non-linearity to the network graph. Rectified linear units
-(ReLUs) are zero for negative inputs leave positive inputs unchanged.
+(ReLUs) are zero for negative inputs and leave positive inputs unchanged.
 ReLUs are the recommended activation function for modern neural
-networks \cite{goodfellow2016deep} we use these here as well.
+networks \cite{goodfellow2016deep}, we use these here as well.
 Since the linear parts of the ReLU and the linear matrix multiplication
@@
 \subsection{Decision Tree}
-Decision trees are essentially binary trees, which work with the input
+Decision Trees are essentially binary trees, which work with the input
 features at the roots, decisions are made by moving
@@
 Common choices are cross-entropy of Gini-coefficient \cite{aggarwal2015data}.
-During construction splits minimizing the chosen function are chosen.
+During construction splits minimizing the chosen function are selected.
 
@@
 
-Before collecting the data, we need to find the variables of interest and mapping their source, as well as to determine the use cases of interest.
+Before collecting the data, we needed to find the variables of interest and map their source, as well as to determine the use cases of interest.
 Our study focussed on the data described in Table~\ref{tab:data_source} and the six use cases described in Table~\ref{tab:use_cases}.
@@
 
-Once the data is clean and compiled in one directory, the next step was to split the data based on the assembly cycle.
-For our purpose, we split the dataset into individual data-samples with help of the action tags included in the dataset Table~\ref{tab:data_source}.
-Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so.
-At this point, we have a series of data-samples based on time series.
+Once the data was clean and compiled in one directory, the next step was to split the data based on the assembly cycle.
+For our purpose, we split the dataset into individual data-samples with help of the \textit{action tag}included in the dataset Table~\ref{tab:data_source}.
+Subsequently, each data-sample was automatically checked for missing sensor values and discarded if so.
+% At this point, we have a series of data-samples based on time series.
 However, we are not interested in a time series analysis, since having the time parameter would not necessarily improve the prediction results, but rather make the approach more complex, and more data would be needed, therefore it was needed to compress each time-series based data-sample into atemporal data-samples.
 
-Each time-series sample collected is the result of data collected during one machine assembly cycle (MAC).
-The starting point of one MAC is the very first moment the robotic arm grabs the white disk from the store area and the ending point is before grabbing the next white disk in the same area.
-To eliminate time as a variable in our dataset, it was needed to acquire the data at specific moments of the MAC.
+Each time-series sample was the result of data collected during one machine assembly cycle (MAC).
+The starting point of one MAC was defined as the very first moment the robotic arm grabs the white disk from the store area and the ending point was defined as the starting of the subsequent MAC, the grabbing of the next white disk in the same area.
+To eliminate time as a variable in our dataset, it was needed to transform time-series into feature data suitable describing a MAC in a way that different MACs are easily comparable.
 For that reason, we defined a set of sampling-conditions that helped us to collect the relevant data during the MAC:
 \begin{itemize}
-       \item Value of the robot position ($xyz$) while dropping both disks in the storage area
+       \item Value of the robot position ($xyz$) while dropping both disks in the conveyor - Gate
        \item Mean conveyor speed value per conveyor band
@@
 The robot's position at disk drop is marked in 
-Figure~\ref{fig:robot_pos_cell}. The quality prediction problem is 
-framed as a classification task. The input vectors which we feed into our
+Figure~\ref{fig:robot_pos_cell}. The quality prediction problem was 
+framed as a classification task. The input vectors which we fed into our
 classifiers consist of the arm positions at the disk drops for both
 disks in three dimensions, as well as the largest recorded belt speed
-of all three belts. The interpretation of the quality measurement is 
-used as the training target. It can be OK or NOK which we encode as 
+of all three belts. The interpretation of the quality measurement was 
+used as the training target. It can be OK or NOK which we encoded as 
 zero and one.
 
-We work with a total of 528 measurements. Each containing arm and belt data
-logs of individual cell run. 50 samples are set aside at random for testing 
-purposes, leaving 478 training samples. The random number generator seed is
+We worked with a total of 528 measurements. Each containing arm and belt data
+logs of individual cell run. 50 samples were set aside at random for testing 
+purposes, leaving 478 training samples. The random number generator seed was
 set to one to ensure the train and test set splits are identical 
@@
 
-We compare a total of three different classifier architectures on the data.
+We compared a total of three different classifier architectures on the data.
 A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
-structure.
-In this case, we chose to train all three models using standard hyperparameters, which we found to work well.
-\footnote{To allow exact reproduction of our results source code is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
+structure. In this case, we chose to train all three models using exemplary 
+default hyperparameters, which we found to work.
+\footnote{To allow exact reproduction of our results source code
+ is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
 
@@
 Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples
-quality measurements indicate a problem. This sets the 
+quality measurements indicated a problem. This set the 
 baseline over the entire data set, which would be obtained by simply labeling all samples
-as faulty. Over the test set, we require to classify more than 64\% of the data correctly.
-We would therefore expect any naive classifier to produce at least 64\% accuracy, which we have to surpass.
-In Table~\ref{tab:class_comp}, we observe that this is indeed the case for all three approaches evaluated here.
+as faulty. For the test set, we required to classify more than 64\% of the data correctly.
+Therefore, we expected any naive classifier to produce at least 64\% accuracy, which we had to surpass.
+In Table~\ref{tab:class_comp}, we observe that this was indeed the case for all three approaches evaluated here.
 
-Based on the MLP prediction results presented on Table~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} show that even though the prediction model is not 100\% accurate, the percentage of false-positive predictions is 0\%.
-The false-negative results represent the 12\% of the test sample and the true predictions constitute 88\% of the test data.
+The MLP prediction results presented on Table~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} show that even though the prediction model was not 100\% accurate, the percentage of false-positive predictions was 0\%.
+The false-negative results represented 12\% of the test sample and the true predictions constituted 88\% of the test data.
 
-The outcome of the models shows that the decision tree performed best followed by the multilayer perceptron and the support vector machine.
-However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, multilayer perceptron would be the preferred solution to be implemented in industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
+The outcome of the models showed that the Decision Tree performed best followed by the Multilayer Perceptron and the Support Vector Machine.
+However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, Multilayer Perceptron would be the preferred solution to be implemented in industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
 
@@
 On the other hand, we have the statistical methods, which are known to be fast and efficient, but the lack of reviewing each product until the next batch review might imply a considerable loss of the produced products whenever NOK products are found.
-This is based on the uncertainty of when did the error occur and how many products are affected.
+This is based on the uncertainty of when the error occurred and how many products are affected.
 
-By implementing ML models capable to predict the quality of the product, based on just the initial conditions of the process would be a great asset for the industrial processes.
-Within the limits of our work, we predict with 98\% certainty the product quality by implementing a decision tree model with a 6-variables vector as input.
-However, our decision for industrial applications would be the MLP with 88\% accuracy, to guarantee that all passed parts are OK and avoid labeling a NOK piece as OK.
+By implementing ML models based on just the initial conditions of the process and capable to predict the quality of the product, would be a great asset for the industrial processes.
+Within the limits of our work, we predicted with 98\% certainty the product quality by implementing a Decision Tree model with a 6-variables vector as input.
+However, our decision for industrial applications would be the MLP with 88\% accuracy, to guarantee that all passed parts are OK and avoid labeling NOK pieces as OK.
 For further work, we expect to increase the accuracy of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.
@@
 Difficulties at implementing ML models in production are also described by others authors \cite{paleyes2020challenges}.
-
-\vspace{0.2cm}
-
+\vspace{0.1cm}
 \textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture.
@@
 
-\textbf{Data synchronization}; two OPC-UA servers were used on this implementation. This lead to a series of data synchronization problems due to differences in the internal clock of both servers.
+\textbf{Data synchronization}; two OPC-UA servers were used on this implementation. This led to a series of data synchronization problems due to differences in the internal clock of both servers.
 To solve the issue, it was needed to write a time-stamp synchronization script that was deployed during the data preprocessing phase.
@@
 
+\section{Author Contributions}
+
+Pérez M. and Moritz performed writing - original draft, conceptualization, review, and editing; Investigation; Software and Data Curation.
+Schmallenbach performed writing - Review \& editing.
+Wagner, Heinbach, Steinberg, Steffes-lai, Garcke performed writing - Review.
+Burggräf performed supervision of work.
+
 \section*{Acknowledgments}

### 2020-12-14 02_Paper/paper.tex
Final revision. Added Author contribution
add well.
Correction 14.12.2020

@@
 
-\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-2630. {\it E-mail address:} fabian.steinberg@uni-siegen.de}
+\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} fabian.steinberg@uni-siegen.de}
 
@@
 Common choices are cross-entropy of Gini-coefficient \cite{aggarwal2015data}.
-During construction splits minimizing the chosen function are selected.
+During the construction splits minimizing, the selected functions are chosen.
 
@@
 
-Once the data was clean and compiled in one directory, the next step was to split the data based on the assembly cycle.
-For our purpose, we split the dataset into individual data-samples with help of the \textit{action tag}included in the dataset Table~\ref{tab:data_source}.
+Once the data was cleaned and compiled in one directory, the next step was to split the data based on the assembly cycle.
+For our purpose, we split the dataset into individual data-samples with help of the \textit{action flags}included in the dataset Table~\ref{tab:data_source}.
 Subsequently, each data-sample was automatically checked for missing sensor values and discarded if so.
@@
 \begin{itemize}
-       \item Value of the robot position ($xyz$) while dropping both disks in the conveyor - Gate
+       \item Value of the robot position ($xyz$) while dropping both disks in the \textit{conveyor - gate}
        \item Mean conveyor speed value per conveyor band
@@
 
-We compared a total of three different classifier architectures on the data.
-A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
+We compared a total of three different classifier architectures on the data,
+a Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
 structure. In this case, we chose to train all three models using exemplary 
@@
 
-By implementing ML models based on just the initial conditions of the process and capable to predict the quality of the product, would be a great asset for the industrial processes.
+Implementing ML models based on just the initial conditions of the process and capable to predict the quality of the product, would be a great asset for the industrial processes.
 Within the limits of our work, we predicted with 98\% certainty the product quality by implementing a Decision Tree model with a 6-variables vector as input.
@@
 \vspace{0.1cm}
+
 \textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture.
@@
 
-\textbf{Dataset size}; as the starting point we collected as many data points as the ones found in the iris Dataset \cite{fisher_1936}.
+\textbf{Dataset size}; as the starting point we collected as many data points like the ones found in the iris Dataset \cite{fisher_1936}.
 The next step was to collect batches of data of around 30 minutes per use case.
@@
 
-Pérez M. and Moritz performed writing - original draft, conceptualization, review, and editing; Investigation; Software and Data Curation.
-Schmallenbach performed writing - Review \& editing.
-Wagner, Heinbach, Steinberg, Steffes-lai, Garcke performed writing - Review.
+Pérez M. and Wolter performed writing - original draft, conceptualization, review, and editing; investigation; software and data curation.
+Schmallenbach performed writing - review \& editing.
+Wagner, Heinbach, Steinberg, Garcke, and Steffes-lai performed writing - review.
 Burggräf performed supervision of work.

### 2020-12-15 02_Paper/paper.tex
Author Contributions

@@
 structure. In this case, we chose to train all three models using exemplary 
-default hyperparameters, which we found to work.
+default hyperparameters, which we found to work well.
 \footnote{To allow exact reproduction of our results source code
@@
 Schmallenbach performed writing - review \& editing.
-Wagner, Heinbach, Steinberg, Garcke, and Steffes-lai performed writing - review.
-Burggräf performed supervision of work.
+Burggräf, Wagner, Heinbach, Steinberg performed writing - conceptualization, review.
+Garcke, and Steffes-lai performed writing - review.
+% Burggräf performed supervision of work.
 

### 2021-03-30 02_Paper/paper.tex
corresponding author
fix link.

@@
 \author[a]{Benjamin Heinbach}
-\author[a]{Fabian Steinberg*} 
-\author[a]{Alejandro R. Pérez M.}
+\author[a]{Fabian Steinberg} 
+\author[a]{Alejandro R. Pérez M.*}
 \author[a]{Lennart Schmallenbach}
@@
 
-\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} fabian.steinberg@uni-siegen.de}
+\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} alejandro.perez@uni-siegen.de}
 
@@
 \footnote{To allow exact reproduction of our results source code
- is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}
+ is available at \url{https://github.com/USi-IPEM/Demo-Cell-Classification}}
 

### 2021-06-14 02_Paper/paper.tex
figure 3
update related work.

@@
 Among the most used methods, we have Auditing, Total Quality Control (TCQ) \cite{illes2017new}, Poka-Yoke Techniques \cite{robinson1997using}, the 100\% control of each produced product \cite{Hinckley1997QC}, and statistical methods like the Statistical Process Control (SPC) \cite{selvamuthu2018introduction}.
-Independently of the method used, the goal is the same, to avoid the production of faulty products, or to identify and remove them, before delivering those to the customer.\cite{mitra2016fundamentals}.
+Independently of the method used, the goal is the same, to avoid the production of faulty products or to identify and remove them before delivering those to the customer.\cite{mitra2016fundamentals}.
 However, the relationship between cost and efficiency varies from one method to another.
-This is noticeable, e.g., at the cost of highly specialized equipment for automated inspection, or the cost of employees performing a manual inspection of the produced products versus the accuracy of detecting all faulty products \cite{Diego1998QCCost}.
+This is noticeable, e.g., at the cost of highly specialized equipment for automated inspection, or the cost of employees performing a manual review of the produced products versus the accuracy of detecting all faulty products \cite{Diego1998QCCost}.
 
@@
 The advantage of quantitative measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable controlled adjustment of the process parameters, as well as the possibility of observing trends in the collected data.
-This  enables the employment of predictive models to determine the quality of the product before the QC process takes place \cite{bishop2006pattern, krauss2019machine}.
+This allows the employment of predictive models to determine the quality of the product before the QC process takes place \cite{bishop2006pattern, krauss2019machine}.
 
-With the evolution of machine learning (ML) applications \cite{bishop2006pattern, Burggraef2018AIinprod}, approaches combining QC and predictive models are becoming more relevant.
+With the evolution of machine learning (ML) applications \cite{bishop2006pattern}, approaches combining QC and predictive models are becoming more relevant.
 The applications range from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process-oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}, see Section~\ref{sec:related_works}.
@@
 While implementing ML models to QC, several challenges arise that have not yet been sufficiently addressed, e.g., what to consider while evaluating the output from ML models for industrial applications?
-(model accuracy vs applicability at industrial environments); what steps should be followed to prepare the data for predictive QC methods?; and what findings and lessons are worth to consider for further applications in the area?.
+(model accuracy vs.
+applicability at industrial environments); what steps should be followed to prepare the data for predictive QC methods?; and what findings and lessons are worth considering for further applications in the area?.
 For this, we cover the methods used for quality checks in production, as well as the bases of predictive analytics in production (Section~\ref{sec:related_works}). 
 We describe a suitable industrial platform to implement the ML models (Section~\ref{sec:democell}).
-Then, we explain the three machine learning methods implemented in this work: Multilayer perceptrons, Support Vector Machines, and Decision Tree (Section~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section~\ref{sec:experiment}).
+Then, we explain the three machine learning methods implemented in this work: Multilayer perceptrons, Support Vector Machines, and a Decision Tree (Section~\ref{sec:ML}), followed by the description of the experiment process from the data acquisition and preprocessing, to the classifier optimization and testing (Section~\ref{sec:experiment}).
 Finally, we present the findings achieved after the finalization of this project phase (Section~\ref{sec:conclusion}), as well as present a list of lessons learned for the implementation of the project, which might be helpful for further implementations (Section~\ref{sec:lessons}).
 
-\section{Related Works} \label{sec:related_works}% 1 Page
-
-According to Delen and Damirkan, predictive analytics (PA) consists of unraveling the inherent relationships (if any) between input and output by using data and mathematical techniques \cite{delen2013data}.
-PA offers a wide range of applications, and it can be implemented, as long as sufficient data are available \cite{bishop2006pattern}.
+\section{Related Work} \label{sec:related_works}% 1 Page
+The digital transformation of the manufacturing industry \cite{mourtzis2018towards,caggiano2018cloud,mourtzis2019modelling} allows the application of machine learning-powered predictive analytics techniques.
+According to Delen and Damirkan, predictive analytics (PA) consists of unraveling the inherent relationships (if any) between input and output by using data, and mathematical techniques \cite{delen2013data}.
+PA offers a wide range of applications and is usable as long as sufficient data are available \cite{bishop2006pattern}.
 According to Krauß, there is a wide range of applications for PA in the industrial and production environment. 
-Some common industrial applications of PA are focussed in products (design and optimization), machines and assets (predictive maintenance, anomaly detection, self learning-machines) and process (scheduling, process design, predictive process control) \cite{krauss2019machine}.
+Some industrial applications of PA focues machines and assets (predictive maintenance, anomaly detection, self learning-machines) \cite{colledani2020production}, and process (scheduling, process design, predictive process control) \cite{krauss2019machine}.
 
@@
 This could be due to computer power limitations in earlier research and the recent increase of ML applications in this area.
-Related works mostly belongs to two groups, defect analysis of produced pieces and process-oriented QC.
-Due to the recent advances in ML approaches specialized in image and pattern recognition \cite{bishop2006pattern}, a great number of publications focus on product-analysis based on images from cameras during the production process,
-e.g., Escobar employed pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focussed on defect prediction within printed layers by employing supervised models based on features extracted directly from the machine code and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
+The related work mostly belongs to two groups, defect analysis of produced pieces and process-oriented QC.
+Due to the recent advances in ML approaches specialized in image and pattern recognition \cite{bishop2006pattern} and the advent of standardized data collection~\cite{mourtzis2018towards}, a great number of publications focus on product-analysis based on images from cameras during the production process,
+e.g., Escobar employed pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focussed on defect prediction within printed layers by employing supervised models based on features extracted directly from the machine code, and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
 Other authors focussed their research on process-oriented QC, e.g., 
-Krauß focussed on describing the ML pipeline to implement automated machine learning for predictive quality in production \cite{krauss2020automated} and product quality prediction in a process chain \cite{krauss2019machine}; Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}; Ritter studied the ways of process modeling on quality prediction and assurance of chipboards \cite{ritter1992neue}.
+Krauß focussed on describing the ML pipeline to implement automated machine learning for predictive quality in production \cite{krauss2020automated}, and product quality prediction in a process chain \cite{krauss2019machine}; Aumi focussed on the model development for predictive quality control of batch processes \cite{aumi2012model}; Ritter studied the ways of process modeling on quality prediction, and assurance of chipboards \cite{ritter1992neue}.
 
 Applications that combine PA with QC might improve the current QC processes.
-However, based on the previous findings, there are no clear references to the impact of implementing ML models based just on model accuracy, together with industrial factors of the QC process.
-By employing machine learning (ML) techniques (Section~\ref{sec:ML}), together with the QC traditional methods, it would be possible to improve the relationship between inspection costs and the probability of detecting faulty products during the QC process, as well as, decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
+However, based on the previous findings, there are no unambiguous references to the impact of implementing ML models based just on model accuracy, together with industrial factors of the QC process.
+By employing machine learning (ML) techniques (Section~\ref{sec:ML}), together with the QC traditional methods, it would be possible to improve the relationship between inspection costs and the probability of detecting faulty products during the QC process, as well as decrease the risk of labeling NOK pieces as OK and deliver them to costumers.
 However, before implementing these techniques, it is important to define the platform where these predictive analytics models will be implemented in a controlled and transparent industrial environment.
@@
 \includestandalone[width=.45\textwidth]{img/arm_data_plot}
-       \caption{Robot arm movement patterns. We show the movement of the 
-                cell's robot arm, its grippers, and the encoding of the overall
-                position in the system. The changes in the grip flag are triggered,
-                when the gripper opens or closes. 0 indicates an open, while
-                one indicates a closed gripper. The position flags mark the state
-                of the cell's arm. 0 means the black disk is in store,
-                one that the black disk is at the gate, two that the white disk
-                is in store and three that the white disk is located at the gate.
-             }
+\caption{Three dimensional robot arm movement patterns.}
 \label{fig:robot_pos_cell}
@@
 The robot's position at disk drop is marked in 
-Figure~\ref{fig:robot_pos_cell}. The quality prediction problem was 
+Figure~\ref{fig:robot_pos_cell}. We show the movement of the cell's robot arm, its grippers, and the encoding of the overall position in the system.
+The changes in the grip flag are triggered, when the gripper opens or closes.
+0 indicates an open, while one indicates a closed gripper.
+The position flags mark the state of the cell's arm.
+0 means the black disk is in store, one that the black disk is at the gate, two that the white disk is in store and three that the white disk is located at the gate.
+The quality prediction problem was
 framed as a classification task. The input vectors which we fed into our
@@
 Schmallenbach performed writing - review \& editing.
-Burggräf, Wagner, Heinbach, Steinberg performed writing - conceptualization, review.
-Garcke, and Steffes-lai performed writing - review.
+Burggräf, Wagner, Heinbach, Steinberg performed writing - conceptualization, review. Garcke, and Steffes-lai performed writing - review.
 % Burggräf performed supervision of work.
@@
 
-\bibliographystyle{elsarticle-harv} %elsarticle-harv} %abbrv %IEEEtran
+%\bibliographystyle{elsarticle-harv} %elsarticle-harv} %abbrv %IEEEtran
+\bibliographystyle{unsrt}
 \bibliography{bib}

### 2021-06-14 02_Paper/paper.tex
add flow-chart.

@@
 The related work mostly belongs to two groups, defect analysis of produced pieces and process-oriented QC.
-Due to the recent advances in ML approaches specialized in image and pattern recognition \cite{bishop2006pattern} and the advent of standardized data collection~\cite{mourtzis2018towards}, a great number of publications focus on product-analysis based on images from cameras during the production process,
+Due to the recent advances in ML approaches specialized in image and pattern recognition \cite{bishop2006pattern} and the advent of standardized data collection~\cite{mourtzis2018towards}, a great number of publications focus on product analysis based on images from cameras during the production process,
 e.g., Escobar employed pattern recognition for defect detection in a binary classification problem based on a $l_1$-regularized logistic regression \cite{Carlos2018MLforQC}; Sohnius focussed on defect prediction within printed layers by employing supervised models based on features extracted directly from the machine code, and the scan of the layers surface \cite{Sohnius2019PASurfacequality}.
@@
 
+\begin{figure}
+\centering
+\includestandalone[width=.4\linewidth]{./img/flow_chart}
+\caption{Idealized flow-chart of our simulated manufacturing process loop. All process elements can be disturbed at any time.}
+\label{fig:ideal_cell}
+\end{figure}
+
 Our case study is an abstraction of an assembly process of the industry.
 This case study is a highly flexible and transparent platform regarding software and hardware access and manipulation.
-The industry 4.0 demonstration cell is composed of three independent conveyor belts, a robotic assembly arm (UR3), a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200, see Figure~\ref{fig:ind_cell}.
+The industry 4.0 demonstration cell is composed of three independent conveyor belts, a robotic assembly arm (UR3), a laser scanner used for quality control as well as a wide range of sensors, all orchestrated by a SIEMENS PLC S7-1200.
+We show an idealized process flow-chart in Figure~\ref{fig:ideal_cell} and an illustration of the cell components in Figure~\ref{fig:ind_cell}.
 The executed abstracted assembly process consists of stacking two disks of different sizes on top of each other.

### 2021-06-14 02_Paper/paper.tex
update caption table 3.

@@
        \end{tabular}
-       \caption{Comparison of Support Vector Machine (SVM), Multilayer Perceptron and 
-                Decision Tree classification on our anomaly detection task. 
-                The first row shows the performance of naively predicting a broken piece
-                every time.}
+       \caption{Comparison of Support Vector Machine (SVM), Multilayer Perceptron and Decision Tree classification on our anomaly detection task. }
        \label{tab:class_comp}
@@
 
-Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples
-quality measurements indicated a problem. This set the 
-baseline over the entire data set, which would be obtained by simply labeling all samples
-as faulty. For the test set, we required to classify more than 64\% of the data correctly.
+Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples quality measurements indicated a problem. 
+The first row shows the performance of naively predicting a broken piece every time.
+This accuracy sets the baseline over the entire data set, which would be obtained by simply labeling all samples as faulty.
 Therefore, we expected any naive classifier to produce at least 64\% accuracy, which we had to surpass.

### 2021-06-14 02_Paper/paper.tex
draft now meets page limit requirements.

@@
 
-Considering the high amount of data available in industries, one approach to reduce the inspection costs and simultaneously increase the accuracy of detecting faulty products would be to implement an ML model capable to predict the product quality based on the initial state of the machine.
+% Considering the high amount of data available in industries, one approach to reduce the inspection costs and simultaneously increase the accuracy of detecting faulty products would be to implement an ML model capable to predict the product quality based on the initial state of the machine.
 This will not only help to detect faulty products before the QC process is performed, it would also strengthen the current QC methods by combining them with QC predictive models.
 
-While implementing ML models to QC, several challenges arise that have not yet been sufficiently addressed, e.g., what to consider while evaluating the output from ML models for industrial applications?
+Regarding the use of ML models in QC, several challenges arise that have not yet been sufficiently addressed, e.g., what to consider while evaluating the output from ML models for industrial applications?
 (model accuracy vs.
@@
 Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticeable shifting on pieces' position as well as the stop of the process.
-
 The continuous data collection and the clear correlation between the machine parameters and the quality of the product, is the ideal play-ground to implement a sandbox for machine learning implementations.
@@
 \begin{figure}
-       \includegraphics[width=.45\textwidth]{img/demozelle}
+       \centering
+       \includegraphics[width=.38\textwidth]{img/demozelle}
        \caption{The industry 4.0 demonstration cell at the University of Siegen}
@@
 This represents the interaction between multiple servers in real production environments.
-
 Before collecting the data, we needed to find the variables of interest and map their source, as well as to determine the use cases of interest.
@@
 Approximately 15 hours of data were collected in different sessions, while equally sampling each use case during the data acquisition stage.
-
 \begin{table}
@@
 \end{table}
-
+%
 \begin{table}
@@
 \end{table}
-
+%
 \begin{figure}
@@
 \end{figure}
-
+%
 \subsection{Data preprocessing}
-
 Once the data was collected, the next step was to clean the raw data and organize it accordingly \cite{bishop2006pattern}.
@@
 Once the delta-time was determined, a time-stamp function was implemented to correct the time-shift between samples and be able to merge all the data without incompatibilities.
-
 Data tags interpretation is an important step in the preprocessing process \cite{bishop2006pattern}.
@@
 This last step, might be optional in other implementations, however, it proves to be a great addition for testing purposes.
-
 Once the data was cleaned and compiled in one directory, the next step was to split the data based on the assembly cycle.
@@
 However, we are not interested in a time series analysis, since having the time parameter would not necessarily improve the prediction results, but rather make the approach more complex, and more data would be needed, therefore it was needed to compress each time-series based data-sample into atemporal data-samples.
-
 Each time-series sample was the result of data collected during one machine assembly cycle (MAC).
@@
 \end{itemize}
-
 Each time-series sample was evaluated based this sampling-condition, and the result of each evaluation was considered as our atemporal data-sample, which we used as the base for our classifier.
@@
 \begin{figure}
-\includestandalone[width=.45\textwidth]{img/arm_data_plot}
+\includestandalone[width=.425\textwidth]{img/arm_data_plot}
 \caption{Three dimensional robot arm movement patterns.}
@@
 zero and one.
-
 We worked with a total of 528 measurements. Each containing arm and belt data
@@
 for all experiments.
-
 We compared a total of three different classifier architectures on the data,
@@
  is available at \url{https://github.com/USi-IPEM/Demo-Cell-Classification}}
-
+%
 \begin{table}
@@
 \end{table}
-
+%
 Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples quality measurements indicated a problem. 
@@
 In Table~\ref{tab:class_comp}, we observe that this was indeed the case for all three approaches evaluated here.
-
 The MLP prediction results presented on Table~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} show that even though the prediction model was not 100\% accurate, the percentage of false-positive predictions was 0\%.
 The false-negative results represented 12\% of the test sample and the true predictions constituted 88\% of the test data.
-
 The outcome of the models showed that the Decision Tree performed best followed by the Multilayer Perceptron and the Support Vector Machine.
@@
 This is based on the uncertainty of when the error occurred and how many products are affected.
-
 Implementing ML models based on just the initial conditions of the process and capable to predict the quality of the product, would be a great asset for the industrial processes.
@@
 For further work, we expect to increase the accuracy of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.
-
 It is important to state that this prediction model is not yet ready to fully replace the statistical methods, nor the hundred percent quality check method, since this research is still in its early stages and needs further development.
@@
 \section{Lesson Learned} \label{sec:lessons} % 1/2 Page
-
 It is worth to mention the most important points learned during the project implementation.
@@
 Difficulties at implementing ML models in production are also described by others authors \cite{paleyes2020challenges}.
-\vspace{0.1cm}
-
+\\
+%
 \textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture.
-To overcome the situation stated above, it was necessary to reprogram big sections of the machine control system.
-
+To overcome the situation stated above, it was necessary to reprogram big sections of the machine control system. \\
+%
 \textbf{Data synchronization}; two OPC-UA servers were used on this implementation. This led to a series of data synchronization problems due to differences in the internal clock of both servers.
@@
 Without harmonious time-stamps, determining the production cycle would have been impossible and the input data for the ML model would have been useless, and the model inaccurate.
-
+\\
+%
 \textbf{Data interpretation}; this process is considered complicated, time-consuming, and a fundamental step for any ML applications.
 It is fundamental to understand the assembly process, the timing from the machine movements, the boundaries of the machine's sensors, as well a basic correlation within the presented data.
-
+\\
+%
 \textbf{Missing values}; to minimize the risk of false results delivered by the ML model, it would be compulsory to carefully review the ML input data.
@@
 Whenever there was missing data, and as long as we did not fabricate data, we employed statistical methods to fill the data gap.
-
+\\
+%
 \textbf{Adapting the industry 4.0 demonstration cell}; the initial state of the demonstrator was very limited.
@@
 To overcome this uncertainty, we modified the machine program to raise specific flags whenever certain actions were executed.
-
+\\
+%
 \textbf{Machine Learning}; careful measurement and  meaningful preprocessing
 of our cell-data was key to the successful application of all three algorithms.
-Without the labels, the problem could not have been framed as a supervised 
-classification problem.
-
+Without the labels, the problem could not have been framed as a supervised classification problem. \\
+%
 \textbf{Dataset size}; as the starting point we collected as many data points like the ones found in the iris Dataset \cite{fisher_1936}.
@@
 
-\section{Author Contributions}
-
-Pérez M. and Wolter performed writing - original draft, conceptualization, review, and editing; investigation; software and data curation.
-Schmallenbach performed writing - review \& editing.
-Burggräf, Wagner, Heinbach, Steinberg performed writing - conceptualization, review. Garcke, and Steffes-lai performed writing - review.
+\vspace{0.1cm}
+\footnotesize
+\textbf{Author Contributions}
+Pérez M. and Wolter writing - original draft, conceptualization, review, and editing; investigation; software and data curation.
+Schmallenbach writing - review, editing.
+Burggräf, Wagner, Heinbach, Steinberg writing - conceptualization, review. Garcke, and Steffes-lai writing - review.
 % Burggräf performed supervision of work.
 
-\section*{Acknowledgments}
+\footnotesize
+\textbf{Acknowledgments}
 This work was funded by the European Regional Development Fund (ERDF) within the project "ManuBrain".

### 2021-06-15 02_Paper/paper.tex
Minor edits on corresponding author and table captions

@@
 
-\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} alejandro.perez@uni-siegen.de}
+\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} fabian.steinberg@uni-siegen.de}
 
@@
 With the evolution of machine learning (ML) applications \cite{bishop2006pattern}, approaches combining QC and predictive models are becoming more relevant.
-The applications range from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process-oriented QC \cite{krauss2020automated, krauss2019machine, aumi2012model, ritter1992neue}, see Section~\ref{sec:related_works}.
+The applications range from the defect analysis of the produced piece \cite{Carlos2018MLforQC, Sohnius2019PASurfacequality}, to process-oriented QC \cite{krauss2019machine, krauss2020automated,  aumi2012model, ritter1992neue}, see Section~\ref{sec:related_works}.
 Independently of the research area previously stated, within the scope of the related works, there is no evidence of an evaluation framework for diverse ML techniques applied in QC process.
@@
 structure. In this case, we chose to train all three models using exemplary 
-default hyperparameters, which we found to work well.
-\footnote{To allow exact reproduction of our results source code
+default hyperparameters, which we found to work well. \footnote{To allow exact reproduction of our results source code
  is available at \url{https://github.com/USi-IPEM/Demo-Cell-Classification}}
+Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples quality measurements indicated a problem. 
+The first row shows the performance of naively predicting a broken piece every time.
+This accuracy sets the baseline over the entire data set, which would be obtained by simply labeling all samples as faulty.
+Therefore, we expected any naive classifier to produce at least 64\% accuracy, which we had to surpass.
+In Table~\ref{tab:class_comp}, we observe that this was indeed the case for all three approaches evaluated here.
+The MLP prediction results presented on Table~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} show that even though the prediction model was not 100\% accurate, the percentage of false-positive predictions was 0\%.
+The false-negative results represented 12\% of the test sample and the true predictions constituted 88\% of the test data.
+The outcome of the models showed that the Decision Tree performed best followed by the Multilayer Perceptron and the Support Vector Machine.
+However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, Multilayer Perceptron would be the preferred solution to be implemented in industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
 %
@@
        \end{subtable}
-       \caption{Confusion matrices result of the prediction of 50 test data-points.
-We present the result of the predictions given by all three algorithms in detail based on the comparison between true values vs predictions.
-The tables read from the upper-left cell as: true-positive, false-positive, false-negative, true-negative.}
+       \caption{Confusion matrices result of the prediction of 50 test data-points. }
        \label{tab:Confusion_matrix}
@@
 %
-Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples quality measurements indicated a problem. 
-The first row shows the performance of naively predicting a broken piece every time.
-This accuracy sets the baseline over the entire data set, which would be obtained by simply labeling all samples as faulty.
-Therefore, we expected any naive classifier to produce at least 64\% accuracy, which we had to surpass.
-In Table~\ref{tab:class_comp}, we observe that this was indeed the case for all three approaches evaluated here.
-The MLP prediction results presented on Table~\ref{tab:Confusion_matrix}\subref{tab:MPL_conf_matrix} show that even though the prediction model was not 100\% accurate, the percentage of false-positive predictions was 0\%.
-The false-negative results represented 12\% of the test sample and the true predictions constituted 88\% of the test data.
-The outcome of the models showed that the Decision Tree performed best followed by the Multilayer Perceptron and the Support Vector Machine.
-However, by reviewing the confusion matrices presented in Table~\ref{tab:Confusion_matrix}, Multilayer Perceptron would be the preferred solution to be implemented in industrial applications due to the 0\% ratio in false-positive results and high accuracy of 88\%.
 
@@
 Burggräf, Wagner, Heinbach, Steinberg writing - conceptualization, review. Garcke, and Steffes-lai writing - review.
-% Burggräf performed supervision of work.
 
